### 2020-04-17 Analisis exploratorio.Rmd
Subida documentos monitoreo visual

---
title: "Exploracion monitoreo aves"
author: "Gorgia Graells"
date: "2/3/2020"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###Metodología

Orden de datos en donde todas las presencia de la base de datos quedan como abundancias de cada especie para cada sitio muestreado.

Se calculó la riqueza mínima y máxima de especies y la riqueza acumulada de especies (100 permutaciones) por temporada estudiada.

Se calculó el índice de diversidad de Shannon para especies de aves por cada sitio por temporada de muestreo. Se comparó la diferencia entre la diversidad de invierno y primavera revisando su aumento o disminución para cada sitio estudiado. Se comparó la diversidad por ambientes para cada temporada estudiada.

NMDS:
Análisis de cluster a partir de matriz de dissimilaridades. Separación de grupos a partir de dendrograma

seleccion variables ambientales mediante stepwise (funcion ordistep) para las dos temporadas de estudio

#Resultados

### 2020-04-17 README.Rmd
Subida documentos monitoreo visual

--- 2020-04-17 Analisis exploratorio.Rmd
@@
 ---
-title: "Exploracion monitoreo aves"
-author: "Gorgia Graells"
-date: "2/3/2020"
-output: word_document
+title: "Monitoreo visual"
+output: github_document
 ---
@@
 
-###Metodología
-
-Orden de datos en donde todas las presencia de la base de datos quedan como abundancias de cada especie para cada sitio muestreado.
-
-Se calculó la riqueza mínima y máxima de especies y la riqueza acumulada de especies (100 permutaciones) por temporada estudiada.
-
-Se calculó el índice de diversidad de Shannon para especies de aves por cada sitio por temporada de muestreo.
-Se comparó la diferencia entre la diversidad de invierno y primavera revisando su aumento o disminución para cada sitio estudiado.
-Se comparó la diversidad por ambientes para cada temporada estudiada.
-
-NMDS:
-Análisis de cluster a partir de matriz de dissimilaridades. Separación de grupos a partir de dendrograma
-
-seleccion variables ambientales mediante stepwise (funcion ordistep) para las dos temporadas de estudio
-
-#Resultados
+## Documentación

### 2020-04-17 AnalisisVegan.R

@@ -1,0 +1,281 @@
+#Vegan 
+
+#Exploración datos y analisis preliiminares
+#PAQUETE VEGAN
+
+library(readxl)
+library(tidyverse)
+library(vegan)
+library(MASS)
+library(ggplot2)
+library(knitr)
+
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+
+###### Modificando data frame
+
+AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+rownames(AvesInv) <-AvesInv$Sitio
+AvesInv <- AvesInv %>% dplyr::select(-Sitio)
+
+AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+rownames(AvesPrim) <-AvesPrim$Sitio
+AvesPrim <- AvesPrim %>% dplyr::select(-Sitio)
+
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_ocu.rds")
+Sitio_Amb <- Amb %>% dplyr::select(Sitio, AMBIENTE)
+
+#Inv_amb <- AvesInv %>% left_join(Sitio_Amb) %>% group_by(AMBIENTE, Especie) %>% summarise(n=sum(N_individuos))%>% spread(key = Especie, value = n, fill=0) %>% ungroup
+#Prim_amb <- AvesPrim %>% left_join(Sitio_Amb) %>% group_by(AMBIENTE, Especie) %>% summarise(n=sum(N_individuos))%>% spread(key = Especie, value = n, fill=0) %>% ungroup
+
+#write.csv(Inv_amb, "AvesInv_porAmb.csv")
+#write.csv(Prim_amb, "AvesPrim_porAmb.csv")
+
+
+############inspeccion datos
+
[…]

### 2020-04-17 anosim.R

@@ -1,0 +1,27 @@
+#Vegan -Simper
+
+#disimilaridad segun bray-curtis... aporte de sp a cada grupo definido
+
+library(readxl)
+library(tidyverse)
+library(vegan)
+library(MASS)
+library(ggplot2)
+library(knitr)
+library(parallel)
+
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_ocu.rds")
+
+
+Inv <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_regInv.rds")
+#Dissimilaridad entre grupos
+
+Inv_dist <-vegdist(Inv, method="bray", binary=FALSE, diag=FALSE, upper=FALSE, na.rm = FALSE)
+
+Inv_anosim <- with(Amb, anosim(Inv_dist, AMBIENTE))
+summary(Inv_anosim)
+plot(Inv_anosim)
+
+

### 2020-04-17 exploracion datos, analisis preliminar.R

@@ -1,0 +1,52 @@
+#Exploración datos y analisis preliiminares
+#EXPLORACION 
+
+library(readxl)
+library(tidyverse)
+library(MASS)
+library(ggplot2)
+library(knitr)
+library(vegan)
+
+#############
+#Preparacion datos
+
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+AvesInv <- AvesInv %>% dplyr::select(-Sitio)
+
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
+
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_ocu.rds")
+Amb <- Amb %>% dplyr::select(-Sitio)
+
+#############
+#matriz de similitudes
+#Invierno
+Inv.dist <- vegdist(AvesInv)
+Inv.ano <- with(Amb, anosim(Inv.dist, AMBIENTE))
+summary(Inv.ano)
+plot(Inv.ano, xlab="Clases", ylab="Ranking de distancias")
+
+Prim.dist <- vegdist(AvesPrim)
+Prim.ano <- with(Amb, anosim(Prim.dist, AMBIENTE))
+summary(Prim.ano)
+plot(Prim.ano, xlab="Clases", ylab="Ranking de distancias")
+
+#########
+
+#reagrupación aves por ambiente
+
[…]

### 2020-08-03 Analisis_Occu_punto/Analisis_Occu_Invierno.R
Archivos de carpeta ocupancia. Analisis de ocupancia, preparacion de capas, preparacion de datos

@@ -1,0 +1,70 @@
+#ANALISIS DE OCUPANCIA / Rstudio cloud
+
+#devtools::install_github("derek-corcoran-barrios/DiversityOccu")
+
+library(DiversityOccupancy)
+library(readr)
+library(dplyr)
+
+
+#Invierno
+
+data_reg <-read_rds("Occdata_regInv.rds")
+
+data_ocu <-read_rds("Occdata_ocu.rds")
+data_ocu <- data_ocu %>% dplyr::select(-Sitio)
+
+data_det <-read_rds("Occdata_detInv.rds") 
+
+
+
+###
+
+
+Occu <- batchoccu(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=45,  form= ~Presencia_perros+ Temperatura +Humedad+ DirViento +RapViento+ Agua+ Presencia_otros ~ CobVeg + AMBIENTE+ Distancia_rio+ Distancia_Costa +Distancia_Agua+ Altura+ Distancia_construccion+ Distancia_camino, dredge=TRUE, SppNames =c("AGUILUCHO", "BLANQUILLO", "CHERCAN", "CHINCOL", 
+                                                                                                                                                                                                                                                                                    "CHURRETE_CHICO",  "CHURRETE_COMUN", "CHURRETE_COSTERO", 
+                                                                                                                                                                                                                                                                                   "COLEGIAL",  "CORMORAN", "COTORRA_ARGENTINA","DIUCA", "DIUCON",  
+                                                                                                                                                                                                                                                                                    "DORMILONA_CABEZA_NEGRA","GAVIOTA_FRANKLIN","GAVIOTA_GARUMA", "GARZA_CHICA","GAVIOTA", 
+                                                                                                                                                                                                                                                                                    "GOLONDRINA_CHILENA",  "GOLONDRINA_DORSO_NEGRO",  "GORRION", 
+                                                                                                                                                                                                                                                                                    "GUANAY",  "HUAIRAVO", "JILGUERO",  "JOTE_CABEZA_ROJA", 
[…]

### 2020-08-03 Analisis_Occu_punto/Analisis_Occu_Primavera.R

@@ -1,0 +1,43 @@
+#ANALISIS OCUPANCIA PRIMAVERA/Rstudio cloud
+
+#library(devtools)
+#devtools::install_github("derek-corcoran-barrios/DiversityOccu")
+
+library(DiversityOccupancy)
+library(readr)
+library(dplyr)
+
+setwd("~/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
+
+data_reg <-read_rds("Occdata_regPRIM.rds")
+
+data_ocu <-read_rds("Occdata_ocu.rds")
+data_ocu <- data_ocu %>% select(-Sitio)
+
+data_det <-read_rds("Occdata_detPrim.rds") 
+
+##
+
+OccuPrim <- batchoccu(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=48,  form= ~Presencia_perros+ Temperatura +Humedad+ DirViento +RapViento+ Agua+ Presencia_lobos+ Presencia_pescadores ~ CobVeg + AMBIENTE+ Distancia_rio+ Distancia_Costa +Distancia_Agua+ Altura+ Distancia_construccion+ Distancia_camino, dredge=TRUE, SppNames =c("BLANQUILLO", "CACHUDITO", "CAHUIL", "CHERCAN", "CHINCOL", 
+                                                                                                                                                                                                                                                                                                                                                        "CHURRETE_CHICO", "CHURRETE_COMUN", "CHURRETE_COSTERO", "CODORNIZ",
+                                                                                                                                                                                                                                                                                                                                                        "COLEGIAL", "COMETOCINO", "CORMORAN", "COTORRA_ARGENTINA","DIUCA", "FIOFIO",  
+                                                                                                                                                                                                                                                                                                                                                        "GAVIOTA_FRANKLIN","GAVIOTA_GARUMA", "GARZA_GRANDE","GAVIOTA", "GAVIOTIN_ELEGANTE",
+                                                                                                                                                                                                                                                                                                                                                        "GOLONDRINA_CHILENA",  "GOLONDRINA_DORSO_NEGRO",  "GORRION", 
+                                                                                                                                                                                                                                                                                                                                                        "GUANAY",  "HUAIRAVO", "HUALA", "JOTE_CABEZA_NEGRA", "JOTE_CABEZA_ROJA", 
[…]

### 2020-08-03 Analisis_Occu_punto/Occu37sp.R

@@ -1,0 +1,472 @@
+# Función ocupancia nueva junio
+#Se trabajo con 37 especies, todas presentes en ambas temporadas 
+#Se evalúa ocupancia utilizando bufferes generados en MapaYuryi.R
+
+
+library(tidyverse)
+library(stringr)
+library(unmarked)
+library(MuMIn)
+library(caret)
+
+
+setwd("~/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
+##########################
+
+####INVIERNO###
+
+## OCUPANCIA PARA LAS 37 especies 
+
+data_reg <- read_rds("Occdata_regInv.rds")
+
+colnames(data_reg) <- str_replace_all(colnames(data_reg), " ", "_")
+
+#seleccion de 37 especies
+data_reg <-data_reg %>% dplyr::select(starts_with("BLANQUILLO"), starts_with("CHERCAN"),starts_with("CHINCOL"), starts_with("CHURRETE_CHICO"), 
+                                                           starts_with("CHURRETE_COMUN"), starts_with("CHURRETE_COSTERO"), starts_with("COLEGIAL"), starts_with("CORMORAN"), starts_with("COTORRA_ARGENTINA"),
+                                                           starts_with("DIUCA"),starts_with ("FRANKLIN"),starts_with("GARUMA"), starts_with("GAVIOTA"), starts_with("GOLONDRINA_CHILENA"), 
+                                                           starts_with("GOLONDRINA_DORSO_NEGRO"),  starts_with("GORRION"),  starts_with("GUANAY"),  starts_with("HUAIRAVO"),starts_with("JOTE_NEGRO"), 
+                                                           starts_with("JOTE_CABEZA_ROJA"), starts_with("LILE"), starts_with("MIRLO"), starts_with("MONJA"),  starts_with("PALOMA"), 
+                                                           starts_with("PELICANO"), starts_with("PERRITO"), starts_with("PILPILEN"), starts_with("PILPILEN_NEGRO"), starts_with("PIQUERO"), 
[…]

### 2020-08-03 Analisis_Occu_punto/Prep datos_Occu_punto.R

@@ -1,0 +1,443 @@
+ #OCUPANCIA para MONITOREO PUNTO 
+
+#Preparación de datos para analisis"
+
+library(readr)
+library(readxl)
+library(tidyverse)
+library(hms)
+library(dplyr)
+
+
+##########################################################
+#########################################################
+
+#REGISTRO AVES: INVIERNO 2019
+
+
+Reg_completo_aves <- read_csv("/home/giorgia/Documents/Doctorado Tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL"))) 
+
+ ### Modificar data frame
+
+SITIOS <- Reg_completo_aves %>% pull(Sitio) %>% unique() %>% sort()
+Spp <- Reg_completo_aves %>% pull(Especie) %>% unique() %>% sort()
+
+Datos <- list()     #separación de especies en listas distintas
+for(i in 1:length(Spp)){
+  Datos[[i]] <- Reg_completo_aves %>% filter(Especie==Spp[i])
+  Datos[[i]]  <- Datos[[i]]  %>% group_by(Sitio, Dia_muestreo) %>% summarise(n = sum(N_individuos))
+  
+}
+
+names(Datos) <- Spp
+
+
+### Generemos data frame base
+
+
+OccData <- list()
+
+for(x in 1:length(Datos)){
+  Temp <- data.frame(Dia1 = rep(0, length(SITIOS)), Dia2 = rep(0, length(SITIOS)), Dia3 = rep(0, length(SITIOS)))
+  row.names(Temp) <- SITIOS
+  for(i in 1:nrow(Datos[[x]])){
+    Temp[row.names(Temp) == Datos[[x]]$Sitio[i], Datos[[x]]$Dia_muestreo[i]] <- Datos[[x]]$n[i]
+  }
+  colnames(Temp) <- paste0(Spp[x], c(1,2,3))
+  OccData[[x]] <- Temp
+  message(paste(Spp[x], "Ready!"))
+}
+
+OccData <- bind_cols(OccData)
+row.names(OccData) <- SITIOS
+
+
+## Cambiando para ocupacia/solo presencia y ausencias
+
+OccData2 <- OccData
+
+for(i in 1:nrow(OccData)){
[…]

### 2020-08-03 Analisis_Occu_punto/Prep_capas.R

@@ -1,0 +1,159 @@
+##preparación de capas ambientales
+
+##distancias geograficas
+#library(devtools)
+#devtools::install_github("DerekYves/placement")
+library(placement)
+library(raster)
+library(rgdal)
+library(sf)
+library(fasterize)
+library(tidyverse)
+
+
+
+###Selección area:Chile
+
+#pacman::p_load(readr, leaflet, geojsonio, stringr, rgdal)
+#Chile <- readOGR("G:/Mi unidad/Documentos Yoryi/Documents yoryi/Doctorado Tesis/Mapas/CHL_adm(1)/CHL_adm0.shp")
+Chile_reg <- st_read("G:/Mi unidad/Documentos Yoryi/Documents yoryi/Doctorado Tesis/Mapas/CHL_adm(1)/CHL_adm3.shp")
+  
+###Seleccion de estudio: Valparaiso , viña y concon
+
+Valparaiso <- Chile_reg %>% dplyr::filter(NAME_1 == "Valparaíso") %>% dplyr::filter(NAME_3 %in% c("Vina del Mar", "Valparaiso"))
+
+
+###Generacion de capas###
+
+#####Utilizar capa de altura de http://srtm.csi.cgiar.org/ para utilizar como molde de raster para capas siguientes
+#(mejor resolucion que worldclim)
+
+Valpo <- raster::getData("SRTM",  lon = -71.61269, lat = -33.0472)
+
+Valpo <- crop(Valpo, extent(Valparaiso))
+
+Temporal <- Valpo
+values(Temporal) <- ifelse(is.na(values(Temporal)), 1, NA)
+Borde_costa_Mascara <- fasterize(sf = Valparaiso, raster = Valpo)
+
+saveRDS(Borde_costa_Mascara, "Borde_costa_masc.rds")
+
+##Altura 
+
+Borde_costa_mascara <- read_rds("Borde_costa_masc.rds")
+Alt <- Valpo*Borde_costa_mascara
+
+saveRDS(Alt, "Alt.rds")
+
+
+###Distancia al mar###############################################
+
+Dist_marValpo <- distance(Temporal, doEdge = TRUE)
+Dist_marValpo <- Dist_marValpo*Borde_costa_Mascara
+
+saveRDS(Dist_marValpo, "Dist_marValpo.RDS")
+
+
+###Distance to rivers##############################################
+#Rios bajados del sitio de DivaGis
[…]

### 2020-08-03 Analisis_Occu_punto/Scraping datos clima.R

@@ -1,0 +1,129 @@
+#SCRAPING PARA OBTENER DATOS DE CLIMA EN METEORED.CL
+
+
+################################
+#Ejemplo tutorial
+
+#Scraping con phantomjs //web con javascript
+
+library(rvest)
+library(stringr)
+library(plyr)
+library(dplyr)
+library(ggvis)
+library(knitr)
+
+# Let phantomJS scrape techstars, output is written to techstars.html
+
+system("./phantomjs scrape_techstars.js")
+
+batches <- html("techstars.html") %>%   html_nodes(".batch")
+
+class(batches) #crea una lista con la información de la web
+
+
+batch_titles <- batches %>%   html_nodes(".batch_class") %>%   html_text()
+
+batch_season <- str_extract(batch_titles, "(Fall|Spring|Winter|Summer)")
+batch_year <- str_extract(batch_titles, "([[:digit:]]{4})")
+
+
+# location info is everything in the batch title that is not year info or season info
+batch_location <- sub("\\s+$", "",
+                      sub("([[:digit:]]{4})", "",
+                          sub("(Fall|Spring|Winter|Summer)","",batch_titles)))
+
+
+# create data frame with batch info.
+batch_info <- data.frame(location = batch_location,
+                         year = batch_year,
+                         season = batch_season)
+
+breakdown <- lapply(batches, function(x){
+  company_info <- x %>% html_nodes(".parent")
+  companies_single_batch <- lapply(company_info, function(y){
+    as.list(gsub("\\[\\+\\]\\[\\-\\]\\s", "", y %>%
+                   html_nodes("td") %>%
+                   html_text()))
+  })
+  
+  df <- data.frame(matrix(unlist(companies_single_batch),
+                          nrow=length(companies_single_batch),
+                          byrow=T,
+                          dimnames = list(NULL, c("company","funding","status","hq"))))
+  return(df)
+})
+
+
+# Add batch info to breakdown
+batch_info_extended <- batch_info[rep(seq_len(nrow(batch_info)),
+                                      sapply(breakdown, nrow)),]
+breakdown_merged <- rbind.fill(breakdown)
+
+# Merge all information
+techstars <- tbl_df(cbind(breakdown_merged, batch_info_extended)) %>%
+  mutate(funding = as.numeric(gsub(",","",gsub("\\$","",funding))))
+
+##########################################################################
+
[…]

### 2020-08-03 Analisis_Occu_punto/areas verdes.R

@@ -1,0 +1,14 @@
+#Draw features on a blank slate
+
+library(leaflet.extras)
+
+leaflet() %>%
+  setView(0,0,2) %>%
+  addTiles() %>%
+  addDrawToolbar(
+    targetGroup='draw',
+    editOptions = editToolbarOptions(selectedPathOptions = selectedPathOptions()))  %>%
+  addLayersControl(overlayGroups = c('draw'), options =
+                     layersControlOptions(collapsed=FALSE)) %>%
+  addStyleEditor()
+

### 2020-08-03 Analisis_Occu_punto/figuras para avance.R

@@ -1,0 +1,28 @@
+#figura construcción para presentación
+
+library(viridis)
+library(tidyverse)
+
+setwd("G:/Mi unidad/Documentos Yoryi/Documents yoryi/Doctorado Tesis/Monitoreo aves/Analisis_Occu_punto")
+construccion <- read_rds("Capa_construccion.rds")
+plot(construccion)
+
+#es necesario cortar con mascara Valparaíso
+#crop o st_crop? según clase del objeto:
+
+class(construccion) #este es un raster, por lo q se usa crop
+
+Borde_costa_mascara <- read_rds("Borde_costa_masc.rds")
+e<- extent(Borde_costa_mascara)
+
+
+const_valpo <- crop(construccion,e)
+values(const_valpo)<- ifelse(is.na(values(const_valpo)),0,1)
+
+#para igualar las resoluciones a la mejor de estas dos capas
+
+Borde_costa_mascara<- resample(Borde_costa_mascara, const_valpo, method="ngb")
+
+const_valpo <- const_valpo*Borde_costa_mascara
+
+plot(const_valpo)

### 2020-08-03 Analisis_Occu_punto/funcion_plot.R

@@ -1,0 +1,101 @@
+library(tidyverse)
+library(DiversityOccupancy)
+library(gridExtra)
+
+#ocupancia trabajada en rstudio cloud
+#archivo guardado en wd, nombre: Ocupancia45_avesInv.rds
+Occu45 <-read_rds("Ocupancia45_avesInv.rds") 
+
+batch = Occu45
+spp = 8
+variable = "Distancia_Costa"
+
+test_plot <- function (batch, spp, variable, N = 50)
+{
+  upper <- lower <- NULL
+
+  Vars <- batch$models[[spp]]@formula %>% str_split(pattern = "~", simplify = T) %>% .[3] %>% str_split(pattern = "\\+", simplify = T) %>% as.character() %>% str_trim() %>% str_remove_all("1")
+  Vars <- Vars[str_count(Vars) != 0]
+  
+  model_data <- batch$Covs %>% select(Vars)
+  
+  stopifnot(variable %in% Vars)
+  
+  all_vars <- model_data %>% select(-one_of(variable))
+  num_vars <- all_vars %>% select_if(is.numeric) %>% summarize_all(mean)
+  cat_vars <- all_vars %>% select_if(Negate(is.numeric)) %>% purrr::map(unique)
+  
+  resp_var <- model_data %>% pull(variable) 
+  if(is.numeric(resp_var)) {
+    resp_vals <- seq(min(resp_var), max(resp_var), length.out=N)
+  } else {
+    resp_vals <- unique(resp_var)
+  }
+  
+  new_data <- tidyr::crossing(num_vars, !!!cat_vars, !!variable:=resp_vals)
+  if(nrow(new_data) < 1){
+    new_data <- data.frame(resp_vals)
+    colnames(new_data) <- variable
+  }
+  
+  pred <- predict(batch$models[[spp]], newdata = as.data.frame(new_data), se_fit=TRUE, type= "state") %>% bind_cols(new_data)
+  
+  ## Plot the response
+  my_aes <- aes(x= !!sym(variable), y = Predicted)
+  line_aes <- aes(x= !!sym(variable), y = Predicted)
+  if (length(cat_vars)==1) {
+    my_aes[["fill"]] <- sym(names(cat_vars))
+    line_aes[["colour"]] <- sym(names(cat_vars))
+  } else if (length(cat_vars)>1) {
[…]

### 2020-08-03 Analisis_Occu_punto/imagenes_sat.R

@@ -1,0 +1,27 @@
+#imagenes satelitales
+
+library(raster)
+library(readr)
+
+#construccion y caminos
+
+build_up <- raster("19H_hbase_human_built_up_and_settlement_extent_utm_30m.tif")
+plot(build_up)
+
+values(build_up) <-ifelse(values(build_up) > 240, NA, values(build_up))
+build_up <- projectRaster(build_up, crs = "+proj=longlat +datum=WGS84 +no_defs", method="ngb") #reproyeccion
+build_up <- readAll(build_up)
+write_rds(build_up, "Capa_build_up.rds")
+
+build_up <- read_rds("Capa_build_up.rds")
+
+#conviertiendo en dos capas: construccion y caminos
+construccion <- build_up
+values(construccion) <-  ifelse(values(build_up) != 201, NA, 1)
+plot(construccion)
+write_rds(construccion, "Capa_construccion.rds")
+
+caminos <- build_up
+values(caminos) <- ifelse(values(build_up) != 202, NA, 1)
+plot(caminos)
+write_rds(caminos, "Capa_caminos.rds")

### 2020-08-03 Analisis_Occu_punto/mapas_leaflet.R

@@ -1,0 +1,32 @@
+#LEAFLET PARA VER MAPAS Y PUNTOS
+
+library(leaflet)
+
+pal <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values(Dist_marValpo),
+                    na.color = "transparent")
+
+leaflet() %>% addTiles() %>%
+  addRasterImage(Dist_marValpo, colors = pal, opacity = 0.8) %>%
+  addLegend(pal = pal, values = values(Dist_marValpo),
+            title = "Distancia al mar") %>% addMarkers(data=Coords, ~Longitud, ~Latitud, label = ~Sitio)
+
+
+pal <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values(Pop),
+                    na.color = "transparent")
+
+leaflet() %>% addTiles() %>%
+  addRasterImage(Pop, colors = pal, opacity = 0.8) %>%
+  addLegend(pal = pal, values = values(Pop),
+            title = "poblacion") %>% addMarkers(data=Puntos)
+
+
+
+distancia_rio<- read_rds("DistanceToRiver.rds")
+
+pal <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values(distancia_rio),
+                    na.color = "transparent")
+
+leaflet() %>% addTiles() %>%
+  addRasterImage(distancia_rio, colors = pal, opacity = 0.8) %>%
+  addLegend(pal = pal, values = values(distancia_rio),
+            title = "Distancia rio") %>% addMarkers(data=Coords, ~Longitud, ~Latitud, label = ~Sitio)

### 2020-08-03 Funcionales aves.R
Analisis de rasgos funcionales y gremios

@@ -1,0 +1,29 @@
+#Base de datos rasgos funcionales
+#
+
+library(tidyverse)
+library(readr)
+library(readxl)
+
+#Se toman los nombres de las 37sp desde el archivo  Bird_guilts.xlsx
+Bird_guilts <- read_excel("Bird guilts.xlsx") %>% dplyr::select(Nombre, Especie)
+
+BirdFuncDat <- read_delim("BirdFuncDat.txt", "\t", escape_double = FALSE, trim_ws = TRUE) %>% 
+  rename(Especie=Scientific) %>% mutate(Especie= str_replace(Especie, "Larus pipixcan", "Leucophaeus pipixcan")) %>% 
+  mutate(Especie= str_replace(Especie, "Larus modestus", "Leucophaeus modestus"))
+
+
+BirdFunc <- left_join(Bird_guilts,BirdFuncDat)
+
+saveRDS(BirdFunc, "BirdFunc.rds")
+
+#prim
+cluster1 <-BirdFunc %>% filter(Nombre %in% c("CORMORAN", "CHINCOL","GAVIOTA","PALOMA", "ZORZAL"))
+cluster2 <-BirdFunc %>% filter(Nombre %in% c("TORTOLA", "RARA", "TORDO"))
+
+#inv
+cluster1 <-BirdFunc %>% filter(Nombre %in% c("TIUQUE", "PALOMA", "CHINCOL","GAVIOTA"))
+cluster2<-BirdFunc%>%filter(Nombre%in%c("CORMORAN","PELICANO COMÚN","MONJA","PIQUERO","PILPILEN","CHURRETE CHICO","PILPILEN NEGRO","GARUMA","JOTE CABEZA NEGRA"))
+cluster3 <-BirdFunc %>% filter(Nombre %in% c("BLANQUILLO","CHURRETE COMUN","QUELTEHUE","COLEGIAL","GOLONDRINA DORSO NEGRO","PERRITO","LILE","CHURRETE COSTERO", "GUANAY", "FRANKLIN","TAGUA COMUN","COTORRA ARGENTINA","DIUCA","GORRION","HUAIRAVO"))
+cluster4 <-BirdFunc %>% filter(Nombre %in% c("TORTOLA", "RARA", "TORDO"))
+

### 2020-08-03 Caract_sitios.R
Ambientes y mapa

@@ -1,0 +1,27 @@
+#Caracterización sitios muestreo
+
+library(tidyverse)
+library(ggplot2)
+
+data_ocu <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
+
+data_ocu <-data_ocu %>%  dplyr::select(AMBIENTE, contains("2200")) 
+colnames(data_ocu) <-colnames(data_ocu) %>%  str_remove_all(pattern = paste0("Buffer_",2200, "_"))
+
+#CobVeg + Altura + Distancia_Agua+ Distancia_rio+ Pastizales+Matorrales + Oceano+ Sup_impermeables+ Suelo_arenoso +Grava +
+#  Cultivos+ Bosque_Nativos
+
+data_ocu <- data_ocu %>%  group_by(AMBIENTE) %>%  summarise_all(.funs = list(Mean = mean, SD= sd)) %>% pivot_longer(cols = contains(c("Mean", "SD")), names_to = "Variable", values_to = "Valor")
+
+
+data_ocu_mean <- data_ocu %>% dplyr::filter(str_detect(Variable, "Mean")) %>% mutate(Variable = str_remove_all(Variable,"_Mean")) %>% rename(Media = Valor)
+  
+data_ocu_sd <-  data_ocu %>% dplyr::filter(str_detect(Variable, "SD")) %>% mutate(Variable = str_remove_all(Variable,"_SD")) %>% rename(SD = Valor) %>% full_join(data_ocu_mean)
+
+Caract_amb <- data_ocu_sd %>% filter(Variable!="Nieve") %>% filter(Variable!="Nubes")
+
+saveRDS(Caract_amb, "Caract_amb.rds")
+
+ggplot(Caract_amb, aes(x = AMBIENTE, y = Media)) + geom_col(aes(fill = Variable), position = "dodge") + geom_errorbar(aes(group = Variable, ymax = Media + SD, ymin = Media - SD), position = "dodge") + facet_wrap(~AMBIENTE, scales = "free_x",)
+

### 2020-08-03 MapaYuryi.R

@@ -1,0 +1,83 @@
+##Generación de capas de buffer (10 distancias distintas desde de los puntos de muestreo)
+#A partir de raster de cobertura de suelo de Chile completo
+
+library(leaflet)
+library(raster)
+library(tidyverse)
+library(sf)
+
+setwd("~/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit")
+
+LandCover <- readRDS("Landcover.rds")
+values(LandCover) <- ifelse(is.na(values(LandCover)), 0, values(LandCover))
+Codes <- readRDS("Codes.rds")
+
+Coords <- read_csv("~/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL"))) %>% dplyr::select(Sitio, Longitud, Latitud) %>% dplyr::distinct() %>% st_as_sf(coords = c(2,3), crs = "+proj=longlat +datum=WGS84 +no_defs")
+
+## Buffers
+
+Coords2 <- Coords %>% sf::st_transform("+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")
+
+Occdata_ocu <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_ocu.rds")
+
+Distancias <- 2200
+
+Bs <- list()
+for(x in 1:length(Distancias)){
+  Buffers <- list()
+  
+  for(i in 1:nrow(Coords2)){
+    Buffer <- Coords2[i,] %>% st_buffer(Distancias[x]) %>% rasterize(LandCover)
+    
+    Temp <- raster::trim(Buffer * LandCover)
+    
+    Table <- data.frame(Code = as.numeric(as.character(names(values(Temp) %>% table))), Frecuencia = values(Temp) %>% table %>% as.numeric(), stringsAsFactors = F) %>% full_join(Codes) %>% dplyr::filter(!is.na(Frecuencia))
+  
+    
[…]

### 2020-08-03 DiversidadAves.Rmd
Analisis exploratorios, comunitarios con vegan, ocupancia (funcion nueva) y ocupancia por ambiente (funcion nueva con rpediccion para sitios). mas readme

---
title: "Diversidad de aves"
author: "Giorgia Graells"
date: "5/4/2020"
output:
  html_document:
    df_print: paged
  pdf_document: default
bibliography: /home/giorgia/Documents/Doctorado tesis/Review Urban ecology/CoastalReviewGit/tesis_ref_2019sept.bib
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```

Urbanizacion

Centrar en especies marinas y su interaccion con las terrestres

Seasonal patterns of urban bird diversity in a Mediterranean coastal city: the positive role of open green spaces (Tzortzakaki et al. 2018)

Existen espacios urbanos creados por el hombre que presentan ventajas para las aves... como es el caso de  los espacio abandonados en las ciudades para especies terrestres

Hipotesis: La interacción entre aves marinas y terrestres ocurre en un ecotono intervenido por la urbanización el cual pudiera presentar elementos positivos y negativos para la presencia de las distintas especies en basae a sus necesidades de habitat y alimenticias.

### Extraido de: @lepczyk2017global

Because animals respond differentially to urbaniza-tion, they are often classified into the following categories: (1)urban avoiders,which are species that are generally absent in highly developed areas, but can bepresent in natural areas embedded in urban area; (2)urban utilizers, which arespecies that use urban resources and conditions but whose populations requireimmigration from natural areas; and (3)urban dwellers, which are species thatreproduce and persist in urban areas (@fischer2015categorizing).

The presence and distribution of bird species inside a city depend, amongother factors, on the biogeographic species pools, the natural history of species,and the nature and distribution of habitat-related traits (Lepczyk et al.2008;MacGregor-Fors and Scondube2011; McCaffrey et al.2012). In general,omnivorous, granivorous, and cavity-nesting species have shown the strongestassociations with urban areas in temperate areas (Chace and Walsh2006).However, insectivorous, frugivorous, and nectarivorous species are also predom-inant in some tropical and subtropical urban areas (Brazil and Mexico, Singapore,Australia, respectively; Ortega-A ́lvarez and MacGregor-Fors2011a,b).

#### Global and regional drivers

Human population size andland-cover class had the strongest correspondence with the number of bird species.The age of the cities played a tertiary role suggesting human history has a muchmore limited role relative to the physical features of the city.
Increment habitat heterogeneity with urbanization (Desrochers et al.2011)

#### Season drivers

Breeding season and migration

#### Local scale drivers

As predicted by thespecies-area relationship, urban bird species richness is strongly correlated witharea, both at the scale of the entire city (MacGregor-Fors et al.2011; Ferencet al.2014a) and within individual urban habitat patches (Fernandez-Juricic andJokimaki2001;M€ortberg2001; Chamberlain et al.2007; Murgui2007; van Heeziket al.2013). Within cities, bird species density was highest in cities with the lowestproportion of urban land cover (Aronson et al.2014), indicating that the provisionof green space at the city scale is crucial to bird species conservation in cities(Chace and Walsh2006; Evans et al.2009).

Within cities a number of factors have been suggested that determine theirsuitability for birds. These factors include (1) the presence and size of remnant(native) vegetation patches, (2) the presence of nonnative predators, (3) the struc-ture and floristic attributes of planted vegetation, and (4) supplementary feeding byhumans (Chace and Walsh2006).

### Extraído de @bellocq2017urbanization

Patrones espaciales y temporales en argentina. Se muestran relaciones interesantes con la latitud, pero rescato gráficos de riqueza de aves en relacion a distancia de centros urbanos o a cubierta de concreto. Por último un gráfico de persistencia de especies en epoca reproductiva y no reproductiva (0 a 1). Detalle de la figura: "Interannual variability of bird community composition along the urban gradient of Mardel Plata city, showing the values of persistence during the breeding and nonbreeding seasons.Persistence values vary from 0 (no species were recorded in all 3 years) to 1 (all species wererecorded all 3 years). Thecontinuous lineindicates that the level of persistence was the same inboth periods. Adapted from Leveau and Leveau (2012)"

```{r}
library(tidyverse)
library(ggplot2)

AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
```

###Metodología

Orden de datos en donde todas las presencia de la base de datos quedan como abundancias de cada especie para cada sitio muestreado.

Se calculó la riqueza mínima y máxima de especies y la riqueza acumulada de especies (100 permutaciones) por temporada estudiada.

Se calculó el índice de diversidad de Shannon para especies de aves por cada sitio por temporada de muestreo. Se comparó la diferencia entre la diversidad de invierno y primavera revisando su aumento o disminución para cada sitio estudiado. Se comparó la diversidad por ambientes para cada temporada estudiada.

NMDS:
Análisis de cluster a partir de matriz de dissimilaridades. Separación de grupos a partir de dendrograma

seleccion variables ambientales mediante stepwise (funcion ordistep) para las dos temporadas de estudio

#Resultados

#### Caracterización de sitios de muestreo

```{r, fig.height=8, fig.width=7}
Caract_amb <-read_rds ("Caract_amb.rds")

ggplot(Caract_amb, aes(x = AMBIENTE, y = Media)) + geom_col(aes(fill = fct_reorder(Variable, Media, .desc=TRUE)), position = "dodge") + geom_errorbar(aes(group = fct_reorder(Variable, Media, .desc=TRUE), ymax = Media + SD, ymin = Media - SD), position = "dodge") + facet_wrap(~AMBIENTE, scales = "free_x", nrow = 3) + theme_bw()+ labs(fill="Variables")+ xlab("Ambientes")+ ylab("Promedio porcentaje cobertura")

```

#### Aves

Un total de 54 especies de aves fueron identificadas en los sitios muestreados. De estas xx fueron vistas durante la epoca de invierno y xx durante la primavera. Sólo 37 especies se mantuvieron presentes durante ambas temporadas de muestreo

#### Ocupancia aves

```{r, fig.height=7,fig.width=8}
#extraído de Occu37sp.R

FUNS <- function(x){
  abs(diff(range(x)))
}
meta_ocupancia <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/meta_ocupancia.rds")
plot(meta_ocupancia)
```

```{r}
#### Cluster por ocupancia (Ocupación predicha por sitio muestreado en base a modelos definidos anteriormente)
library(ggdendro)

OccuPrim37_final <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/OccuPrim37_final.rds")

Dist_Prim <- dist(x = t(OccuPrim37_final$fit))
Cluster_Prim <- hclust(Dist_Prim)

#plot(Cluster_Prim, labels = Nombres)
ggdendrogram(Cluster_Prim)

```

```{r}
OccuInv37_final <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/OccuInv37_final.rds")

Dist_Inv <- dist(x = t(OccuInv37_final$fit))
Cluster_Inv <- hclust(Dist_Inv)

#plot(Cluster_Inv, labels = Nombres)
ggdendrogram(Cluster_Inv)
```

### separación por gremios de aves

### Comportamineto especies por ambiente

Dado que los ambientes no definen espacios diferenciables, es mejor hacer esto segun una variable y por sitios... quizas las mismas variables seleccionadas por ocupancia para cada gremio
```{r}

ggplot(AvesInv) + geom_point(aes(x=AMBIENTE, y=Especie, color =Comportamiento))

```

#### Referencias

### 2020-08-03 README.Rmd
subida de readme sin comentarios
Analisis exploratorios, comunitarios con vegan, ocupancia (funcion nueva) y ocupancia por ambiente (funcion nueva con rpediccion para sitios). mas readme

@@
 
-## Documentación
+#### Documentación
+
+Revisar para completar
+
+### Analisis comunitario de especies preliminar
+
+Analisis preliminar: solo reagrupacion de datos **exploracion datos, analisis preliminar.R**
+
+Utilización del paquete vegan, archivo **AnalisisVegan.R**
+
+### Ocupancia monitoreo visual
+
+#### Preparación de capas de trabajo
+
+Cada capa de trabajo para ocupancia se realizó de forma independiente y fueron determinadas en base a las preguntas de investigación.
+El archivo Prep_capas muestra este trabajo tomando como referencia la capa "altura" que determina la resolucion del raster.
+
+Se utilizó un shape file de Chile politico contemplando frontera nacional y división de comunas.Se trabajo solo con la máscara de las comunas de valparaiso, vinña del mar y concon.
+Las capas creadas fueron distancia a la costa a partir de la frontera de chile por el oeste, rios de chile descargados de divagis, distancia a cuerpos de agua al interior de las ciudades, distancia a caminos (NASA:build_up), distancia a construccion (NASA:build_up) y poblacion de divagis.
+la capa build up de la nasa era una y fue dividida en dos: caminos y contruccion /imagenes_sat.R
+creacion de capa "distancias" que incluye todas las variables.
+
+#### Preparación de datos para ocupancia
+
+Dada la confeccion del paquete DiversityOccupancy, los datos deben estar ordenados de una forma en particular.
+Para esto se debió crear un data frame para los registros de especies por cada uno de los tres dias de muestreo por sitio, un data frame para las variables de ocupancia para cada sitio y una lista de todas las variables de detección para los momentos en que se realizan los registros de especies.
+archivo Prep datos_Occu_punto.R
+
+Archivos para ocupancia: (capas deteccion, ocupancia y registros)
+
+INVIERNO
+Occdata_regInv.rds
+Occdata_ocu.rds
+Occdata_detInv.rds
+
+PRIMAVERA
+Occdata_regPRIM.rds
+Occdata_ocu.rds
+Occdata_detPrim.rds
+
+Datos presencias:
+
++ Invierno: /home/giorgia/Documents/Doctorado Tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv
+
++ Primavera: /home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv
+
+#### Ocupancia
+
+El análisis de ocupancia se realizó para los datos de invierno y primavera por separado. Los análisis se enceuntran en los archivos Analisis_Occu_Invierno.R y Analisis_Occu
+
+En esos mismo archivos se determinó la ocupancia y deteccion de las 6 especies usadas en las encuestas para cada ambiente
+
+Existe un archivo llamado Prueba_funcion_nueva.R que armó Derek para ocupancia de varias especies, en donde se continua con la siguiente especies aun cuando la anterior no haya convergido en un modelo.
+
+#### Junio
+Se realiza ocupancia con función nueva utilizando nuevas variables ambientales generadas en **MapaYuryi.R** que corresponde a capas de cobertura vegetal en buffers (distancia desde los puntos de muestreo), archivo de salida que incluye variables ambientales y buffers por distancia: **Occdata_ocu.rds** y un leaflet al final del código para ver las capas por cada sitio en el mapa.
+La ocupancia se realiza en el archivo **Occu37sp.R** utilizando las 37 especies primero para la temporada de invierno.
+Se genera un data frame con el resumen de los modelos, el cual se exporta como csv **Resumen_ocuInv_buffer.csv** ubicado en la carpeta de ocupancia.
+Se determinó a mano los modelos con valores significativos y se incluyó el valor de SE en **Resumen_ocuInv_buffer.csv** mediante excel.
+El elemento **ResModelosOcuBuffer.csv** muestra el resultado de los modelos de ocupancia por distintcas capas de buffer, lo q determina las escalas.
+A partir de esta tabla y según los valores de AICc, se eligieron los valores más bajos para determinar la escala a trabajar
+Se corrió ocupancia con laas variables ambientales y los porcentajes de cobertura vegetal definidos para la escala buffer de 2200m radio, todos juntos. 
+Resultados están en **OccuInv37_final.rds** y **OccuPrim37_final.rds**
+El resumen de resultados esta en una planilla excel llamada **Resumen_ocu_37total.xlsx** ubicada en la carpeta **Analisis_Occu_punto**.
+
+Para poder comparar el efecto de los estimadores por igual se estandarizaron las variables mediante un escalamiento (también en **Occu37sp.R**).
+El escalamiento se realizó para primavera e invierno y se corrió la ocupancia nuevamente para las variables seleccionadas que se habian identificado como las más importantes (algunas variables no se presentaban en el mapa revisado de buffers del leaflet).
+Se guardan los valores de estimadores en un data frame: PorSppInv- PorSppPrim para graficar tipo meta-analisis (guardado como **meta_ocupancia.rds**, incluuir funcion **FUN**)
+
+existe el archivo **Prueba_Funcion_Nueva.R** que contiene otros analisis de ocupancia realizados
+
+Se genera un nuevo archivo llamado **PredOccuAmb_37sp.R** donde se rescatan los datos de predicciones de la ocupancia realizada y se arman graficos de todas las especies para mostrar el rango de ocupancia dde las especies para cada ambiente para primavera e invierno.
+Se modificó la funcion de ocupancia, ahora llamada DiversityOccupancy::batchoccu3, en donde se fuerza a generar un modelo con el AMBIENTE para cada especie. Se ve la oacupancia por sitio
+
+#### Ordenando los resultados y buscando una explicacion: 1. Marco conceptual rasgos funcionales
+
+Se crearon dos archivos: 
+1. **Funcionales aves.R** 
+Se toman los nombres de las 37sp desde el archivo  Bird_guilts.xlsx, se descargaron los rasgos funcionales de aves (alimenticios y de habitat) y se filtro para las 37 aves trabajadas (comun a ambas temporadas)
+2. **Clusters ocupancia.R** para ver la agrupacion de especies segun variables de ocupancia para invierno y primavera y luego generar los clusters para rasgos funcionales

### 2020-08-03 AnalisisVegan.R

@@ -127,8 +127,9 @@ plot(vare.mds.Prim, type = "t", display = "sites")
 #...................
 
 
-#cluster analysis- "single", "complete", or "average" type: INVIERNO
+#cluster analysis- "single", "complete", or "average" type
 
+#invierno
 dis.Inv <- vegdist(AvesInv)
 cluster.Inv <- hclust(dis.Inv, "complete")
 plot(cluster.Inv)
@@ -158,7 +159,7 @@ grp <- cutree(cluster.Prim, 3)
 #Eigenvector methods -PCA CA
 
 #Principal components analysis can be run as:
-vare.pca <- rda(Aves)
+vare.pca <- rda(AvesPrim)
 vare.pca
 
 plot(vare.pca)
@@ -172,7 +173,7 @@ vare.pca <- rda(Aves, scale = TRUE)
 vare.pca
 
 plot(vare.pca, scaling = 3)
-dim(Aves)
+dim(AvesPrim)
 
 #####
 #Correspondence analysis is very similar to pca:
@@ -196,8 +197,8 @@ plot(vare.dca, display="sites", cex = 0.5)
 
 ##################
 #################  
-# Environmental interpretation
-
+# Environmental interpretation (imagen 900x600)
+#inv
 vare.mds <- metaMDS(AvesInv, trace = FALSE)
 ef <- envfit(ord=vare.mds, env=Amb, permu = 999)
 ef
@@ -209,10 +210,17 @@ ef <- envfit(vare.mds~ CobVeg + Distancia_Costa+Altura, Amb, perm=999) #Variable
 plot(vare.mds, display="site")
 plot(ef)
 
+#prim
 vare.mds2 <-metaMDS(AvesPrim,trace=FALSE)
-ef <- envfit(vare.mds ~ CobVeg + Distancia_Costa+Altura, Amb) #Variables significativas <0.001
-plot(vare.mds, display = "sites")
-plot(ef, p.max = 0.05)
+ef2 <- envfit(ord=vare.mds, env=Amb, permu = 999) #Variables significativas <0.001
+ef2
+plot(vare.mds2, display = "sites")
+plot(ef2, p.max = 0.05)
+#para variables significativas
+ef2 <- envfit(vare.mds2~ CobVeg + Distancia_Costa+Altura, Amb, perm=999) #Variables significativas <0.001
+plot(vare.mds2, display="site")
+plot(ef2)
+
 
 #plot(ef)
 tmp <- with(Amb, ordisurf(vare.mds, CobVeg, add = TRUE))

### 2020-08-03 Clusters ocupancia.R

@@ -1,0 +1,46 @@
+
+## Clusters
+
+#### Cluster por ocupancia (Ocupación predicha por sitio muestreado en base a modelos definidos anteriormente)
+library(tidygraph)
+library(ggdendro)
+
+###################
+#Cluster primavera
+OccuPrim37_final <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/OccuPrim37_final.rds")
+
+Dist_Prim <- dist(x = t(OccuPrim37_final$fit))
+Cluster_Prim <- hclust(Dist_Prim)
+
+#plot(Cluster_Prim, labels = Nombres)
+ggdendrogram(Cluster_Prim)
+
+
+###################
+#Cluster invierno
+OccuInv37_final <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/OccuInv37_final.rds")
+
+Dist_Inv <- dist(x = t(OccuInv37_final$fit))
+Cluster_Inv <- hclust(Dist_Inv)
+
+#plot(Cluster_Inv, labels = Nombres)
+ggdendrogram(Cluster_Inv)
+
+
+##################
+#Cluster rasgos funcionales
+
+
+
+
+#### Con bootstraping
+
+library(pvclust)
+## multiscale bootstrap resampling (non-parallel)
+boston.pv <- pvclust(OccuInv37_final$fit, nboot=5000, parallel=FALSE, method.dist = "euclidian", method.hclust = "complete")
+
+
+plot(boston.pv)
+pvrect(boston.pv, pv = "si")
+pvrect(boston.pv, pv = "au")
+pvrect(boston.pv, pv = "bp")

### 2020-08-03 PredOccuAmb_Allsp.R

@@ -1,0 +1,488 @@
+# Prediccion de ocupancia para ambientes 
+
+library(tidyverse)
+library(stringr)
+library(unmarked)
+library(MuMIn)
+library(caret)
+
+setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
+
+## Funcion nueva ocupancia:
+
+batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
+  if(is.null(SppNames)){
+    SppNames <- paste("species", 1:spp, sep =".")
+  }
+  secuencia <- c(1:spp)*(ncol(pres)/spp)
+  secuencia2<-secuencia-(secuencia[1]-1)
+  models <- vector('list', spp)
+  fit <- matrix(NA, nrow(pres), spp)
+  Mods <- list()
+  if(is.null(SppNames)){
+    colnames(fit) <- paste("species", 1:spp, sep =".")
+  }else if(class(SppNames) == "character"){
+    colnames(fit) <- SppNames
+  }
+  if (dredge == FALSE) {
+    for(i in 1:length(secuencia)) {
+      data <- pres[, secuencia2[i]:secuencia[i]]
+      data2 <- unmarkedFrameOccu(y = data, siteCovs = sitecov, obsCovs = obscov)
+      try({
+        models[[i]] <- occu(as.formula(form), data2)
+      }, silent = T)
+      try({
+        fit[, i] <- suppressWarnings(predict(models[[i]], type = "state", newdata = sitecov))$Predicted
+      }, silent = T)
+      Mods = NULL
+      print(paste("Species", as.character(i), "ready!"))
+    }
+  }
+  else {
+    for(i in 1:length(secuencia)) {
+      data <- pres[, secuencia2[i]:secuencia[i]]
+      data2 <- unmarkedFrameOccu(y = data, siteCovs = sitecov, obsCovs = obscov)
+      try({
+        #Partimos en dos Detección y occupancia
+        form <- as.character(form)
+        Div <- str_squish(form) %>% str_remove_all(" ")  %>% stringr::str_split(pattern = "~", simplify = T)
+        
+        ### Separamos dos formulas Occupancia y Deteccion
+        
+        Det <- Div[length(Div) - 1]
+        
+        VarDet <- str_split(Det, "\\+", simplify = T) %>% as.character()
+        
+        Fs <- list()
+        
[…]

### 2020-08-03 Prueba_Funcion_Nueva.R

@@ -1,0 +1,195 @@
+#Funcion nueva ocupancia para avance
+#Se trabajo con las 6 especies de las encuestas y se evaluó ocupancia en los distintos ambientes. 
+# No se evaluó ocupancia para las otras variables
+  
+library(tidyverse)
+library(stringr)
+library(unmarked)
+library(MuMIn)
+
+setwd("~/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
+
+## OCUPANCIA PARA LAS 6 ESPECIES DE ENCUESTAS, POR AMBIENTE, PRIMAVERA
+
+data_reg <-read_rds("Occdata_regPRIM.rds") #%>% dplyr::select(starts_with("CHINCOL"), starts_with("CORMORAN"), starts_with("PALOMA"), starts_with("PELICANO"),starts_with("ZORZAL"),starts_with("GAVIOTA"))
+
+data_ocu <-read_rds("Occdata_ocu.rds")
+data_ocu <- data_ocu %>% select(-Sitio)
+
+buffer <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Buffers.rds")
+
+data_det <-read_rds("Occdata_detPrim.rds")
+
+
+
+
+#pres = data_reg
+#sitecov = data_ocu
+#obscov = data_det
+#spp = 5
+#dredge = T
+#SppNames =c( "CHINCOL", "CORMORAN", "PALOMA", "PELICANO", "ZORZAL")
+#form <-  "~Presencia_perros+ Temperatura +Humedad+ DirViento +RapViento+ Agua+ Presencia_lobos+ Presencia_pescadores ~ CobVeg + AMBIENTE+ Distancia_rio+ Distancia_Costa +Distancia_Agua+ Altura+ Distancia_construccion+ Distancia_camino"
+
+#Funcion ocupancia nueva
+batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
+  if(is.null(SppNames)){
+    SppNames <- paste("species", 1:spp, sep =".")
+  }
+  secuencia <- c(1:spp)*(ncol(pres)/spp)
+  secuencia2<-secuencia-(secuencia[1]-1)
+  models <- vector('list', spp)
+  fit <- matrix(NA, nrow(pres), spp)
+  Mods <- list()
+  if(is.null(SppNames)){
[…]

### 2020-08-04 PredOccuAmb_Allsp.R
Ocupancia con ambiente como variable forzada. El codigo está listo para la primavera, falta invierno.

@@ -284,6 +284,9 @@ batchoccu3 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
   return(result)
 }
 
+
+
+
 #Ocupancia para todas las especies en primavera
 
 data_det <-read_rds("Occdata_detPrim.rds")
@@ -297,9 +300,13 @@ data_reg <-read_rds("Occdata_regPRIM.rds")
 
 Spp <- colnames(data_reg) %>% str_remove_all("\\d") %>% unique()
 
-Nuevos_Datos <- data.frame(AMBIENTE = unique(data_ocu$AMBIENTE), Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA)
+#Nuevos_Datos <- data.frame(AMBIENTE = unique(data_ocu$AMBIENTE), Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA)
+Nuevos_Datos <- data_ocu %>% group_by(AMBIENTE) %>% summarise_all(mean) %>% mutate(Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA)
 
 Resultados <- list()
+
+PorSitio <- data.frame(Sitio = read_rds("Occdata_ocu.rds")$Sitio, Ambiente = data_ocu$AMBIENTE)
+
 
 for(i in 1:length(Spp)){
   data_reg_temp <- data_reg %>% dplyr::select(starts_with(Spp[i]))
@@ -307,25 +314,29 @@ for(i in 1:length(Spp)){
   data_reg_temp <- data_reg_temp[,1:3]
   
   message("Ajustando el modelo")
-  OccuPrim_temp <- batchoccu3(pres = data_reg_temp, sitecov = data_ocu, obscov = data_det, spp=1,  form= "~1 ~ AMBIENTE", dredge=TRUE, SppNames =Spp[i])
+  OccuPrim_temp <- batchoccu3(pres = data_reg_temp, sitecov = data_ocu, obscov = data_det, spp=1,  form= "~Temperatura + Humedad +Agua~ AMBIENTE + CobVeg + Distancia_Costa+Altura+ Distancia_construccion+Distancia_rio", dredge=TRUE, SppNames =Spp[i])
   
-  Nuevos_Datos_Temp <- Nuevos_Datos
+  Nuevos_Datos$Spp <- Spp[i]
+
+  Nuevos_Datos_Temp <- as.data.frame(Nuevos_Datos)
   
[…]

### 2020-08-04 README.Rmd
Actualizacion README

@@
 Se modificó la funcion de ocupancia, ahora llamada DiversityOccupancy::batchoccu3, en donde se fuerza a generar un modelo con el AMBIENTE para cada especie. Se ve la oacupancia por sitio
+Ocupancia con ambiente como variable forzada.
+El codigo está listo para la primavera, falta invierno.
+Se obtienen dos resultados: para cada ambiente (considerando el promedio de cada variable para cada ambiente) y para cada sitio considerando el valor de cada variable
 

### 2020-08-05 README.Rmd
Ocupancia con ambiente forzado con variables ambientales considerando buffers 2200m pra inv y primm. NMDS con vegan y graficos

--- 2020-08-03 README.Rmd
@@
 Se modificó la funcion de ocupancia, ahora llamada DiversityOccupancy::batchoccu3, en donde se fuerza a generar un modelo con el AMBIENTE para cada especie. Se ve la oacupancia por sitio
+Ocupancia con ambiente como variable forzada.
+Se corrio ocupancia con forzamiento de ambiente y todas las otras variables definidas en el ppt seleccionadas con anteriorirdad (incluidos los buffers de 2200 (prim e inv).
+Se obtienen dos resultados: para cada ambiente (considerando el promedio de cada variable para cada ambiente) y para cada sitio considerando el valor de cada variable
+Se corre nmsd en vegan y se hacen varios graficos bacanes
 

### 2020-08-05 PredOccuAmb_Allsp.R

@@ -147,7 +147,7 @@ batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
   return(result)
 }
 
-
+#Nueva funcion ocupancia con ambiente forzado como variable de ocupancia
 batchoccu3 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
   if(is.null(SppNames)){
     SppNames <- paste("species", 1:spp, sep =".")
@@ -286,12 +286,11 @@ batchoccu3 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
 
 
 
-
 #Ocupancia para todas las especies en primavera
 
 data_det <-read_rds("Occdata_detPrim.rds")
 
-data_ocu <-read_rds("Occdata_ocu.rds")
+data_ocu <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
 data_ocu <- data_ocu %>% dplyr::select(-Sitio)
 colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
 
@@ -314,7 +313,7 @@ for(i in 1:length(Spp)){
   data_reg_temp <- data_reg_temp[,1:3]
   
   message("Ajustando el modelo")
-  OccuPrim_temp <- batchoccu3(pres = data_reg_temp, sitecov = data_ocu, obscov = data_det, spp=1,  form= "~Temperatura + Humedad +Agua~ AMBIENTE + CobVeg + Distancia_Costa+Altura+ Distancia_construccion+Distancia_rio", dredge=TRUE, SppNames =Spp[i])
+  OccuPrim_temp <- batchoccu3(pres = data_reg_temp, sitecov = data_ocu, obscov = data_det, spp=1,  form= "~ Temperatura +Humedad ~ CobVeg +AMBIENTE+ Altura + Distancia_rio+ Buffer_2200_Pastizales+Buffer_2200_Matorrales + Buffer_2200_Oceano+ Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso+ Buffer_2200_Cultivos + Buffer_2200_Plantación_de_árboles ", dredge=TRUE, SppNames =Spp[i])
   
   Nuevos_Datos$Spp <- Spp[i]
 
[…]

### 2020-08-06 PredOccuAmb_Allsp.R
Arreglo en el códifo para incluir la extraccion del mejor modelo en los df de resultados y el guardado de todos los DF

@@ -300,9 +300,9 @@ data_reg <-read_rds("Occdata_regPRIM.rds")
 Spp <- colnames(data_reg) %>% str_remove_all("\\d") %>% unique()
 
 #Nuevos_Datos <- data.frame(AMBIENTE = unique(data_ocu$AMBIENTE), Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA)
-Nuevos_Datos <- data_ocu %>% group_by(AMBIENTE) %>% summarise_all(mean) %>% mutate(Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA)
+Nuevos_Datos <- data_ocu %>% group_by(AMBIENTE) %>% summarise_all(mean) %>% mutate(Pred = NA, SE = NA, Spp = NA, Up = NA, Down = NA, Modelo = NA)
 
-Resultados <- list()
+ResultadosPrim <- list()
 
 PorSitio <- data.frame(Sitio = read_rds("Occdata_ocu.rds")$Sitio, Ambiente = data_ocu$AMBIENTE)
 
@@ -326,6 +326,7 @@ for(i in 1:length(Spp)){
   message(paste("Prediciendo occupancia", Spp[i]))
   
   Nuevos_Datos_Temp$Pred <- predict(OccuPrim_temp$models[[1]], type = "state", newdata = Nuevos_Datos_Temp)$Predicted
+  Nuevos_Datos_Temp$Modelo <- OccuPrim_temp$Mods[[1]]$Form[1]
   
   message("Prediciendo SE")
   
@@ -336,11 +337,15 @@ for(i in 1:length(Spp)){
   Nuevos_Datos_Temp$Up <- predict(OccuPrim_temp$models[[1]], type = "state", newdata = Nuevos_Datos_Temp)$upper
   
   Nuevos_Datos_Temp$Down <- predict(OccuPrim_temp$models[[1]], type = "state", newdata = Nuevos_Datos_Temp)$lower
-  Resultados[[i]] <- Nuevos_Datos_Temp
+  ResultadosPrim[[i]] <- Nuevos_Datos_Temp
   message(i)
 }
 
-Resultados <- Resultados %>% reduce(bind_rows)
+ResultadosPrim <- ResultadosPrim %>% reduce(bind_rows)
+PorSitioPrim <- PorSitio
+
+saveRDS(ResultadosPrim, "ResultadosPrim.rds")
+saveRDS(PorSitioPrim, "PorSitioPrim.rds")
 
 ##############################################
 
[…]

### 2020-08-07 README.Rmd
Archivo nuevo Ensamble_fun.R para hacer analisis exploratorios de relaciones ensambles aves por ambiente y rasgos funcionales.

@@
 Se corrio ocupancia con forzamiento de ambiente y todas las otras variables definidas en el ppt seleccionadas con anteriorirdad (incluidos los buffers de 2200 (prim e inv).
-Se obtienen dos resultados: para cada ambiente (considerando el promedio de cada variable para cada ambiente) y para cada sitio considerando el valor de cada variable
+Se obtienen dos resultados: para cada ambiente (considerando el promedio de cada variable para cada ambiente) y para cada sitio considerando el valor de cada variable, se saca tb el mejor modelo y queda en una columna.
+Se guardan los resultados como **ResultadosInv.rds**, **ResultadosPrim.rds**, **PorSitioInv.rds** y **PorSitioPrim.rds** y **PredOccuSitio.rds**
+
 Se corre nmsd en vegan y se hacen varios graficos bacanes
@@
 2. **Clusters ocupancia.R** para ver la agrupacion de especies segun variables de ocupancia para invierno y primavera y luego generar los clusters para rasgos funcionales
+
+Archivo **Ensamble_func.R** con graficos y analisis exploratorios de ensamble de aves y su posible explicacion con rasgos funcionales

### 2020-08-07 Ensamble_func.R

@@ -1,0 +1,58 @@
+# Ensamble aves definido por rasgos funcionales
+
+library(ggrepel)
+library(tidyverse)
+library(stringr)
+library(MuMIn)
+library(caret)
+library(readr)
+
+setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit")
+
+
+
+#Informacion de ensambles
+
+Todo_NMDS <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Todo_NMDS.csv")
+Hull <- Todo_NMDS %>% group_by(AMBIENTE, Estacion) %>% slice(chull(MDS1, MDS2))
+
+
+# Informacion rasgos funcionales
+BirdFunc <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdFunc.rds")
+colnames(BirdFunc) <- make.names(colnames(BirdFunc))
+
+Species <- read_csv("Species.csv") %>%   rename(Nombre =Especies)
+Species <- full_join(x=Species, y= BirdFunc)
+
+Species_hull <- Species %>% group_by(Diet.5Cat) %>% dplyr::filter(!is.na(MDS1), !is.na(MDS2))%>% slice(chull(MDS1, MDS2))#####
+
+
+# Grafico con especies
+
+ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) + 
+  geom_polygon(data = Hull, aes(color = AMBIENTE, fill = AMBIENTE), alpha = 0.2)  + 
+  facet_wrap(~Estacion) + 
+  geom_point(data = Species, aes(color=Diet.5Cat)) + 
+  ggrepel::geom_text_repel(data = Species, aes(label = Nombre), size=2)+
+  theme_bw()
+
+
+
+###
+ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) + 
+  geom_polygon(data = Hull, aes(color = AMBIENTE), alpha = 0.2)  + 
+  facet_wrap(~Estacion) + 
+  geom_point(data = Species, size=1, aes(color=Diet.5Cat)) + 
+  geom_polygon(data=Species_hull,  aes(color=Diet.5Cat, lty = Diet.5Cat, fill=Diet.5Cat), alpha = 0.1)+
[…]

### 2020-08-07 Funcionales aves.R

@@ -4,26 +4,27 @@
 library(tidyverse)
 library(readr)
 library(readxl)
+library(taxize)
 
-#Se toman los nombres de las 37sp desde el archivo  Bird_guilts.xlsx
-Bird_guilts <- read_excel("Bird guilts.xlsx") %>% dplyr::select(Nombre, Especie)
+
+setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit")
+
+#Se toman los nombres de las 59sp totales de ambas temporadas desde el archivo Bird guilts.xlsx preparado con nombre comun y cientifico
+
+Bird_sp <- read_excel("Bird guilts.xlsx") %>% dplyr::select(-Alimentacion)%>% dplyr::select(-Habitat)
 
 BirdFuncDat <- read_delim("BirdFuncDat.txt", "\t", escape_double = FALSE, trim_ws = TRUE) %>% 
-  rename(Especie=Scientific) %>% mutate(Especie= str_replace(Especie, "Larus pipixcan", "Leucophaeus pipixcan")) %>% 
-  mutate(Especie= str_replace(Especie, "Larus modestus", "Leucophaeus modestus"))
+  rename(Especie=Scientific) %>% mutate(Especie= str_replace(Especie, "Larus pipixcan", "Leucophaeus pipixcan"),
+                                        Especie= str_replace(Especie, "Larus modestus", "Leucophaeus modestus"),
+                                        Especie= str_replace(Especie, "Buteo polyosoma", "Geranoaetus polyosoma"),
+                                        Especie= str_replace(Especie, "Casmerodius albus", "Ardea alba"),
+                                        Especie= str_replace(Especie, "Larus maculipennis", "Chroicocephalus maculipennis"),
+                                        Especie= str_replace(Especie, "Sterna elegans", "Thalasseus elegans"),
+                                        Especie= str_replace(Especie, "Carduelis barbata", "Spinus barbatus"),
+                                        Especie= str_replace(Especie, "Catharacta chilensis", "Stercorarius chilensis")) 
+  
 
 
[…]

### 2020-08-07 PredOccuAmb_Allsp.R

@@ -413,12 +413,20 @@ saveRDS(ResultadosInv, "ResultadosInv.rds")
 saveRDS(PorSitioInv, "PorSitioInv.rds")
 
 
-###
+#################################################################################################################
+setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
+
+
+ResultadosInv <- readRDS("ResultadosInv.rds")
+ResultadosPrim <- readRDS("ResultadosPrim.rds")
+PorSitioInv <- readRDS("PorSitioInv.rds")
+PorSitioPrim <- readRDS("PorSitioPrim.rds")
+
 
 ###################################################################### Visualizando
 #PRIM
 ResultadosPrim <- ResultadosPrim %>% mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO", "VERDE", "ROCA INTERVENIDA", "PLAYA INTERVENIDA", "PLAYA NATURAL"))
-ggplot(Resultados, aes(x=AMBIENTE, y=Pred))+ geom_point(aes(color = Spp)) + geom_errorbar(aes(ymax = Pred + SE, ymin = Pred - SE, color = Spp)) + ylim(c(0,1.05))+
+ggplot(ResultadosPrim, aes(x=AMBIENTE, y=Pred))+ geom_point(aes(color = Spp)) + geom_errorbar(aes(ymax = Pred + SE, ymin = Pred - SE, color = Spp)) + ylim(c(0,1.05))+
   xlab("Ambientes")+ylab("Predicción de presencia") + facet_wrap(~Spp)+theme_classic()+ theme(axis.text.x = element_text(angle=70, vjust= 1, hjust=1), legend.position = "none")
 
 #INV
@@ -434,33 +442,12 @@ ggplot(ResultadosInv, aes(x=AMBIENTE, y=Pred))+ geom_point(aes(color = Spp)) + g
 ###############################
 #Inicio analisis vegan
 
-library(vegan)
-
-#modificando el orden de columnas para analisis vegan
-
-#Prim
-PredOccuAmb_Prim <- Resultados %>%  dplyr::select(-SE) %>% dplyr::select(-Up) %>% dplyr::select(-Down)%>%  
-  group_by(AMBIENTE,Spp) %>% spread(key = Spp, value = Pred, fill=0) %>% ungroup
-
[…]

### 2020-08-12 README.Rmd
Resumen de modelos e importancia de variables

@@
 
-Se crearon dos archivos: 
-1. **Funcionales aves.R** 
-Se toman los nombres de las 37sp desde el archivo  Bird_guilts.xlsx, se descargaron los rasgos funcionales de aves (alimenticios y de habitat) y se filtro para las 37 aves trabajadas (comun a ambas temporadas)
-2. **Clusters ocupancia.R** para ver la agrupacion de especies segun variables de ocupancia para invierno y primavera y luego generar los clusters para rasgos funcionales
+Se crearon distintos archivos: 
+**Funcionales aves.R** 
+Se toman los nombres de todas las especies desde el archivo  Bird_guilts.xlsx, se descargaron los rasgos funcionales de aves (alimenticios y de habitat) y se filtro para todas las aves, idependiente de la temporada
 
-Archivo **Ensamble_func.R** con graficos y analisis exploratorios de ensamble de aves y su posible explicacion con rasgos funcionales
+**Clusters ocupancia.R** para ver la agrupacion de especies segun variables de ocupancia para invierno y primavera y luego generar los clusters para rasgos funcionales
+
+Archivo **Ensamble_func.R** con graficos y analisis exploratorios de ensamble de aves y su posible explicacion con rasgos funcionales.
+Resumen de modelos e importancia de variables.- se obtiene el df Resumen_Modelos (para inv y prim)

### 2020-08-12 Ensamble_func.R

@@ -27,10 +27,10 @@ Species <- full_join(x=Species, y= BirdFunc)
 Species_hull <- Species %>% group_by(Diet.5Cat) %>% dplyr::filter(!is.na(MDS1), !is.na(MDS2))%>% slice(chull(MDS1, MDS2))#####
 
 
-# Grafico con especies
+# Grafico con areas ambientes y especies con puntos
 
 ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) + 
-  geom_polygon(data = Hull, aes(color = AMBIENTE, fill = AMBIENTE), alpha = 0.2)  + 
+  geom_polygon(data = Hull, aes( fill = AMBIENTE), alpha = 0.2)  + 
   facet_wrap(~Estacion) + 
   geom_point(data = Species, aes(color=Diet.5Cat)) + 
   ggrepel::geom_text_repel(data = Species, aes(label = Nombre), size=2)+
@@ -43,16 +43,88 @@ ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) +
   geom_polygon(data = Hull, aes(color = AMBIENTE), alpha = 0.2)  + 
   facet_wrap(~Estacion) + 
   geom_point(data = Species, size=1, aes(color=Diet.5Cat)) + 
-  geom_polygon(data=Species_hull,  aes(color=Diet.5Cat, lty = Diet.5Cat, fill=Diet.5Cat), alpha = 0.1)+
+  geom_polygon(data=Species_hull,  aes(lty = Diet.5Cat, fill=Diet.5Cat), alpha = 0.2)+
   ggrepel::geom_text_repel(data = Species, aes(label = Nombre), size=2)+
   theme_bw()
 
 
 
-################################3
 
-data_ocu <-readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+#########################################################################################
 
-PredOccuSitio <- readRDS("~/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/PredOccuSitio.rds")
+#Resumen de modelos e importancia de variables
 
+#Invierno
+ResultadosInv2 <- ResultadosInv %>% group_by(Spp) %>% summarise(Modelo = unique(Modelo))
+
+
[…]

### 2020-08-12 PredOccuAmb_Allsp.R

@@ -414,13 +414,11 @@ saveRDS(PorSitioInv, "PorSitioInv.rds")
 
 
 #################################################################################################################
-setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
 
-
-ResultadosInv <- readRDS("ResultadosInv.rds")
-ResultadosPrim <- readRDS("ResultadosPrim.rds")
-PorSitioInv <- readRDS("PorSitioInv.rds")
-PorSitioPrim <- readRDS("PorSitioPrim.rds")
+ResultadosInv <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/ResultadosInv.rds")
+ResultadosPrim <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/ResultadosPrim.rds")
+PorSitioInv <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/PorSitioInv.rds")
+PorSitioPrim <- readRDS("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/PorSitioPrim.rds")
 
 
 ###################################################################### Visualizando

### 2020-08-14 Analisis_Occu_punto/Prep datos_Occu_punto.R
Modificacion de codigo para trabajar ocupancias con nombre de especies en vez de nombre comun de aves. Modificacion enarcihvo de preparacion de cpas ocupancia y cambio de elementos Occdata_regPRIM.rds y Occdata_regInv.rds guardados en MonitoreoVisualGit

@@ -15,9 +15,18 @@ library(dplyr)
 #REGISTRO AVES: INVIERNO 2019
 
 
-Reg_completo_aves <- read_csv("/home/giorgia/Documents/Doctorado Tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL"))) 
+Reg_completo_aves <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL"))) 
+Reg_completo_aves <- Reg_completo_aves  %>% 
+  mutate(Especie=case_when(Especie == "JOTE NEGRO"~"JOTE CABEZA NEGRA",
+                           Especie == "LILEN"~"LILE",
+                           Especie == "PELICANO"~"PELICANO COMÚN", 
+                          TRUE~Especie)) %>% rename(Nombre=Especie)
 
- ### Modificar data frame
+Nombre_sp <- read_excel("Bird guilts.xlsx") %>% dplyr::select(Nombre, Especie) %>% mutate(Especie=str_replace_all(Especie, " ", "_"))
+
+Reg_completo_aves <- left_join(Reg_completo_aves, Nombre_sp)
+ 
+### Modificar data frame
 
 SITIOS <- Reg_completo_aves %>% pull(Sitio) %>% unique() %>% sort()
 Spp <- Reg_completo_aves %>% pull(Especie) %>% unique() %>% sort()
@@ -66,7 +75,17 @@ saveRDS(OccData2, "Occdata_regInv.rds")
 
 #REGISTRO DE AVES : PRIMAVERA 2019
 
-Registro_aves_verano <- read_csv("G:/Mi unidad/Documentos Yoryi/Documents yoryi/Doctorado Tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
[…]

### 2020-08-18 README.Rmd
readme con resumen de modelos e importancia de variables
Se cambio el nombre de las especies por los nombres cientificos y se corrio ocupancia para todas las sp nuevamente. Graficos Tmabien se vio analisis NMDS y ensambles con nuevos y mejores colores

@@
 Resumen de modelos e importancia de variables.- se obtiene el df Resumen_Modelos (para inv y prim)
+
+--- analisis exploraorios con rasgos funcionales, pero se presentan errores desde informaciond e ocupancia por nombre comun de especies (ademas dde elevados valores de ocupancia para mas de 42 sp)
+14 agoosto: Modificacion de codigo para trabajar ocupancias con nombre de especies en vez de nombre comun de aves.
+Modificacion enarcihvo de preparacion de cpas ocupancia y cambio de elementos Occdata_regPRIM.rds y Occdata_regInv.rds guardados en MonitoreoVisualGit
+
+Se cambio el nombre de las especies por los nombres cientificos y se corrio ocupancia para todas las sp nuevamente. Graficos
+Tmabien se vio analisis NMDS y ensambles con nuevos y mejores colores

### 2020-08-18 Ensamble_func.R

@@ -18,34 +18,46 @@ Hull <- Todo_NMDS %>% group_by(AMBIENTE, Estacion) %>% slice(chull(MDS1, MDS2))
 
 
 # Informacion rasgos funcionales
-BirdFunc <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdFunc.rds")
+BirdFunc <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdFunc.rds")%>% mutate(Especie=str_replace_all(Especie, " ", "_"))
 colnames(BirdFunc) <- make.names(colnames(BirdFunc))
 
-Species <- read_csv("Species.csv") %>%   rename(Nombre =Especies)
+Species <- read_csv("Species.csv") %>%   rename(Especie =Especies)   
 Species <- full_join(x=Species, y= BirdFunc)
 
 Species_hull <- Species %>% group_by(Diet.5Cat) %>% dplyr::filter(!is.na(MDS1), !is.na(MDS2))%>% slice(chull(MDS1, MDS2))#####
 
 
+
+
 # Grafico con areas ambientes y especies con puntos
 
 ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) + 
-  geom_polygon(data = Hull, aes( fill = AMBIENTE), alpha = 0.2)  + 
+  geom_polygon(data = Hull, aes( fill = AMBIENTE), alpha = 0.3)  + 
   facet_wrap(~Estacion) + 
   geom_point(data = Species, aes(color=Diet.5Cat)) + 
-  ggrepel::geom_text_repel(data = Species, aes(label = Nombre), size=2)+
+  scale_fill_manual(values=c('#1b9e77','#d95f02','#7570b3','#e7298a','#66a61e','#e6ab02'))+
+    theme_bw()
+
+# Grafico con areas ambientes y especies con nombres
+
+ggplot(Todo_NMDS, aes(x = MDS1, y = MDS2)) + 
+  geom_polygon(data = Hull, aes( fill = AMBIENTE), alpha = 0.3)  + 
+  facet_wrap(~Estacion) + 
+  geom_point(data = Species, aes(color=Diet.5Cat)) + 
+  ggrepel::geom_text_repel(data = Species, aes(label = Nombre), size=3)+
[…]

### 2020-08-18 PredOccuAmb_Allsp.R

@@ -6,7 +6,6 @@ library(unmarked)
 library(MuMIn)
 library(caret)
 
-setwd("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto")
 
 ## Funcion nueva ocupancia:
 
@@ -288,9 +287,9 @@ batchoccu3 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
 
 #Ocupancia para todas las especies en primavera
 
-data_det <-read_rds("Occdata_detPrim.rds")
+data_det <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_detPrim.rds")
 
-data_ocu <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+data_ocu <-read_rds("Occdata_occu.rds")
 data_ocu <- data_ocu %>% dplyr::select(-Sitio)
 colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
 
@@ -304,7 +303,7 @@ Nuevos_Datos <- data_ocu %>% group_by(AMBIENTE) %>% summarise_all(mean) %>% muta
 
 ResultadosPrim <- list()
 
-PorSitio <- data.frame(Sitio = read_rds("Occdata_ocu.rds")$Sitio, Ambiente = data_ocu$AMBIENTE)
+PorSitio <- data.frame(Sitio = read_rds("Occdata_occu.rds")$Sitio, Ambiente = data_ocu$AMBIENTE)
 
 
 for(i in 1:length(Spp)){
@@ -320,7 +319,7 @@ for(i in 1:length(Spp)){
   Nuevos_Datos_Temp <- as.data.frame(Nuevos_Datos)
   
   PorSitio <-  PorSitio %>% mutate(Spp = NA)
-  PorSitio$Spp <- OccuPrim_temp$fit
+  PorSitio$Spp <- OccuPrim_temp$fit 
   colnames(PorSitio)[i + 2] <- Spp[i]
   
   message(paste("Prediciendo occupancia", Spp[i]))
@@ -340,7 +339,7 @@ for(i in 1:length(Spp)){
   ResultadosPrim[[i]] <- Nuevos_Datos_Temp
   message(i)
 }
-
+#
[…]

### 2020-08-20 Exploración_enfocada.R
Se borró script de exploración de datos Se geneó un nuevo script llamado ExploracionEnfocada

@@ -1,0 +1,60 @@
+#Exploracion datos monitoreo visual aves
+
+#reorden y vegan con preguntas generales Stefan tras reunion 18 agosot 2020
+
+library(readxl)
+library(tidyverse)
+library(vegan)
+library(MASS)
+library(ggplot2)
+library(knitr)
+
+#Preparacion datos
+
+
+BirdNames <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdFunc.rds")%>% mutate(Especie=str_replace_all(Especie, " ", "_"))
+BirdNames <- BirdNames %>%  dplyr::select(Nombre, Especie) %>%  rename(cientifico =Especie) %>%   rename(Especie =Nombre) 
+
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% 
+  mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
+         Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Especie= str_replace(Especie, "LILEN", "LILE"))
+
+AvesInv <- left_join(x=AvesInv, y= BirdNames)
+
+
+
+
+
+...
+
+
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
+
+
+
+
+
+
+
+
+
+#preparacion de datos para matriz similitudes 
+
[…]

### 2020-08-20 exploracion datos, analisis preliminar.R

@@ -1,52 +1,0 @@
-#Exploración datos y analisis preliiminares
-#EXPLORACION 
-
-library(readxl)
-library(tidyverse)
-library(MASS)
-library(ggplot2)
-library(knitr)
-library(vegan)
-
-#############
-#Preparacion datos
-
-AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesInv <- AvesInv %>% dplyr::select(-Sitio)
-
-AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
-AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
-
-Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_ocu.rds")
-Amb <- Amb %>% dplyr::select(-Sitio)
-
-#############
-#matriz de similitudes
-#Invierno
-Inv.dist <- vegdist(AvesInv)
-Inv.ano <- with(Amb, anosim(Inv.dist, AMBIENTE))
-summary(Inv.ano)
-plot(Inv.ano, xlab="Clases", ylab="Ranking de distancias")
-
-Prim.dist <- vegdist(AvesPrim)
-Prim.ano <- with(Amb, anosim(Prim.dist, AMBIENTE))
-summary(Prim.ano)
-plot(Prim.ano, xlab="Clases", ylab="Ranking de distancias")
-
-#########
-
-#reagrupación aves por ambiente
-
[…]

### 2020-08-20 README.Rmd
Grafico de riqueza de especies por ambiente y estacion Limpieza de script vegan

@@
 Tmabien se vio analisis NMDS y ensambles con nuevos y mejores colores
+
+### Exploración de datos en base a reunion 18 agosto
+
+Se acuerda generar una grafico de riqueza de especies por ambiente, separado en marino-terrestre
+Para Presencia especies, abundancia y probabilidad de ocupancia realizar:
+- NMDS + ANOSIM
+- SIMPER
+- BIOENV
+
+Se borró script de exploración de datos en donde se habia comenzado con la exploración, pero fue cocntinuada en el script AnalisisVegan
+Se geneó un nuevo script llamado ExploracionEnfocada, en donde se resuelve lo conversado en reunion del 18 agosto con stefan.
+
+grafico de riqueza por ambiente, estacional

### 2020-08-20 AnalisisVegan.R

@@ -1,6 +1,6 @@
 #Vegan 
 
-#Exploración datos y analisis preliiminares
+#Exploración datos y analisis preliminares
 #PAQUETE VEGAN
 
 library(readxl)
@@ -10,27 +10,33 @@ library(MASS)
 library(ggplot2)
 library(knitr)
 
-AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+#Preparación de datos
 
-###### Modificando data frame
-
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
 AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-rownames(AvesInv) <-AvesInv$Sitio
 AvesInv <- AvesInv %>% dplyr::select(-Sitio)
 
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
 AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-rownames(AvesPrim) <-AvesPrim$Sitio
-AvesPrim <- AvesPrim %>% dplyr::select(-Sitio)
+AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
 
[…]

### 2020-08-20 Exploración_enfocada.R

@@ -11,28 +11,57 @@ library(knitr)
 
 #Preparacion datos
 
-
-BirdNames <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdFunc.rds")%>% mutate(Especie=str_replace_all(Especie, " ", "_"))
-BirdNames <- BirdNames %>%  dplyr::select(Nombre, Especie) %>%  rename(cientifico =Especie) %>%   rename(Especie =Nombre) 
-
-AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% 
-  mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
-         Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
-         Especie= str_replace(Especie, "LILEN", "LILE"))
-
-AvesInv <- left_join(x=AvesInv, y= BirdNames)
+BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
 
 
+#Riqueza invierno
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))%>% rename(Nombre =Especie)
+AvesInv <- AvesInv %>% group_by(Sitio, Nombre, AMBIENTE) %>% summarise(n=sum(N_individuos)) %>% 
+  mutate(Nombre= str_replace(Nombre, "PELICANO", "PELICANO COMÚN"),
[…]

### 2020-08-21 Exploración_enfocada.R
Analisis vegan de NMDS, ANOSIM y SIMPER para abundancias de especies en invierno y primavera

@@ -9,10 +9,14 @@ library(MASS)
 library(ggplot2)
 library(knitr)
 
+
+
+#####################################
+# PRIMERA PARTE: RIQUEZA DE ESPECIES
+
+
 #Preparacion datos
-
 BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
-
 
 #Riqueza invierno
 AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
@@ -33,8 +37,6 @@ Riqueza_Prom <- AvesInv_riq %>% group_by(AMBIENTE, Habitat) %>% summarise(Riquez
 ggplot(AvesInv_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), position="dodge") + facet_wrap(~AMBIENTE, scales = "free_x", ncol=2)+
   scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
   xlab("Sitios de muestreo")+   theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
-
-
 
 # Riqueza primavera
 
@@ -64,14 +66,11 @@ ggplot(AvesPrim_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), posi
   xlab("Sitios de muestreo")+ theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
 
 
+#########################
+## SEGUNDA PARTE: ABUNDANCIA
 
 
-
-
-
-
-
-#preparacion de datos para matriz similitudes 
+#preparacion de datos bundancia por especie
 
 AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
[…]

### 2020-08-21 Exploración_enfocada.R
analisis Envfit para inv y prim para abundancia

@@ -78,12 +78,19 @@ AvesInv <- AvesInv %>% dplyr::select(-Sitio)
 
 AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
 AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
+AvesPrim <-AvesPrim %>% dplyr::select(-Sitio) 
 
 #Datos ambientales  incluidos buffers
 Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
-Amb <- Amb %>% dplyr::select(-Sitio)
-
+Amb <- Amb %>% dplyr::select(-Sitio)%>% 
+  dplyr::select(CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>% 
+  rename( `Cobertura vegetal` =CobVeg) %>% rename( `Distancia a río` =Distancia_rio) %>% 
+  rename( `Bosque nativo` =`Buffer_2200_Bosque Nativo`) %>% rename( Cultivos =`Buffer_2200_Cultivos`) %>% 
+  rename( Grava =`Buffer_2200_Grava`) %>% rename( Oceano =`Buffer_2200_Oceano`) %>% 
+  rename( Pastizales =`Buffer_2200_Pastizales`) %>% rename( `Matorrales` =`Buffer_2200_Matorrales`) %>% 
+  rename( `Superficies impermeables` =`Buffer_2200_Sup impermeables`) %>% rename( `Suelo arenoso` =`Buffer_2200_Suelo arenoso`) %>% 
[…]

### 2020-08-21 Exploración_enfocada.R
Analisis NMDS, anosim, simper, envfit listos para abundancia, comp especies y ocupancia

@@ -13,7 +13,7 @@ library(knitr)
 
 #####################################
 # PRIMERA PARTE: RIQUEZA DE ESPECIES
-
+#####################################
 
 #Preparacion datos
 BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
@@ -66,11 +66,13 @@ ggplot(AvesPrim_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), posi
   xlab("Sitios de muestreo")+ theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
 
 
-#########################
-## SEGUNDA PARTE: ABUNDANCIA
 
 
-#preparacion de datos bundancia por especie
+#####################################
+# SEGUNDA PARTE: ORDINATION ANALISIS- para presencia sp, abundancias y prob ocupancia
+#####################################
+
+#preparacion de datos 
 
 AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
 AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
@@ -92,13 +94,13 @@ Amb <- Amb %>% dplyr::select(-Sitio)%>%
   rename( `Plantacion de arboles` =`Buffer_2200_Plantación de árboles`)
   
 
+#############################################################################################################################################
+# PRES-AUS: En base a funcion metaMDS, que estandariza las abundancias, considera solo composicion de especies
 
+##### METAMDS Non-metric Multidimensional scaling- NMDS
 
-
-#### Non-metric Multidimensional scaling- NMDS
 #Invierno
-
-ord1Inv <- metaMDS(AvesInv) #stress= 0.2316387
[…]

### 2020-08-27 README.Rmd
readme: analsis vegan para abundancias inv y prim
analisis Envfit para inv y prim para abundancia
Analisis NMDS, anosim, simper, envfit listos para abundancia, comp especies y ocupancia
modificacion de parametros de distintas funciones para su correcto uso en exploracion con vegan... aprendiendo

@@
 Se borró script de exploración de datos en donde se habia comenzado con la exploración, pero fue cocntinuada en el script AnalisisVegan
-Se geneó un nuevo script llamado ExploracionEnfocada, en donde se resuelve lo conversado en reunion del 18 agosto con stefan.
+Se geneó un nuevo script llamado **Exploracion_enfocada.R**, en donde se resuelve lo conversado en reunion del 18 agosto con stefan.
 
 grafico de riqueza por ambiente, estacional
+
+vegan para abundancia por especie invierno y primavera: NMDS, Anosim, Simper
+vegan para abundancia por especie invierno y primaveera: envfit
+
+analisis listos para abundancia, comp especies y ocupancia
+
+modificacion de parametros de distintas funciones para su correcto uso

### 2020-08-27 Exploración_enfocada.R

@@ -97,29 +97,58 @@ Amb <- Amb %>% dplyr::select(-Sitio)%>%
 #############################################################################################################################################
 # PRES-AUS: En base a funcion metaMDS, que estandariza las abundancias, considera solo composicion de especies
 
+
+
 ##### METAMDS Non-metric Multidimensional scaling- NMDS
+#metaMDS: estandariza, genera matriz, genera monoMDS
 
-#Invierno
-ord1Inv <- metaMDS(AvesInv) #stress= 0.234609 
-stressplot(ord1Inv)
+### Invierno
+Inv_nmds1_bray <- metaMDS(AvesInv, distance="bray", k=2, try=20, trymax=100, autotransform=TRUE, wascores=FALSE, trace=1, plot=FALSE) 
+#try: num de randomizaciones para solucione estable
+#autotransform: wisconsin double standarization para datos grandes de abundancia
+#stress= 0.2380544  
 
-ordiplot(ord1Inv)
-ordihull(ord1Inv,groups = Amb$AMBIENTE)
-points(ord1Inv)
+plot(Inv_nmds1_bray, type = "n")
+points(Inv_nmds1_bray, display = "sites", cex = 0.8, pch=21, col="red", bg="red") #revisar para graficar con color por grupo
+#probar orditorp para superposicion
 
-AnosimInv <-anosim(AvesInv, grouping=Amb$AMBIENTE, permutations = 999, distance = "bray", strata = NULL,
-       parallel = getOption("mc.cores"))
-summary(AnosimInv)
-plot(AnosimInv)
+stressplot(Inv_nmds1_bray)
+#buen fit con alto valor de ajuste
 
-##Primavera
-ord1Prim <- metaMDS(AvesPrim) #stress= 0.1947774
-stressplot(ord1Prim)
+GoF_Inv_nmds1_bray <- goodness(Inv_nmds1_bray)
+plot(Inv_nmds1_bray, type = "p")
+points(Inv_nmds1_bray, display = "sites", cex=GoF_Inv_nmds1_bray*100) 
 
-ordiplot(ord1Prim)
-ordihull(ord1Prim, groups = Amb$AMBIENTE)
-points(ord1Prim)
+#Testeo con Anosim
[…]

### 2020-08-28 AnalisisVegan.R
Borrado de scripts analisis_vegan.R y anosim.R porque fuerron incluidos en Exploracion_enfocada.R Script modificado ajustando modelos de las funciones y cómo sacar tabla para comparar simpers

@@ -1,295 +1,0 @@
-#Vegan 
-
-#Exploración datos y analisis preliminares
-#PAQUETE VEGAN
-
-library(readxl)
-library(tidyverse)
-library(vegan)
-library(MASS)
-library(ggplot2)
-library(knitr)
-
-#Preparación de datos
-
-AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesInv <- AvesInv %>% dplyr::select(-Sitio)
-
-AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
-AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesPrim <-AvesPrim %>% dplyr::select(-Sitio)
-
-#Datos ambientales  incluidos buffers
-Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
-Amb <- Amb %>% dplyr::select(-Sitio)
-
-
-#############
-#matriz de similitudes
-#Invierno
-Inv.dist <- vegdist(AvesInv)
-Inv.ano <- with(Amb, anosim(Inv.dist, AMBIENTE))
-summary(Inv.ano)
-plot(Inv.ano, xlab="Clases", ylab="Ranking de distancias")
-
-Prim.dist <- vegdist(AvesPrim)
-Prim.ano <- with(Amb, anosim(Prim.dist, AMBIENTE))
-summary(Prim.ano)
-plot(Prim.ano, xlab="Clases", ylab="Ranking de distancias")
-
-
-############inspeccion datos
-
-#plot(Amb, gap=0, panel=panel.smooth)
-
-###################################
-#VEGAN
-#DIVERSIDAD
-
[…]

### 2020-08-28 Exploración_enfocada.R

@@ -95,39 +95,33 @@ Amb <- Amb %>% dplyr::select(-Sitio)%>%
   
 
 #############################################################################################################################################
-# PRES-AUS: En base a funcion metaMDS, que estandariza las abundancias, considera solo composicion de especies
+# A.  Riqueza especies: En base a funcion metaMDS, que estandariza las abundancias, considera solo composicion de especies
 
-
-
-##### METAMDS Non-metric Multidimensional scaling- NMDS
-#metaMDS: estandariza, genera matriz, genera monoMDS
+##### 1. METAMDS Non-metric Multidimensional scaling- NMDS
+#metaMDS: estandariza, genera matriz a partir de vegdist, genera monoMDS
 
 ### Invierno
 Inv_nmds1_bray <- metaMDS(AvesInv, distance="bray", k=2, try=20, trymax=100, autotransform=TRUE, wascores=FALSE, trace=1, plot=FALSE) 
-#try: num de randomizaciones para solucione estable
+#try: num de randomizaciones para soluciones estable
 #autotransform: wisconsin double standarization para datos grandes de abundancia
-#stress= 0.2380544  
+##### stress= 0.2316405   
 
 plot(Inv_nmds1_bray, type = "n")
-points(Inv_nmds1_bray, display = "sites", cex = 0.8, pch=21, col="red", bg="red") #revisar para graficar con color por grupo
-#probar orditorp para superposicion
+points(Inv_nmds1_bray, display = "sites") #revisar para graficar con color por grupo
+ordispider(Inv_nmds1_bray, groups = Amb$AMBIENTE, col=1:6, label = TRUE)
 
+#plot(Inv_nmds1_bray$dist, Inv_nmds1_bray$diss, type = "p")
 stressplot(Inv_nmds1_bray)
 #buen fit con alto valor de ajuste
 
-GoF_Inv_nmds1_bray <- goodness(Inv_nmds1_bray)
-plot(Inv_nmds1_bray, type = "p")
-points(Inv_nmds1_bray, display = "sites", cex=GoF_Inv_nmds1_bray*100) 
-
-#Testeo con Anosim
+## test: ANOSIM
 #ejemplo en PAST3: perm=9999, bray-curtis index similarity
[…]

### 2020-08-28 anosim.R

@@ -1,27 +1,0 @@
-#Vegan -Simper
-
-#disimilaridad segun bray-curtis... aporte de sp a cada grupo definido
-
-library(readxl)
-library(tidyverse)
-library(vegan)
-library(MASS)
-library(ggplot2)
-library(knitr)
-library(parallel)
-
-AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
-Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_ocu.rds")
-
-
-Inv <- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Analisis_Occu_punto/Occdata_regInv.rds")
-#Dissimilaridad entre grupos
-
-Inv_dist <-vegdist(Inv, method="bray", binary=FALSE, diag=FALSE, upper=FALSE, na.rm = FALSE)
-
-Inv_anosim <- with(Amb, anosim(Inv_dist, AMBIENTE))
-summary(Inv_anosim)
-plot(Inv_anosim)
-
-

### 2020-08-30 Exploración_enfocada.R
Creacion de funcion TidyNMDS para extraer datos de metaMDS y poder hacer un ggplot de puntos con color para ambientes

@@ -110,7 +110,21 @@ plot(Inv_nmds1_bray, type = "n")
 points(Inv_nmds1_bray, display = "sites") #revisar para graficar con color por grupo
 ordispider(Inv_nmds1_bray, groups = Amb$AMBIENTE, col=1:6, label = TRUE)
 
-#plot(Inv_nmds1_bray$dist, Inv_nmds1_bray$diss, type = "p")
+#########################################################
+#Función para sacar los datos y ocupar ggplot
+TidyNMDS <- function(MDS, COVS){
+  DF <- COVS
+  DF2 <- MDS$points %>% as.data.frame()
+  DF <- bind_cols(DF2, DF)
+  return(DF = DF)
+}
+#########################################################
+
+#Funcion para grafico NMDS en ggplot
+Tidy_Inv_nmds1_bray <- TidyNMDS(MDS = Inv_nmds1_bray, COVS = Amb)
+ggplot(Tidy_Inv_nmds1_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ scale_color_manual(values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))
+
+#stress
 stressplot(Inv_nmds1_bray)
 #buen fit con alto valor de ajuste
 
@@ -122,7 +136,6 @@ stressplot(Inv_nmds1_bray)
 
 Diss_Inv1 <- vegdist(AvesInv, method="bray", binary=TRUE, diag=TRUE, upper=TRUE, na.rm = FALSE)
 #binary TRUE estandariza presencia/ausencia /revisar metodo de distancia
-
 Anosim_Diss_Inv1<-anosim(Diss_Inv1, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", 
                    strata = NULL, parallel = getOption("mc.cores")) #tengo 4 cores en este pc
 summary(Anosim_Diss_Inv1)
@@ -136,6 +149,11 @@ plot(Prim_nmds1_bray, type = "n")
 points(Prim_nmds1_bray, display = "sites") #revisar para graficar con color por grupo
 ordispider(Prim_nmds1_bray,groups = Amb$AMBIENTE, col=1:6, label = TRUE)
 
+#grafico con ggplot funcion nueva
[…]

### 2020-09-01 Comportamiento_Aves.R
Funcion nueva para envfit y sacar datos para grafico en ggplot nuevo archivo comportamineto aves
subida de readme en rmd y md

@@ -1,0 +1,17 @@
+#Comportamiento aves por ambiente
+
+ComportamientoInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especie, Comportamiento) %>% 
+  mutate(Comportamiento=as.character(Comportamiento),
+         Comportamiento= str_replace(Comportamiento, "1", "Nadando o caminando en el agua"),
+         Comportamiento= str_replace(Comportamiento, "2", "En el suelo -tierra, pasto, arena, roca"),
+         Comportamiento= str_replace(Comportamiento, "3", "Entre el follaJe -en árbol o arbusto"),
+         Comportamiento= str_replace(Comportamiento, "4", "Posado en altura -poste o cable"),
+         Comportamiento= str_replace(Comportamiento, "5", "Volando o planeando"),
+         Comportamiento= str_replace(Comportamiento, "6", "En un nido") )
+  
+
+
+
+group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
+AvesInv <- AvesInv %>% dplyr::select(-Sitio)

### 2020-09-01 Exploración_enfocada.R

@@ -8,8 +8,7 @@ library(vegan)
 library(MASS)
 library(ggplot2)
 library(knitr)
-
-
+library(ggrepel)
 
 #####################################
 # PRIMERA PARTE: RIQUEZA DE ESPECIES
@@ -72,15 +71,18 @@ ggplot(AvesPrim_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), posi
 # SEGUNDA PARTE: ORDINATION ANALISIS- para presencia sp, abundancias y prob ocupancia
 #####################################
 
-#preparacion de datos 
+#############################################################################################################################################
+# A.  Riqueza especies: modificacion a matriz, ocupando solo valores de 0 y 1
+#funcion metaMDS tb estandariza las abundancias, considera solo composicion de especies
 
+#Preparacion de datos con datos de presencia ausencia de especies por sitio
 AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
 AvesInv <- AvesInv %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesInv <- AvesInv %>% dplyr::select(-Sitio)
+AvesInv <- AvesInv %>% dplyr::select(-Sitio) %>% mutate_all(~ifelse(.x > 0, 1, 0))
 
 AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
 AvesPrim <- AvesPrim %>% group_by(Sitio, Especie) %>% summarise(n=sum(N_individuos)) %>% spread(key = Especie, value = n, fill=0) %>% ungroup
-AvesPrim <-AvesPrim %>% dplyr::select(-Sitio) 
[…]

### 2020-09-02 Comportamiento_Aves.R
arreglo de **Comportamiento_aves.R** para inv y prim

@@ -1,17 +1,82 @@
 #Comportamiento aves por ambiente
 
+library(readxl)
+library(tidyverse)
+library(ggplot2)
+
+
+## Invierno
+
 ComportamientoInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
 ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especie, Comportamiento) %>% 
   mutate(Comportamiento=as.character(Comportamiento),
-         Comportamiento= str_replace(Comportamiento, "1", "Nadando o caminando en el agua"),
-         Comportamiento= str_replace(Comportamiento, "2", "En el suelo -tierra, pasto, arena, roca"),
-         Comportamiento= str_replace(Comportamiento, "3", "Entre el follaJe -en árbol o arbusto"),
-         Comportamiento= str_replace(Comportamiento, "4", "Posado en altura -poste o cable"),
-         Comportamiento= str_replace(Comportamiento, "5", "Volando o planeando"),
-         Comportamiento= str_replace(Comportamiento, "6", "En un nido") )
-  
+         Comportamiento= str_replace(Comportamiento, "1", "En el agua"), #Nadando o caminando en el agua
+         Comportamiento= str_replace(Comportamiento, "2", "En el suelo"), #-tierra, pasto, arena, roca
+         Comportamiento= str_replace(Comportamiento, "3", "Entre el follaje"), #-en árbol o arbusto
+         Comportamiento= str_replace(Comportamiento, "4", "Posado en altura"), #-poste o cable
+         Comportamiento= str_replace(Comportamiento, "5", "En el aire"), #Volando o planeando
+         Comportamiento= str_replace(Comportamiento, "6", "En un nido"),
+         Comportamiento= str_replace(Comportamiento, "7", "A altura media"), #, roca o similar
[…]

### 2020-09-03 Comportamiento_Aves.R
arreglo de graficos

@@ -16,13 +16,14 @@ ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especi
          Comportamiento= str_replace(Comportamiento, "4", "Posado en altura"), #-poste o cable
          Comportamiento= str_replace(Comportamiento, "5", "En el aire"), #Volando o planeando
          Comportamiento= str_replace(Comportamiento, "6", "En un nido"),
-         Comportamiento= str_replace(Comportamiento, "7", "A altura media"), #, roca o similar
+         Comportamiento= str_replace(Comportamiento, "7", "Posado a altura media"), #, roca o similar
          Comportamiento= str_replace(Comportamiento, "8", "Otro")) %>% # 8 = anidando o de lejos 
   mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
          Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
          Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
-  group_by(AMBIENTE, Especie, Comportamiento) %>% summarise(Total_ind =n()) %>% ungroup() %>% dplyr::filter(Total_ind >5)
-
+  group_by(AMBIENTE, Especie, Comportamiento) %>% summarise(Total_ind =n()) %>% ungroup() %>% 
+  dplyr::filter(Especie %in% c("CHURRETE COSTERO", "CORMORAN", "SCUA","BLANQUILLO","DIUCA","JOTE CABEZA ROJA","JOTE CABEZA NEGRA","PIQUERO", "PALOMA", "GAVIOTA" ))
+   
 
 BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
 BirdNames <- BirdNames %>%   rename(Cientifico = Especie, Especie =Nombre)
@@ -31,11 +32,11 @@ ComportamientoInv <- left_join(x=ComportamientoInv, y= BirdNames)
 
 ComportamientoInv <- ComportamientoInv %>% 
[…]

### 2020-09-03 Exploración_enfocada.R

@@ -37,6 +37,12 @@ ggplot(AvesInv_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), posit
   scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
   xlab("Sitios de muestreo")+   theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
 
+
+ggplot(AvesInv_riq, aes(x=Habitat, y=Riqueza)) + geom_boxplot(aes(fill=Habitat), position="dodge", notch = T) + facet_wrap(~AMBIENTE, scales = "free_x", ncol=2)+
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
+  xlab("Sitios de muestreo")+   theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
+
+
 # Riqueza primavera
 
 AMB_nombres <-read_rds("Occdata_occu.rds") %>% dplyr::select(Sitio, AMBIENTE)
@@ -60,7 +66,15 @@ AvesPrim_riq <- AvesPrim_riq %>% mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO",
 
 Riqueza_Prom <- AvesPrim_riq %>% group_by(AMBIENTE, Habitat) %>% summarise(Riqueza = mean(Riqueza))
 
-ggplot(AvesPrim_riq, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), position="dodge") + facet_wrap(~AMBIENTE, scales = "free_x", ncol=2)+
+
+AvesRiqTotal <- bind_rows((AvesInv_riq %>% mutate(Temporada = "Invierno")),(AvesPrim_riq %>% mutate(Temporada = "Primavera"))) %>% mutate(AMBIENTE = fct_relevel(AMBIENTE,"PLAYA NATURAL", "PLAYA INTERVENIDA", "ROQUERIO NATURAL", "ROQUERIO INTERVENIDO", "VERDE"))
+
+
[…]

### 2020-09-03 Exploración_enfocada.R
extra corr spearman

@@ -403,6 +403,18 @@ ggplot(Tidy_Prim_nmds2_bray)+
 
 
 
+##############EXTRA EXTRA
+data(varespec)
+data(varechem)
+sol <- bioenv(wisconsin(varespec) ~ log(N) + P + K + Ca + pH + Al, varechem)
+sol
+summary(sol)
+
+
+Bioenv1prim <- bioenv(wisconsin(AvesPrim2)~ `Cobertura vegetal`+ `Distancia a río`+Altura+ `Bosque nativo`+ Cultivos+ Grava + Oceano +Pastizales+ Matorrales+`Superficies impermeables` + `Suelo arenoso`+ `Plantacion de arboles`, Amb)
+summary(Bioenv1prim)
+
+
 #############################################################################################################################################
 # OCUPANCIAS: ocupando probabilidad de presencia por sitio
 

### 2020-09-08 Comportamiento_Aves.R
Generación de **Graficos_MediaSD.R** con graficos para presentacion, datos de especies desdde SIMPER-Contribucion a las diferencias entre ambientes

@@ -21,7 +21,7 @@ ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especi
   mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
          Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
          Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
-  group_by(AMBIENTE, Especie, Comportamiento) %>% summarise(Total_ind =n()) %>% ungroup() %>% 
+  group_by(AMBIENTE, Especie,  Comportamiento) %>% summarise(Total_ind =n()) %>% ungroup() %>% 
   dplyr::filter(Especie %in% c("CHURRETE COSTERO", "CORMORAN", "SCUA","BLANQUILLO","DIUCA","JOTE CABEZA ROJA","JOTE CABEZA NEGRA","PIQUERO", "PALOMA", "GAVIOTA" ))
    
 

### 2020-09-08 Graficos_MediaSD.R

@@ -1,0 +1,130 @@
+
+library(readxl)
+library(tidyverse)
+library(ggplot2)
+
+
+# ABUNDANCIA: Media de sitios por ambiente y sd
+
+## Invierno
+TotalInv1 <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+TotalInv1 <- TotalInv1 %>% dplyr::select(AMBIENTE, Sitio, Especie, N_individuos) %>% 
+    mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
+         Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
+  group_by(AMBIENTE,Sitio, Especie) %>% 
+  summarise(N_total = mean(N_individuos))%>% ungroup() %>% 
+  dplyr::filter(Especie %in% c("GARUMA","PELICANO COMÚN","CORMORAN","QUELTEHUE", "BLANQUILLO","JOTE CABEZA NEGRA", "ZORZAL","PALOMA"))
+
+BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
+BirdNames <- BirdNames %>%   rename(Cientifico = Especie, Especie =Nombre)
+
+TotalInv1 <- left_join(x=TotalInv1, y= BirdNames) 
+
+TotalInv1 <- TotalInv1 %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL")) %>% 
+  mutate(Especie=fct_relevel(Especie, "GARUMA","PELICANO COMÚN","CORMORAN","QUELTEHUE",  "BLANQUILLO","JOTE CABEZA NEGRA", "ZORZAL","PALOMA"))
+
+ggplot(TotalInv1, aes(x=AMBIENTE, y=N_total)) + 
+  geom_boxplot() + 
[…]

### 2020-09-08 Graficos_MediaSD.R
Arreglo de base de datos y grafico de medias para ocupancia por ambiente por especies significativas- inv y prim

@@ -22,7 +22,7 @@ BirdNames <- BirdNames %>%   rename(Cientifico = Especie, Especie =Nombre)
 TotalInv1 <- left_join(x=TotalInv1, y= BirdNames) 
 
 TotalInv1 <- TotalInv1 %>% 
-  mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL")) %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "PLAYA INTERVENIDA","ROQUERIO INTERVENIDO", "PLAYA NATURAL")) %>% 
   mutate(Especie=fct_relevel(Especie, "GARUMA","PELICANO COMÚN","CORMORAN","QUELTEHUE",  "BLANQUILLO","JOTE CABEZA NEGRA", "ZORZAL","PALOMA"))
 
 ggplot(TotalInv1, aes(x=AMBIENTE, y=N_total)) + 
@@ -51,7 +51,7 @@ BirdNames <- BirdNames %>%   rename(Cientifico = Especie, Especie =Nombre)
 TotalPrim1 <- left_join(x=TotalPrim1, y= BirdNames) 
 
 TotalPrim1 <- TotalPrim1 %>% 
-  mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL")) %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "PLAYA INTERVENIDA","ROQUERIO INTERVENIDO", "PLAYA NATURAL")) %>% 
   mutate(Especie=fct_relevel(Especie, "ZARAPITO","GARUMA","FRANKLIN","CHURRETE COSTERO","PALOMA","ZORZAL","CHERCAN","PELICANO COMÚN" ,"GOLONDRINA DORSO NEGRO",  "GAVIOTA"))
 
 ggplot(TotalPrim1, aes(x=AMBIENTE, y=N_total)) + 
@@ -62,69 +62,67 @@ ggplot(TotalPrim1, aes(x=AMBIENTE, y=N_total)) +
 ##############################################################################
 
 # OCUPANCIA: Media de sitios por ambiente y sd
-#
[…]

### 2020-09-09 Graficos_MediaSD.R
Se crearon graficos polares para representar las especies que contribuyen a las diferencias entre ambientes a partir de la riqueza de especies (simper-vegan)

@@ -4,32 +4,41 @@ library(tidyverse)
 library(ggplot2)
 
 
-# ABUNDANCIA: Media de sitios por ambiente y sd
+# RIQUEZA DE ESPECIES: Media de sitios por ambiente y sd
 
-## Invierno
-TotalInv1 <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-TotalInv1 <- TotalInv1 %>% dplyr::select(AMBIENTE, Sitio, Especie, N_individuos) %>% 
-    mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
+#PolaRRR
+
+#invierno
+
+TotalInv1 <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv")%>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL"))) %>% 
+  dplyr::select(AMBIENTE, Sitio, Especie, N_individuos) %>% 
+  group_by(AMBIENTE, Sitio, Especie) %>% 
+  summarise(N_individuos = sum(N_individuos)) %>% 
+  mutate(N_individuos = ifelse(N_individuos > 0, 1, 0)) %>% 
+  ungroup() %>% 
+  pivot_wider(names_from = Especie, values_from = N_individuos, values_fill = 0) %>% 
+  pivot_longer(BLANQUILLO:DIUCA, names_to = "Especie", values_to = "Presencia") %>% 
+  group_by(Especie, AMBIENTE) %>% 
+  summarise(N_Sitios = sum(Presencia))%>% 
+  mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
          Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
-         Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
-  group_by(AMBIENTE,Sitio, Especie) %>% 
[…]

### 2020-09-10 Comportamiento_Aves.R
Cambio en las especies seleccionadas para mostrar en los graficos de comportamiento de aves

@@ -22,7 +22,7 @@ ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especi
          Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
          Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
   group_by(AMBIENTE, Especie,  Comportamiento) %>% summarise(Total_ind =n()) %>% ungroup() %>% 
-  dplyr::filter(Especie %in% c("CHURRETE COSTERO", "CORMORAN", "SCUA","BLANQUILLO","DIUCA","JOTE CABEZA ROJA","JOTE CABEZA NEGRA","PIQUERO", "PALOMA", "GAVIOTA" ))
+  dplyr::filter(Especie %in% c("SCUA","JOTE CABEZA ROJA","DIUCA", "PALOMA","CORMORAN", "PIQUERO","QUELTEHUE", "GAVIOTA"))
    
 
 BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
@@ -32,11 +32,11 @@ ComportamientoInv <- left_join(x=ComportamientoInv, y= BirdNames)
 
 ComportamientoInv <- ComportamientoInv %>% 
   mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL")) %>% 
-  mutate(Especie=fct_relevel(Especie,"PIQUERO","JOTE CABEZA NEGRA", "CORMORAN",  "BLANQUILLO", "SCUA", "GAVIOTA", "JOTE CABEZA ROJA","PALOMA","CHURRETE COSTERO" ,"DIUCA"))
+  mutate(Especie=fct_relevel(Especie, "SCUA","JOTE CABEZA ROJA","DIUCA", "PALOMA","CORMORAN", "PIQUERO","QUELTEHUE", "GAVIOTA"))
 
 ggplot(ComportamientoInv) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento)) + 
-  facet_wrap(~Especie, ncol=5, scales = "free_y")+ theme_bw()+
[…]

### 2020-09-10 Analisis_Occu_punto/Occu37sp.R
Subida de nuevo archivo para GLM de aves- pregunta 0

@@ -443,11 +443,11 @@ PorSppTodo <- PorSppTodo %>% mutate(Origen= case_when(Especies %in% c("BLANQUILL
 #  facet_grid(cols=vars(Temporada)) +geom_vline(xintercept = 0, lty=3)+ theme_bw()
 
 ggplot(PorSppTodo, aes(x = Estimador, y = Parametro)) +  geom_boxplot(aes(color=Temporada))+
-  geom_vline(xintercept = 0, lty=3)+facet_grid(Origen~Temporada)+ theme_bw()
+  geom_vline(xintercept = 0, lty=3)+facet_grid(Origen~Temporada)+ theme_bw()+   ylab("Parametros")
 ###min
 
 ggplot(PorSppTodo, aes(x = Estimador, y = reorder(Parametro, Estimador, min))) +  geom_boxplot(aes(color=Temporada))+
-  geom_vline(xintercept = 0, lty=3)+facet_grid(Origen~Temporada)+ theme_bw()
+  geom_vline(xintercept = 0, lty=3)+facet_grid(Origen~Temporada)+ theme_bw()+ ylab("Variables ocupancia")
 
 ### Rango
 

### 2020-09-10 GLM_aves.R

@@ -1,0 +1,5 @@
+# Verificar diferencias no estacionales para aves
+#mediante GLMmixto x estación
+
+
+hacer glm

### 2020-09-11 Ms_HabitatAves.Rmd
Subida de ms_habitat aves con las preguntas y metodologia acordada para paper

---
title: "Ms Habitat aves"
author: "Giorgia Graells"
date: "9/10/2020"
output: word_document
---

```{r setup, include=FALSE, echo=FALSE, comment=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readxl)
library(tidyverse)
library(vegan)
library(MASS)
library(ggplot2)

```

### Preguntas:

- Cuáles son las especies y su composición en distintos lugares de las ciudades costeras. Existe interacción entre aves marinas y terrestres en espacios marinos y terrestres.

- Como afecta la urbanización en estos espacios, tanto marinos como terrestres?

- Para especies icónicas, cómo se distribuyen en el área de estudio

- Si el uso de espacio es diferenciado, su ubicación desntro de el también en términos de comportamiento?

### Metodología

0. La idea es hacer primero un GLM para ver el efecto de la estacion y ver cómo proceder
1. Hacer una descripcion del ensamble de especies (unidas las temporadas) y representar con un NMDS, ANOSIM y SIMPER.
Utilizar las abundancias corregidas por ocupancia.
Mostrar la comparacioón entre natural y urbano.
Sumar Envfit
2. Realizar un mapa dde probabilidad de presencia para especies icónicas 1-100%
3. Grafficar las barras de comportamiento para las mismas espcies icónicas

```{r figura1}

```

### 2020-09-11 GLM_aves.R
Analisis de glm completo para ver si la estacionalidad tiene un efecto

@@ -1,5 +1,36 @@
 # Verificar diferencias no estacionales para aves
 #mediante GLMmixto x estación
 
+library(tidyverse)
+library(lme4)
 
-hacer glm
+Inv  <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv")%>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
+Inv <- Inv %>% dplyr::select(AMBIENTE, Sitio, Especie, Dia_muestreo, N_individuos) %>%
+  mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
+         Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
+  group_by(AMBIENTE, Sitio, Especie, Dia_muestreo) %>% 
+  summarise(Abundancia = sum(N_individuos)) %>% 
+  mutate(Estacion="Invierno")
+
+AMB_nombres <-read_rds("Occdata_occu.rds") %>% dplyr::select(Sitio, AMBIENTE)
+Prim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")
+Prim <- left_join(Prim, AMB_nombres) 
+Prim <- Prim %>% dplyr::select(AMBIENTE, Sitio, Especie, Dia_muestreo, N_individuos) %>% 
+  mutate(Especie= str_replace(Especie, "PELICANO", "PELICANO COMÚN"),
+         Especie= str_replace(Especie, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Especie= str_replace(Especie, "LILEN", "LILE")) %>% 
+  mutate(AMBIENTE=str_replace(AMBIENTE,"ROCA INTERVENIDA", "ROQUERIO INTERVENIDO"),
+         AMBIENTE=str_replace(AMBIENTE,"ROCA NATURAL", "ROQUERIO NATURAL")) %>% 
+  group_by(AMBIENTE, Sitio, Especie, Dia_muestreo) %>% 
[…]

### 2020-09-18 Ms_HabitatAves.Rmd
Detalle para ocupancia
Empezando a escribir manuscrito

@@
 author: "Giorgia Graells"
-date: "9/10/2020"
-output: word_document
+date: "`r Sys.Date()`"
+output:
+  word_document:
+    reference_docx: "template.docx"
 ---
@@
 
-### Preguntas:
+#### Introduction
 
-- Cuáles son las especies y su composición en distintos lugares de las ciudades costeras. Existe interacción entre aves marinas y terrestres en espacios marinos y terrestres.
+##### objectives
 
-- Como afecta la urbanización en estos espacios, tanto marinos como terrestres?
+The aims of this study are: 1.
+Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2.
+identify how urbanization affects those bird assembles, 3.
+Evaluate iconic bird species habitat ocupation, and 4.
+describe bird behavior in those habitats
 
-- Para especies icónicas, cómo se distribuyen en el área de estudio
+#### Metodology
 
-- Si el uso de espacio es diferenciado, su ubicación desntro de el también en términos de comportamiento?
+##### Study area
 
-### Metodología
+Study area comprehends
+Six habitats were identify in coastal urban areas
 
-0. La idea es hacer primero un GLM para ver el efecto de la estacion y ver cómo proceder
+##### Bird surveys
+
+##### Environmental variables
+
+##### Seasonal GLMM
+
+Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
+We tested a model where seasonality has a interacttion with the habitats defined in this research .
+
+##### Occupancy modelling
+
+##### Bird comunnity
+
+Bird community was analysed by ordination methods with vegan package in R
+
 1. Hacer una descripcion del ensamble de especies (unidas las temporadas) y representar con un NMDS, ANOSIM y SIMPER.
-Utilizar las abundancias corregidas por ocupancia.
+Se utilizó las abundancias corregidas por ocupancia, lo que se obtiene corriendo los modelos de ocupancia para cada especie.
+
 Mostrar la comparacioón entre natural y urbano.
 Sumar Envfit
+
 2. Realizar un mapa dde probabilidad de presencia para especies icónicas 1-100%
+
 3. Grafficar las barras de comportamiento para las mismas espcies icónicas
 
-```{r figura1}
+#### Results
+
+0. El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia
+
+```{r tabla1}
+#Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
+#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0
 

### 2020-09-18 Exploración_enfocada.R

@@ -237,6 +237,10 @@ TidyEnvFit <- function(ENVFit, alpha = 0.05){
 }
 ###################################################
 EnvfitInv <- envfit(Inv_nmds1_bray~ `Cobertura vegetal`+ `Distancia a río`+Altura+ `Bosque nativo`+ Cultivos+ Grava + Oceano +Pastizales+ Matorrales+`Superficies impermeables` + `Suelo arenoso`+ `Plantacion de arboles`, data=Amb, perm=9999)
+
+#plot(Inv_nmds1_bray)
+#plot(EnvfitInv, p.max = 0.01)
+
 Tidy_EnvfitInv <- TidyEnvFit(EnvfitInv)
 
 library(ggplot2)

### 2020-09-22 Ms_HabitatAves.Rmd
Algunos avances del outline de la introduccion

@@
 date: "`r Sys.Date()`"
-output:
-  word_document:
-    reference_docx: "template.docx"
+output: word_document
 ---
@@
 
-##### objectives
+1. Establish importance of the fild- provide background, keywords- present the problem
 
-The aims of this study are: 1.
+[Stablish the importance of this research topic]
+Urbanization have been one of the mayor causes of species loss
+
+[Provide general background information]
+Urban areas presents species homogenization
+
+[Stablish the importance of this research topic, more specific/detailed way]
+Urban homogenization represents...
+
+[Provide general background information, more specific/detailed way]
+
+2. Previous an current research and contributions
+
+[Describe general problem area or the current research focus of the field]
+Birds have been studied un urban areas and show this phenomena
+
+[Provide transition between the general problem area and the literature review]
+Birs comunities in urban areas depend of the perurban composition of species
+
+3. Locate the gap-describe the proble to address-present a prediction to be tested
+
+[Provide brief overview of key research projects in this area]
+More than the half of the cities in the world are coastal cities
+
+[Describe gaps in the research]
+However there is a gap in studies that focus in coastal ecotone and the influence of antrhopized areas
+
+[Decribe paper itself]
+This research describe ...
+with the aim of: 1.
 Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2.
@@
 
+4. Describe the present paper
+[Give details about the methodology reported in the paper]
+Bird surveys were carry out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
+
+[Announces the findings]
+
 #### Metodology
+
+1. Overview-purpose of the work-give source of material/equipment used
+
+[General overview of this section]
+In this research we conducted bird survey in six coastal urban environments in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
+
+[Provide background information and justification]
+Each environment was defined in terms its proximity to the coast, level of anthropotization and land cover (Table 1)
+We used occupancy modeling to provide information about bird habitat use, taking into account probability of detection.
+
+[Provide an overview of the procedure/method itself]
+To compare bird commmunities and species identity in them, we used ordination models
+
+2. Details about materials and methods- justify choices
+
+[Provide details about what was done and used and shows that care was taken]
+
+[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
+
+3. Relate to other studies
+
+[Describe what was done by referring to existing mehods in the literature]
+
+[Provide more detailed information about the method and show that was a good choice]
+
+4. Indicate where problems occurred
+
+[Mention possible difficulty in the methodology]
 
@@
 
-#### Results
+### Results
 
-0. El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia
+1. Revisting the research aim/existing research
+
+2. General overview of results
+
+El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia
 
@@
 ```
+
+3. Invitations to view results
+
+4. Specific/key results in details
+
+5. Comparisons with results in other research
+
+6. problems with results
+
+7. Possible impllications with results
+
+### Discussion/Conclusion
+
+1. Revisting previous research- summarise
+[Revisit previous research]
+[Revisit Introduction to recall specific weakness in methodology used in previous studies]
+
+2. Mapping 
+[Revisit methodology used in this study]
+[Revisit and summarise the results]
+[Show where and how the present work fits into the research "map" in this field]
+
+3. Achivements/contributions- refining implications
+[Recall an aspect of the results that represents a postitive achievement or contribution of this work]
+[Focus in the meaning and implications of the achievements in this work]
+[Note if one of the achievement or contributions of the work is a novelty]
+[Describe implications of the results, including possible applications]
+
+4. Limitations-current and future work-applications
+[Describe limitations which should direct future research]
+[Suggest a specific area to be addressed in future work]

### 2020-09-24 CorrecDetec_Abundancias.R
Nuevo archivo para corregir abundancias por detección

@@ -1,0 +1,213 @@
+#Correccion abundancias aves por modelos de deteccion
+
+library(tidyverse)
+library(stringr)
+library(unmarked)
+library(MuMIn)
+library(caret)
+
+#Ocupancia para todas las especies en primavera
+
+data_det <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_detPrim.rds")
+
+data_ocu <-read_rds("Occdata_occu.rds")
+data_ocu <- data_ocu %>% dplyr::select(-Sitio)
+colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
+
+data_reg <-read_rds("Occdata_regPRIM.rds")
+
+
+batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
+  if(is.null(SppNames)){
+    SppNames <- paste("species", 1:spp, sep =".")
+  }
+  secuencia <- c(1:spp)*(ncol(pres)/spp)
+  secuencia2<-secuencia-(secuencia[1]-1)
+  models <- vector('list', spp)
+  fit <- matrix(NA, nrow(pres), spp)
+  Mods <- list()
+  if(is.null(SppNames)){
+    colnames(fit) <- paste("species", 1:spp, sep =".")
+  }else if(class(SppNames) == "character"){
+    colnames(fit) <- SppNames
+  }
+  if (dredge == FALSE) {
+    for(i in 1:length(secuencia)) {
+      data <- pres[, secuencia2[i]:secuencia[i]]
+      data2 <- unmarkedFrameOccu(y = data, siteCovs = sitecov, obsCovs = obscov)
+      try({
+        models[[i]] <- occu(as.formula(form), data2)
+      }, silent = T)
+      try({
+        fit[, i] <- suppressWarnings(predict(models[[i]], type = "state", newdata = sitecov))$Predicted
+      }, silent = T)
+      Mods = NULL
+      print(paste("Species", as.character(i), "ready!"))
+    }
+  }
+  else {
+    for(i in 1:length(secuencia)) {
+      data <- pres[, secuencia2[i]:secuencia[i]]
+      data2 <- unmarkedFrameOccu(y = data, siteCovs = sitecov, obsCovs = obscov)
+      try({
+        #Partimos en dos Detección y occupancia
+        form <- as.character(form)
[…]

### 2020-09-28 Ms_HabitatAves.Rmd
Correccion de abundancias por sitio por dia en base a probabilidad de deteccion.

@@
 [Provide brief overview of key research projects in this area]
-More than the half of the cities in the world are coastal cities
+More than the half of the cities in the world are coastal cities and they lack of studies addressing marine. terrestrial interactions.
 
@@
 [General overview of this section]
-In this research we conducted bird survey in six coastal urban environments in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
+In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area that includes three municipalities in central Chile.
 
 [Provide background information and justification]
-Each environment was defined in terms its proximity to the coast, level of anthropotization and land cover (Table 1)
-We used occupancy modeling to provide information about bird habitat use, taking into account probability of detection.
+Coastal environments were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1)
 
 [Provide an overview of the procedure/method itself]
-To compare bird commmunities and species identity in them, we used ordination models
+Bird surveys were conducted in each sample site twice (winter (junio-jul) and spring (nov-dec)), 2019 given migratory species en this area, during sunrise and the three hours later for 10 minutes. 
+The total of birds seing and heard was registred, in addition with the position and behavior of the bird or group of birds observed.
+
+A characterization of environments were made throgh vegetational cover measurement and an spatial characterization with landcover information.
 
@@
 
+Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
+We tested a model where seasonality has a interacttion with the habitats defined in this research .
+
+To analyse the data, we used occupancy modeling to provide information about bird habitat use.
+Occupancy variables
+Detection variables
+Seasonal variables
+
 [Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
+To compare bird commmunities and species identity in them, we used ordination methods with vegan package in R with species abundances corrected by occupancy.
+We tested significant differences among environments with an analysis of similarities (ANOSIM)
+
+To determine species contribution to the differrence between environments we used Bray-Curtis dissimilaries with SIMPER analysis.
 
@@
 [Provide more detailed information about the method and show that was a good choice]
+Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models
 
@@
 
-##### Study area
-
-Study area comprehends
-Six habitats were identify in coastal urban areas
-
-##### Bird surveys
-
-##### Environmental variables
-
-##### Seasonal GLMM
-
-Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
-We tested a model where seasonality has a interacttion with the habitats defined in this research .
-
-##### Occupancy modelling
-
-##### Bird comunnity
-
-Bird community was analysed by ordination methods with vegan package in R
+**Poner en paper**
 

### 2020-09-28 Analisis_Occu_punto/Prep datos_Occu_punto.R

@@ -121,6 +121,7 @@ for(x in 1:length(Datos)){
 OccDatav <- bind_cols(OccDatav)
 row.names(OccDatav) <- SITIOS
 
+#saveRDS(OccDatav, "Occdata_regPRIM_abund.rds")
 
 ## Cambiando para ocupacia/solo presencia y ausencias
 

### 2020-09-28 CorrecDetec_Abundancias.R

@@ -155,59 +155,27 @@ batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
 }
 
 
+Spp <- data_reg %>% colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
 
-DetPrim <- batchoccu(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=48,  form= ~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ 1, dredge=TRUE, SppNames =c("BLANQUILLO", "CACHUDITO", "CAHUIL", "CHERCAN", "CHINCOL", "CHURRETE_CHICO", "CHURRETE_COMUN", "CHURRETE_COSTERO", "CODORNIZ",
-                                                                                                                                                                             "COLEGIAL", "COMETOCINO", "CORMORAN", "COTORRA_ARGENTINA","DIUCA", "FIOFIO",  
-                                                                                                                                                                             "GAVIOTA_FRANKLIN","GAVIOTA_GARUMA", "GARZA_GRANDE","GAVIOTA", "GAVIOTIN_ELEGANTE",
-                                                                                                                                                                             "GOLONDRINA_CHILENA",  "GOLONDRINA_DORSO_NEGRO",  "GORRION", 
-                                                                                                                                                                             "GUANAY",  "HUAIRAVO", "HUALA", "JOTE_CABEZA_NEGRA", "JOTE_CABEZA_ROJA", 
-                                                                                                                                                                             "LILE",  "MIRLO", "GAVIOTIN_MONJA",  "PALOMA", "PELICANO", "PERRITO",  "PICAFLOR_GIGANTE",  
[…]

### 2020-09-30 Analisis_Occu_punto/Prep datos_Occu_punto.R
Arreglo de script que prepara capa de deteccion para ocupancia. Error en una hora de muestreo en sitio el litre

@@ -168,7 +168,9 @@ saveRDS(as.data.frame(cov_occu), "Occdata_ocu.rds")
 ## COVARIABLE DETECCIÓN: INVIERNO 2019
 
 cov_occu <- read_rds("Occdata_ocu.rds")
-cov_det <- read_csv("G:/Mi unidad/Documentos Yoryi/Documents yoryi/Doctorado Tesis/Monitoreo aves/Muestreo Aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves.csv") %>% select(Sitio, Observador, Fecha_muestreo, Nubosidad, Neblina, Lluvia, Hora_muestreo, Presencia_otros, Presencia_perros, Nivel_trafico, Dia_muestreo) %>% distinct() %>% mutate(Hora_muestreo = as.character(Hora_muestreo)) %>% filter(Sitio %in% cov_occu$Sitio)
+cov_det <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::select(Sitio, Observador, Fecha_muestreo, Nubosidad, Neblina, Lluvia, Hora_muestreo, Presencia_otros, Presencia_perros, Nivel_trafico, Dia_muestreo) %>% 
+  distinct() %>% mutate(Hora_muestreo = as.character(Hora_muestreo)) %>% filter(Sitio %in% cov_occu$Sitio)
 
 
 ##Hacemos un gather dejando el sito
@@ -181,10 +183,9 @@ Variables <- cov_det2 %>% purrr::map(~summarise(.x, Variable = unique(Variable))
 cov_det3 <- list()
 
 for(i in 1:length(cov_det2)){
-  temp <- cov_det2[[i]] %>% group_split(Sitio)
-  
+  temp <- cov_det2[[i]] %>% group_split(Sitio) %>% map(~dplyr::select(.x,Valor))
+
   for(j in 1:length(temp)){
-    temp[[j]] <- temp[[j]] %>% dplyr::select(-Sitio, -Variable)
     temp[[j]] <- data.frame(Variables1 = temp[[j]][1,], Variables2 = temp[[j]][2,], Variables3 = temp[[j]][3,])
[…]

### 2020-09-30 Analisis_Occu_punto/Prep datos_Occu_punto.R
Correccion de variables de deteccion primavera e invierrno

@@ -199,12 +199,12 @@ names(cov_det3) <- Variables
 cov_det3$Fecha_muestreo <- cov_det3$Fecha_muestreo %>% mutate_all(lubridate::dmy)
 cov_det3$Hora_muestreo <- cov_det3$Hora_muestreo %>% mutate_all(hms::as.hms)
 
-saveRDS(cov_det3, "Occdata_detInv.rds")
+saveRDS(cov_det3, "cov_det3Inv.rds")
 
 #######################################################
 #Agregando más datos historicos descargados de https://climatologia.meteochile.gob.cl
 
-deteccion <- read_rds("Occdata_detInv.rds")
+deteccion <- read_rds("cov_det3Inv.rds")
 
 
 
@@ -311,8 +311,8 @@ saveRDS(deteccion, "Occdata_detInv.rds")
 ## COVARIABLE DETECCION: PRIMAVERA 2019
 
 cov_occu <- read_rds("Occdata_ocu.rds")
-cov_det <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv") %>% 
-  select(Sitio, Observador, Fecha_muestreo, Nubosidad, Neblina, Lluvia, Hora_muestreo, Presencia_pescadores, Presencia_lobos, Presencia_perros, Nivel_trafico, Dia_muestreo) %>% 
+cov_det <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv") %>% 
+  dplyr::select(Sitio, Observador, Fecha_muestreo, Nubosidad, Neblina, Lluvia, Hora_muestreo, Presencia_pescadores, Presencia_lobos, Presencia_perros, Nivel_trafico, Dia_muestreo) %>% 
   distinct() %>% mutate(Hora_muestreo = as.character(Hora_muestreo), Fecha_muestreo = as.character(Fecha_muestreo)) %>% 
   filter(Sitio %in% cov_occu$Sitio)
 
@@ -326,10 +326,9 @@ Variables <- cov_det2 %>% purrr::map(~summarise(.x, Variable = unique(Variable))
 cov_det3 <- list()
 
[…]

### 2020-09-30 CorrecDetec_Abundancias.R
Correccion de script utilizando los datos arreglados de deteccion. Se corrió acopancia y se corrigió la abundancia a partir de la deteccion para invierrno y prim

@@ -6,6 +6,8 @@ library(unmarked)
 library(MuMIn)
 library(caret)
 
+
+####DATOS PRIMAVERA
 #Ocupancia para todas las especies en primavera
 
 data_det <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_detPrim.rds")
@@ -15,7 +17,6 @@ data_ocu <- data_ocu %>% dplyr::select(-Sitio)
 colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
 
 data_reg <-read_rds("Occdata_regPRIM.rds")
-
 
 batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
   if(is.null(SppNames)){
@@ -159,7 +160,6 @@ Spp <- data_reg %>% colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>
 
 DetPrim <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=48,  form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ 1", dredge=TRUE, SppNames = Spp)
 
-
 Detecciones <- list()
 
 for(i in 1:length(DetPrim$models)){
@@ -168,10 +168,9 @@ for(i in 1:length(DetPrim$models)){
 }
 
 
-
 Detecciones <- Detecciones %>% reduce(bind_cols)
 
-rownames(Detecciones) <- rownames(AbundPrim_dia)
+rownames(Detecciones) <- rownames(data_reg)
 
 ### Correccion de abundancias
 
@@ -179,3 +178,178 @@ AbundPrim_dia <-read_rds("Occdata_regPRIM_abund.rds")
 
 AbundPrim_Corregido <- AbundPrim_dia/Detecciones
 saveRDS(AbundPrim_Corregido, "AbundPrim_Corregido.rds")
+################################################################
+
+####DATOS INVIERNO
+#Ocupancia para todas las especies en invierno
+
+data_det <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_detInv.rds")
+
+data_ocu <-read_rds("Occdata_occu.rds")
[…]

### 2020-10-01 Analisis_Occu_punto/Prep datos_Occu_punto.R
Arreglo del codigo, avance en textto y orden de rmd habita aves, pero hay q arreglar el codigo aun porque parque el litre tiene mas las abundancias

@@ -60,6 +60,7 @@ for(x in 1:length(Datos)){
 OccData <- bind_cols(OccData)
 row.names(OccData) <- SITIOS
 
+saveRDS(OccData, "Occdata_regInv_abund.rds")############################ aca quedde
 
 ## Cambiando para ocupacia/solo presencia y ausencias
 

### 2020-10-05 Analisis_Occu_punto/Prep datos_Occu_punto.R
Correccion de datos en preparacion de capas para deteccion (con datos de abundancia para prim y verano). Correccion de datos de archivo CorrDet_Abundancias. para ambas estaciones.

@@ -60,7 +60,7 @@ for(x in 1:length(Datos)){
 OccData <- bind_cols(OccData)
 row.names(OccData) <- SITIOS
 
-saveRDS(OccData, "Occdata_regInv_abund.rds")############################ aca quedde
+#saveRDS(OccData, "Occdata_regInv_abund.rds") #datos abundancia invierno para hacer analisis con abundancia corregida por deteccion
 
 ## Cambiando para ocupacia/solo presencia y ausencias
 
@@ -122,7 +122,7 @@ for(x in 1:length(Datos)){
 OccDatav <- bind_cols(OccDatav)
 row.names(OccDatav) <- SITIOS
 
-#saveRDS(OccDatav, "Occdata_regPRIM_abund.rds")
+#saveRDS(OccDatav, "Occdata_regPRIM_abund.rds")#para hacer analisis de abundancias corregidas por deteccion
 
 ## Cambiando para ocupacia/solo presencia y ausencias
 

### 2020-10-05 CorrecDetec_Abundancias.R

@@ -6,7 +6,6 @@ library(unmarked)
 library(MuMIn)
 library(caret)
 
-
 ####DATOS PRIMAVERA
 #Ocupancia para todas las especies en primavera
 
@@ -174,10 +173,19 @@ rownames(Detecciones) <- rownames(data_reg)
 
 ### Correccion de abundancias
 
-AbundPrim_dia <-read_rds("Occdata_regPRIM_abund.rds")
+AbundPrim_dia <-read_rds("Occdata_regPRIM_abund.rds") #se debe considerar la abundancia de cada sp por sitio
 
 AbundPrim_Corregido <- AbundPrim_dia/Detecciones
-saveRDS(AbundPrim_Corregido, "AbundPrim_Corregido.rds")
+  
+AbundPrim_Corregido2 <- AbundPrim_Corregido %>% 
+  mutate(Sitio = row.names(AbundPrim_Corregido)) %>% 
+  pivot_longer(cols = -Sitio, names_to = "Especie", values_to = "Abundancia") %>% 
+  mutate(Especie = str_remove_all(Especie, "1"), Especie = str_remove_all(Especie, "2"), Especie = str_remove_all(Especie, "3")) %>% 
+  group_by(Sitio, Especie) %>% 
+  summarise(Abundancia = mean(Abundancia, na.rm = T)) %>% 
+  pivot_wider(names_from = Especie, values_from = Abundancia)
+
+saveRDS(AbundPrim_Corregido2, "AbundPrim_Corregido.rds")
 ################################################################
 
 ####DATOS INVIERNO
@@ -341,15 +349,23 @@ for(i in 1:length(DetInv$models)){
   colnames(Detecciones[[i]]) <- paste0(names(DetInv$models)[i],"_",c("Dia1", "Dia2", "Dia3"))
 }
 
-
-
 Detecciones <- Detecciones %>% reduce(bind_cols)
 
 rownames(Detecciones) <- rownames(data_reg)
 
 ### Correccion de abundancias
 
-AbundInv_dia <-read_rds("Occdata_regInv.rds")
-
+AbundInv_dia <-read_rds("Occdata_regInv_abund.rds")
 AbundInv_Corregido <- AbundInv_dia/Detecciones
+
+AbundInv_Corregido[14,seq(3,ncol(AbundInv_Corregido), by = 3)] <- NA #solo para invierno
+
+AbundInv_Corregido2 <- AbundInv_Corregido %>% 
[…]

### 2020-10-06 Ms_HabitatAves.Rmd
Arreglo del codigo, avance en textto y orden de rmd habita aves, pero hay q arreglar el codigo aun porque parque el litre tiene mas las abundancias
ultimos cambios, analisis comunitario listo

@@
 library(ggplot2)
+library(ggrepel)
 
+```
+
+```{r}
+#preparacion de datos registro aves
+
+AvesInv2 <- read_rds("AbundInv_Corregido.rds") 
+AvesInv2 <-AvesInv2 %>% ungroup() %>% dplyr::select(-Sitio) %>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+AvesPrim2 <- read_rds("AbundPrim_Corregido.rds")
+AvesPrim2 <-AvesPrim2 %>% ungroup() %>% dplyr::select(-Sitio)%>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+#Datos ambientales  incluidos buffers
+
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+Amb <- Amb %>% 
+  dplyr::select(Sitio,CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>%
+  rename( `Cobertura vegetal` =CobVeg) %>% rename( `Distancia a río` =Distancia_rio) %>% 
+  rename( `Bosque nativo` =`Buffer_2200_Bosque Nativo`) %>% rename( Cultivos =`Buffer_2200_Cultivos`) %>% 
+  rename( Grava =`Buffer_2200_Grava`) %>% rename( Oceano =`Buffer_2200_Oceano`) %>% 
+  rename( Pastizales =`Buffer_2200_Pastizales`) %>% rename( `Matorrales` =`Buffer_2200_Matorrales`) %>% 
+  rename( `Superficies impermeables` =`Buffer_2200_Sup impermeables`) %>% rename( `Suelo arenoso` =`Buffer_2200_Suelo arenoso`) %>% 
+  rename( `Plantacion de arboles` =`Buffer_2200_Plantación de árboles`)
+
+rownames(Amb) <- Amb$Sitio
+
+Amb <- Amb %>% dplyr::select(-Sitio)
 ```
@@
 2. General overview of results
+A partir del nmds
 
@@
 3. Invitations to view results
+variabilidad entre ambientes segun anosim
 
 4. Specific/key results in details
+que contribuye mas al cambio
+que determina las diferencias
 

### 2020-10-06 README.Rmd
Funcion nueva para envfit y sacar datos para grafico en ggplot nuevo archivo comportamineto aves
subida de readme en rmd y md
Subida de nuevo archivo para GLM de aves- pregunta 0
ultimos cambios, analisis comunitario listo

@@
 modificacion de parametros de distintas funciones para su correcto uso
+
+Creacion de archivo **Comportamineto_Aves.R** para resumen de actividades
+Creación de archivo **Graficos_Aves.R** para diferencias entre ambientes, considerando media de sitios y sd
+
+#Correccion de abundancia por deteccion
+
+Nuevo archivo **CorrecDetec_Abundancias.R** elementos exportados: AbundanciaPrim_corregido.rds y AbundanciaInv_corregido.rds
+En el archivo Prep datos_Occu_punto.R se exportaron las abundancias en formato de sitios por dia para hacer el calculo de la correccion.
+Se modifica tambien la importacion de este nuevo dataframe para hacer los analisis de la comunidad

### 2020-10-06 CorrecDetec_Abundancias.R

@@ -368,4 +368,4 @@ AbundInv_Corregido2 <- AbundInv_Corregido %>%
   summarise(Abundancia = mean(Abundancia, na.rm = T)) %>% 
   pivot_wider(names_from = Especie, values_from = Abundancia)
 
-saveRDS(AbundInv_Corregido, "AbundInv_Corregido.rds")
+saveRDS(AbundInv_Corregido2, "AbundInv_Corregido.rds")

### 2020-10-08 Ms_HabitatAves.Rmd
arreglo de figuras en manuscrito

--- 2020-09-28 Ms_HabitatAves.Rmd
@@
 date: "`r Sys.Date()`"
-output: word_document
+output:
+  word_document: default
   ---
 
-```{r setup, include=FALSE, echo=FALSE, comment=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE,	message = FALSE,warning = FALSE,cache = TRUE,comment = FALSE)
 
@@
 library(ggplot2)
+library(ggrepel)
+library(patchwork)
+library(kableExtra)
 
+```
+
+```{r}
+#preparacion de datos registro aves
+
+AvesInv2 <- read_rds("AbundInv_Corregido.rds") 
+AvesInv2 <-AvesInv2 %>% ungroup() %>% dplyr::select(-Sitio) %>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+AvesPrim2 <- read_rds("AbundPrim_Corregido.rds")
+AvesPrim2 <-AvesPrim2 %>% ungroup() %>% dplyr::select(-Sitio)%>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+#Datos ambientales  incluidos buffers
+
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+Amb <- Amb %>% 
+  dplyr::select(Sitio,CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>%
+  rename( `Vegetation cover` =CobVeg) %>% rename( `Distance to river` =Distancia_rio) %>% 
+  rename( `Native forest` =`Buffer_2200_Bosque Nativo`) %>% rename(Crops =`Buffer_2200_Cultivos`) %>% 
+  rename( Gravel =`Buffer_2200_Grava`) %>% rename( Ocean =`Buffer_2200_Oceano`) %>% 
+  rename( Grassland =`Buffer_2200_Pastizales`) %>% rename( `Shrublands` =`Buffer_2200_Matorrales`) %>% 
+  rename( `Paved surface` =`Buffer_2200_Sup impermeables`) %>% rename( `Sand` =`Buffer_2200_Suelo arenoso`) %>% 
+  rename( `Tree plantation` =`Buffer_2200_Plantación de árboles`) %>% 
+  rename( Altitude = Altura)
+
+rownames(Amb) <- Amb$Sitio
+
+Amb <- Amb %>% dplyr::select(-Sitio)
 ```
@@
 [Suggest a specific area to be addressed in future work]
+
+```{r, results='hide'}
+##### METAMDS: Non-metric Multidimensional scaling- NMDS
+
+#########################################################
+#Función para sacar los datos y ocupar ggplot
+TidyNMDS <- function(MDS, COVS){
+  DF <- COVS
+  DF2 <- MDS$points %>% as.data.frame()
+  DF <- bind_cols(DF2, DF)
+  return(DF = DF)
+}
+#########################################################
+#Invierno
+Inv_nmds2_bray <- suppressMessages(metaMDS(AvesInv2, autotransform = FALSE, distance="bray", k=2, try=20, trymax=100,  wascores=FALSE, trace=1, plot=FALSE))
+#Primavera
+Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
+```
+
+```{r, fig.width=9, fig.height=4}
+#Funcion para grafico NMDS en ggplot Invierno
+Tidy_Inv_nmds2_bray <- TidyNMDS(MDS = Inv_nmds2_bray, COVS = Amb)
+
+Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
+  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area") , values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+  ggtitle('A')
+
+#Funcion para grafico NMDS en ggplot Primavera
+Tidy_Prim_nmds2_bray <- TidyNMDS(MDS = Prim_nmds2_bray, COVS = Amb)
+
+Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
+  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"), values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+  ggtitle('B')
+
+#Ambos graficos con patchwork
+Inv+Prim + plot_layout(guides = 'collect')
+```
+
+```{r, results='hide'}
+## test: ANOSIM
+
+#Invierno
+Diss_Inv2 <- vegdist(AvesInv2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
+#con base de datos por abundancia
+Anosim_Diss_Inv2<-anosim(Diss_Inv2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", strata = NULL, parallel = getOption("mc.cores"))
+Summ_AnosimInv <-summary(Anosim_Diss_Inv2)
+
+#Primavera
+Diss_Prim2 <- vegdist(AvesPrim2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
+#con base de datos por abundancia
+Anosim_Diss_Prim2<-anosim(Diss_Prim2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray",strata = NULL, parallel = getOption("mc.cores")) 
+summary(Anosim_Diss_Prim2)
+
+```
+
+```{r, fig.width=9}
+Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
+  xlab("Variables")+ ylab("Dissimmilarity rank")+
+  ggtitle('A')
+
+Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
+ xlab("Variables")+ ylab("Dissimmilarity rank")+
+   ggtitle('B')
+
+Inv / Prim
+```
+
+```{r, results='hide'}
+##### ENVFIT: Fits an Environmental Vector or Factor onto an Ordination
+###################################################
+TidyEnvFit <- function(ENVFit, alpha = 0.05){
+  DF <- ENVFit$vectors$arrows %>% as.data.frame()
+  DF$Factor <- rownames(DF)
+  DF$Pval <-ENVFit$vectors$pvals
+  DF <- DF %>% dplyr::filter(Pval < alpha)
+  return(DF = DF)
+}
+###################################################
+EnvfitInv2 <- envfit(Inv_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation` , data=Amb, perm=9999)
+Tidy_EnvfitInv2 <- TidyEnvFit(EnvfitInv2)
+
+EnvfitPrim2 <- envfit(Prim_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation`, data=Amb, perm=9999)
+Tidy_EnvfitPrim2 <- TidyEnvFit(EnvfitPrim2)
+```
+
+```{r,  fig.width=9, fig.height=4}
+Inv <- ggplot(Tidy_Inv_nmds2_bray)+
+  geom_segment(data=Tidy_EnvfitInv2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
+  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
+  geom_text_repel(data=Tidy_EnvfitInv2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
+
+  theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
+  ggtitle('A')
+
+Prim <- ggplot(Tidy_Prim_nmds2_bray)+
+  geom_segment(data=Tidy_EnvfitPrim2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
+  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
+  geom_text_repel(data=Tidy_EnvfitPrim2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
+    theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
+  ggtitle('B')
+
+Inv+Prim + plot_layout(guides = 'collect')
+
+```
+
+### References

### 2020-10-09 Ms_HabitatAves.Rmd
Avance en introduccion y metodologia

@@
 ---
-title: "Ms Habitat aves"
+title: "Ms Habitat aves. Species composition in coastal urban habitats"
 author: "Giorgia Graells"
@@
   output:
-  word_document: default
+    bookdown::word_document2:
+      fig_caption: true 
+bibliography: tesis_ref_2020.bib
 ---
@@
 library(kableExtra)
+library(knitr)
 
@@
 [Stablish the importance of this research topic]
-Urbanization have been one of the mayor causes of species loss
+
+Urbanization have been growing rapidly ...
+and is one of the mayor causes of species loss [@czech2000economic].
 
 [Provide general background information]
-Urban areas presents species homogenization
+Urban modificacion over natural environments has promoted loss of native species and their replacement by non-native species [@mckinney2006urbanization].
+This is called biotic homogenization, where few species are adapted to urban and suburban conditions [@mckinney1999biotic].
+Biotic homogenization affects variety of ecosystems [grassland: @zeeman2017biotic], climates [temperate: @zeeman2017biotic],taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic]
 
 [Stablish the importance of this research topic, more specific/detailed way]
-Urban homogenization represents...
+This urban homogenization has effects: 
+a. more homogenized biosfera with lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
+which has been studied mostly in birds and plants
 
 [Provide general background information, more specific/detailed way]
+In birds, urban homogenization in more specific: has a nonrandom filtering effect on birds, they show guildsresponse to urbanization [@silva2016nonrandom].
+Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
+Rural birds
+According to @clergeau2001urban, urban  bird  communities  are  independent of the bird diversity of adjacent landscapes, and that local features are more important than surrounding landscapes.
 
@@
 [Describe general problem area or the current research focus of the field]
-Birds have been studied un urban areas and show this phenomena
+half of population live in coastal cities, however urbanization has been msotly focus in terrestiral aspects.
 
 [Provide transition between the general problem area and the literature review]
-Birs comunities in urban areas depend of the perurban composition of species
+More than the half of the cities in the world are coastal cities and they lack of studies addressing marine and terrestrial interactions.
 
@@
 [Provide brief overview of key research projects in this area]
-More than the half of the cities in the world are coastal cities and they lack of studies addressing marine. terrestrial interactions.
+Urban homogenization has been studied in cities, focused in terrestrial variables
+Considering Birs comunities in urban areas depend of the perurban composition of species, there are no studies in the effects of marine habitats
 
 [Describe gaps in the research]
-However there is a gap in studies that focus in coastal ecotone and the influence of antrhopized areas
+There is a gap in studies that focus in coastal ecotone and the influence of antrhopized areas
+focusing on marine and terrestrial interaction of species in an urbanized area and how birds use this as habitats
 
 [Decribe paper itself]
-This research describe ...
+This research aim to identified the use of coastal urban habitats by birds describing the composition of species in differrent environments, considering bird species origin (marine and terrestrial).
 with the aim of: 1.
@@
 [Give details about the methodology reported in the paper]
-Bird surveys were carry out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
+The present study was carried out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
 
 [Announces the findings]
+Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inlsnd bird species
 
@@
 [General overview of this section]
-In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area that includes three municipalities in central Chile.
+In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area in Central Chile.
+We estimated species composition based on bird presence analised using occupancy models.
 
 [Provide background information and justification]
-Coastal environments were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1)
+Coastal central chile present a rapid urbanization growth since the last... years, endengering natural habitats. 
+The area is near by the chilean capital which has close to 6 million inhabitants.
+This area is inmerse ina a natural-rural matrix composed ... in a grographic Coastal mountain chain-- papers bahi concon y viña
 
 [Provide an overview of the procedure/method itself]
-Bird surveys were conducted in each sample site twice (winter (junio-jul) and spring (nov-dec)), 2019 given migratory species en this area, during sunrise and the three hours later for 10 minutes. 
-The total of birds seing and heard was registred, in addition with the position and behavior of the bird or group of birds observed.
-
-A characterization of environments were made throgh vegetational cover measurement and an spatial characterization with landcover information.
+species composition were analised with the package vegan for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
 
@@
 [Provide details about what was done and used and shows that care was taken]
+Six coastal habitat were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1).
+Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
+Surveys were conducted randomly during sunrise and the three hours later for 10 minutes, registering species and behaviour.
 
 Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
-We tested a model where seasonality has a interacttion with the habitats defined in this research .
-
-To analyse the data, we used occupancy modeling to provide information about bird habitat use.
-Occupancy variables
-Detection variables
-Seasonal variables
+We tested a model where seasonality has a interacttion with the habitats defined in this research.
 
 [Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-To compare bird commmunities and species identity in them, we used ordination methods with vegan package in R with species abundances corrected by occupancy.
-We tested significant differences among environments with an analysis of similarities (ANOSIM)
-
-To determine species contribution to the differrence between environments we used Bray-Curtis dissimilaries with SIMPER analysis.
+Bird commmunities were analised using ordination methods with vegan package in R with species abundances corrected by detection capacity, using occupancy models (see table) [].
+We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
+To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
+Fit of environmental variables on species ordination was also tested. 
+Bird behabiour was counted for each habitat.
 
@@
 [Describe what was done by referring to existing mehods in the literature]
+To independize us from habitats already defined, ocupancy models of eight species were analize. Same species' presences were related to its behaviour detected in those habitats
 
 [Provide more detailed information about the method and show that was a good choice]
-Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models
+Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models, we used corrected abundance from probability of detection for comunity analissi
 
@@
 [Mention possible difficulty in the methodology]
-
-**Poner en paper**
-
-1. Hacer una descripcion del ensamble de especies (unidas las temporadas) y representar con un NMDS, ANOSIM y SIMPER.
-Se utilizó las abundancias corregidas por ocupancia, lo que se obtiene corriendo los modelos de ocupancia para cada especie.
-
-Mostrar la comparacioón entre natural y urbano.
-Sumar Envfit
-
-2. Realizar un mapa dde probabilidad de presencia para especies icónicas 1-100%
-
-3. Grafficar las barras de comportamiento para las mismas espcies icónicas
 
@@
 2. General overview of results
-A partir del nmds
+Bird surveys in the study area detected
+
+A partir del nmds \@ref(Figure:NMDS)
 
@@
 
-```{r, fig.width=9, fig.height=4}
+```{r, fig.width=9, fig.height=4, fig.cap="NMDS"}
 #Funcion para grafico NMDS en ggplot Invierno
@@
 
-#Ambos graficos con patchwork
+#Ambos graficos con paquete patchwork
 Inv+Prim + plot_layout(guides = 'collect')
@@
 Inv / Prim
+```
+
+```{r}
+#Tabla Simper Inv
+
+Inv <-  read.csv("ResumenSimper_Inv2.csv")
+
+knitr::kable(
+  list(Inv[1:28, ], longtable = TRUE, booktabs = TRUE
+       ))
+
+```
+
+```{r}
+#Tabla Simper Inv
+Prim <-  read.csv("ResumenSimper_Prim2.csv")
+
+knitr::kable(
+  list(Prim[1:30, ], longtable = TRUE, booktabs = TRUE
+       ))
+```
+
+```{r}
+# set pander table-layout options
+library(pander)
+Prim <-  read.csv("ResumenSimper_Prim2.csv")
+Prim<- as.data.frame(Prim)
+panderOptions('table.alignment.default', function(Prim)
+    ifelse(sapply(Prim, is.numeric), 'right', 'left'))
+panderOptions('table.split.table', Inf)
+panderOptions('big.mark', ",")
+panderOptions('keep.trailing.zeros', TRUE)
+
+pander(Prim)
+
 ```

### 2020-10-16 Ms_HabitatAves.Rmd
Avance en manuscrito, se corrió ocupnacia para sp obtenidas por simper

@@
 title: "Ms Habitat aves. Species composition in coastal urban habitats"
-author: "Giorgia Graells"
-  date: "`r Sys.Date()`"
 output:
   bookdown::word_document2:
-      fig_caption: true 
+    reference_docx: "Para_Template.docx"
 bibliography: tesis_ref_2020.bib
@@
 
-#### Introduction
+### Introduction
 
@@
 
-#### Metodology
+### Metodology
+
+```{r, results='hide'}
+##### METAMDS: Non-metric Multidimensional scaling- NMDS
+
+#########################################################
+#Función para sacar los datos y ocupar ggplot
+TidyNMDS <- function(MDS, COVS){
+  DF <- COVS
+  DF2 <- MDS$points %>% as.data.frame()
+  DF <- bind_cols(DF2, DF)
+  return(DF = DF)
+}
+#########################################################
+#Invierno
+Inv_nmds2_bray <- suppressMessages(metaMDS(AvesInv2, autotransform = FALSE, distance="bray", k=2, try=20, trymax=100,  wascores=FALSE, trace=1, plot=FALSE))
+#Primavera
+Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
+```
 
@@
 [Provide details about what was done and used and shows that care was taken]
-Six coastal habitat were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Table 1).
+Six coastal habitat were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1).
 Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
@@
 [Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-Bird commmunities were analised using ordination methods with vegan package in R with species abundances corrected by detection capacity, using occupancy models (see table) [].
+Bird commmunities were analised using ordination methods with vegan package in R with species abundances corrected by detection capacity, using occupancy models (see table 1).
 We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
@@
 [Describe what was done by referring to existing mehods in the literature]
-To independize us from habitats already defined, ocupancy models of eight species were analize. Same species' presences were related to its behaviour detected in those habitats
+To independize our analysis from habitats already defined, ocupancy models of eight species were developed and projected over the study area
 
 [Provide more detailed information about the method and show that was a good choice]
-Occupancy models provide a correction using detection probability mong days and colonization-extinction probability between seasons which improve ordination models, we used corrected abundance from probability of detection for comunity analissi
+Covariables of detection and occupation are describedd in table 1.
 
@@
 
+```{r}
+#figura 1 con los 6 ambientes costeros estudiados
+```
+
+```{r}
+#Covariables de deteccion y ocupaciono ocupadas para los modelos
+```
+
 ### Results
@@
 1. Revisting the research aim/existing research
+Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.
 
 2. General overview of results
-Bird surveys in the study area detected
+The six coastal urban habitats shows distingible birs species assembles where only a few species contribute to the difference between them.
+For these habitats, bird assemblages differ between winter and spring seasons.
 
-A partir del nmds \@ref(Figure:NMDS)
-
-El menor valor de AIC determina que la estacion si teiene una interaccion con las especies para definir la abundancia
-
-```{r tabla1}
+```{r tabla3}
 #Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
@@
 3. Invitations to view results
-variabilidad entre ambientes segun anosim
+
+Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla 3).
+Distribution of sites in graphical NMDS (Fig.
+\@ref(fig:NMDS)) showed both seassons presented differences in abundance of species mostly in the inland sites.
+Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
+
+```{r NMDS, fig.width=9, fig.height=4, fig.cap="Sites distribution in A winter and B spring"}
+#Funcion para grafico NMDS en ggplot Invierno
+Tidy_Inv_nmds2_bray <- TidyNMDS(MDS = Inv_nmds2_bray, COVS = Amb)
+
+Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
+  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area") , values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+  ggtitle('A')
+
+#Funcion para grafico NMDS en ggplot Primavera
+Tidy_Prim_nmds2_bray <- TidyNMDS(MDS = Prim_nmds2_bray, COVS = Amb)
+
+Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
+  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"), values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+  ggtitle('B')
+
+#Ambos graficos con paquete patchwork
+Inv+Prim + plot_layout(guides = 'collect')
+```
+
+Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats.
+There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
+\@ref(fig:ANOSIM))
+
+```{r, results='hide'}
+## test: ANOSIM
+
+#Invierno
+Diss_Inv2 <- vegdist(AvesInv2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
+#con base de datos por abundancia
+Anosim_Diss_Inv2<-anosim(Diss_Inv2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", strata = NULL, parallel = getOption("mc.cores"))
+Summ_AnosimInv <-summary(Anosim_Diss_Inv2)
+
+#Primavera
+Diss_Prim2 <- vegdist(AvesPrim2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
+#con base de datos por abundancia
+Anosim_Diss_Prim2<-anosim(Diss_Prim2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray",strata = NULL, parallel = getOption("mc.cores")) 
+summary(Anosim_Diss_Prim2)
+
+```
+
+```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A winter and B spring"}
+Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
+  xlab("Variables")+ ylab("Dissimmilarity rank")+
+  ggtitle('A')
+
+Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
+ xlab("Variables")+ ylab("Dissimmilarity rank")+
+   ggtitle('B')
+
+Inv / Prim
+```
 
 4. Specific/key results in details
-que contribuye mas al cambio
-que determina las diferencias
+
+There is just few species that contribute to differences between habitats.
+During winter: *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*.
+And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (Fig.
+\@ref(fig:SIMPER1), Fig.
+\@ref(fig:SIMPER2)).
+
+```{r SIMPER1, fig.cap="Simper analysis for winter"}
+# set pander table-layout options
+library(pander)
+Inv <-  read.csv("ResumenSimper_Inv2.csv")
+Inv<- as.data.frame(Inv)
+panderOptions('table.alignment.default', function(Inv)
+    ifelse(sapply(Inv, is.numeric), 'right', 'left'))
+panderOptions('table.split.table', Inf)
+panderOptions('big.mark', ",")
+panderOptions('keep.trailing.zeros', TRUE)
+
+pander(Inv)
+#Inv$Especie
+```
+
+```{r SIMPER2, fig.cap="Simper analysis for spring"}
+# set pander table-layout options
+library(pander)
+Prim <-  read.csv("ResumenSimper_Prim2.csv")
+Prim<- as.data.frame(Prim)
+panderOptions('table.alignment.default', function(Prim)
+    ifelse(sapply(Prim, is.numeric), 'right', 'left'))
+panderOptions('table.split.table', Inf)
+panderOptions('big.mark', ",")
+panderOptions('keep.trailing.zeros', TRUE)
+
+pander(Prim)
+
+```
+
+During winter, community assemblages were explain by three environmental variables: coastal urban habitats, crops and tree plantations. 
+In spring, variables were coastal urban habitats and native forest.
+
+species for each habitat
+Occupancy model map show
+```{r}
+#ORDISTEP
+
+#Invierno
+#Step: AvesInv2 ~ AMBIENTE + Cultivos + `Plantacion de arboles`
+
+#Primavera
+#Step: AvesPrim2 ~ AMBIENTE + `Bosque nativo`
+
+```
 
 5. Comparisons with results in other research
+
+Occupancy models for specific species
 
@@
 
-```{r, results='hide'}
-##### METAMDS: Non-metric Multidimensional scaling- NMDS
-
-#########################################################
-#Función para sacar los datos y ocupar ggplot
-TidyNMDS <- function(MDS, COVS){
-  DF <- COVS
-  DF2 <- MDS$points %>% as.data.frame()
-  DF <- bind_cols(DF2, DF)
-  return(DF = DF)
-}
-#########################################################
-#Invierno
-Inv_nmds2_bray <- suppressMessages(metaMDS(AvesInv2, autotransform = FALSE, distance="bray", k=2, try=20, trymax=100,  wascores=FALSE, trace=1, plot=FALSE))
-#Primavera
-Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
-```
-
-```{r, fig.width=9, fig.height=4, fig.cap="NMDS"}
-#Funcion para grafico NMDS en ggplot Invierno
-Tidy_Inv_nmds2_bray <- TidyNMDS(MDS = Inv_nmds2_bray, COVS = Amb)
-
-Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
-  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area") , values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
-  ggtitle('A')
-
-#Funcion para grafico NMDS en ggplot Primavera
-Tidy_Prim_nmds2_bray <- TidyNMDS(MDS = Prim_nmds2_bray, COVS = Amb)
-
-Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
-  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"), values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
-  ggtitle('B')
-
-#Ambos graficos con paquete patchwork
-Inv+Prim + plot_layout(guides = 'collect')
-```
-
-```{r, results='hide'}
-## test: ANOSIM
-
-#Invierno
-Diss_Inv2 <- vegdist(AvesInv2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
-#con base de datos por abundancia
-Anosim_Diss_Inv2<-anosim(Diss_Inv2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray", strata = NULL, parallel = getOption("mc.cores"))
-Summ_AnosimInv <-summary(Anosim_Diss_Inv2)
-
-#Primavera
-Diss_Prim2 <- vegdist(AvesPrim2, method="bray", binary=FALSE, diag=TRUE, upper=TRUE, na.rm = FALSE)
-#con base de datos por abundancia
-Anosim_Diss_Prim2<-anosim(Diss_Prim2, grouping=Amb$AMBIENTE, permutations = 9999, distance = "bray",strata = NULL, parallel = getOption("mc.cores")) 
-summary(Anosim_Diss_Prim2)
-
-```
-
-```{r, fig.width=9}
-Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
-  xlab("Variables")+ ylab("Dissimmilarity rank")+
-  ggtitle('A')
-
-Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
- xlab("Variables")+ ylab("Dissimmilarity rank")+
-   ggtitle('B')
-
-Inv / Prim
-```
-
-```{r}
-#Tabla Simper Inv
-
-Inv <-  read.csv("ResumenSimper_Inv2.csv")
-
-knitr::kable(
-  list(Inv[1:28, ], longtable = TRUE, booktabs = TRUE
-       ))
-
-```
-
-```{r}
-#Tabla Simper Inv
-Prim <-  read.csv("ResumenSimper_Prim2.csv")
-
-knitr::kable(
-  list(Prim[1:30, ], longtable = TRUE, booktabs = TRUE
-       ))
-```
-
-```{r}
-# set pander table-layout options
-library(pander)
-Prim <-  read.csv("ResumenSimper_Prim2.csv")
-Prim<- as.data.frame(Prim)
-panderOptions('table.alignment.default', function(Prim)
-    ifelse(sapply(Prim, is.numeric), 'right', 'left'))
-panderOptions('table.split.table', Inf)
-panderOptions('big.mark', ",")
-panderOptions('keep.trailing.zeros', TRUE)
-
-pander(Prim)
-
-```
-
-```{r, results='hide'}
-##### ENVFIT: Fits an Environmental Vector or Factor onto an Ordination
-###################################################
-TidyEnvFit <- function(ENVFit, alpha = 0.05){
-  DF <- ENVFit$vectors$arrows %>% as.data.frame()
-  DF$Factor <- rownames(DF)
-  DF$Pval <-ENVFit$vectors$pvals
-  DF <- DF %>% dplyr::filter(Pval < alpha)
-  return(DF = DF)
-}
-###################################################
-EnvfitInv2 <- envfit(Inv_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation` , data=Amb, perm=9999)
-Tidy_EnvfitInv2 <- TidyEnvFit(EnvfitInv2)
-
-EnvfitPrim2 <- envfit(Prim_nmds2_bray~  `Vegetation cover`+ `Distance to river`+Altitude+ `Native forest`+ Crops+ Gravel + Ocean +Grassland+ Shrublands+`Paved surface` + `Sand`+ `Tree plantation`, data=Amb, perm=9999)
-Tidy_EnvfitPrim2 <- TidyEnvFit(EnvfitPrim2)
-```
-
-```{r,  fig.width=9, fig.height=4}
-Inv <- ggplot(Tidy_Inv_nmds2_bray)+
-  geom_segment(data=Tidy_EnvfitInv2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
-  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
-  geom_text_repel(data=Tidy_EnvfitInv2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
-
-  theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
-  ggtitle('A')
-
-Prim <- ggplot(Tidy_Prim_nmds2_bray)+
-  geom_segment(data=Tidy_EnvfitPrim2, x = 0, y = 0, aes(xend =NMDS1 , yend = NMDS2), arrow = arrow(length = unit(0.2, "cm")))+
-  geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+
-  geom_text_repel(data=Tidy_EnvfitPrim2, aes(x=NMDS1, y=NMDS2, label=Factor), seed = 10)+
-    theme_classic()+ scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"),values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))+
-  ggtitle('B')
-
-Inv+Prim + plot_layout(guides = 'collect')
-
-```
-
 ### References

### 2020-10-16 README.Rmd
Avance en manuscrito, se corrió ocupnacia para sp obtenidas por simper

@@
 #### Documentación
-
-Revisar para completar
 
@@
 Se modifica tambien la importacion de este nuevo dataframe para hacer los analisis de la comunidad
+
+Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**
+Analisis para manuscrito en **Analisis_HabitatAves.R**.
+Para manuscritos see realiza ocupancia de ls especies obtenidas de simper para invierno y primavera en **Occu_especifica_Ms.R**, resultados en **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**

### 2020-10-16 Comportamiento_Aves.R

@@ -4,6 +4,9 @@ library(readxl)
 library(tidyverse)
 library(ggplot2)
 
+#There is just few species that contribute to differences between habitats. 
+#During winter: Pelecanus thagus, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and Sephanoides sephaniodes. 
+#And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, 
 
 ## Invierno
 

### 2020-10-16 Occu_especifica_Ms.R

@@ -6,9 +6,7 @@ library(unmarked)
 library(MuMIn)
 library(caret)
 
-
-####DATOS INVIERNO
-#Ocupancia para todas las especies en invierno
+#### INVIERNO
 
 data_det <-read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Analisis_Occu_punto/Occdata_detInv.rds")
 
@@ -16,8 +14,9 @@ data_ocu <-read_rds("Occdata_occu.rds")
 data_ocu <- data_ocu %>% dplyr::select(-Sitio)
 colnames(data_ocu) <- str_replace_all(colnames(data_ocu), pattern = " ", "_")
 
-data_reg <-read_rds("Occdata_regInv.rds")
-
+Simper <-read_csv("ResumenSimper_Inv2.csv")
+Simper <- Simper$Especie %>% as.character %>% unique()
+data_reg <-read_rds("Occdata_regInv.rds") %>% dplyr::select(starts_with(Simper))
 
 batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge = FALSE) {
   if(is.null(SppNames)){
@@ -157,44 +156,33 @@ batchoccu2 <- function(pres, sitecov, obscov, spp, form, SppNames = NULL, dredge
 }
 
 
-Spp <- data_reg %>% colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
+Spp <- data_reg %>% dplyr::select(starts_with(Simper)) %>% 
+  colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
 
-DetInv <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=45,  form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ 1", dredge=TRUE, SppNames = Spp)
+OccuInv <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=8,  
[…]

### 2020-10-16 Tablas_Ms_HabitatAves.Rmd
Archivo nuevo con tablas de ocupancia para sp simper

---
title: "Tablas_Ms_ HabitatAves"
author: "Giorgia Graells"
date: "10/16/2020"
output: 
  pdf_document: 
    keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
library(tidyverse)
```

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")

```

```{r, results='asis'}
DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))

kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")

```

### 2020-10-16 Tablas_Ms_HabitatAves.Rmd
Ocupancia especifica para especies obtenidas de simper, guardado de datos y nuevo .Rmd con tablas de manuscrito

@@
 ```{r, results='asis'}
-DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
-                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))
+DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii"), 
+                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23Na - 21.04Gr + 44.82Sa}$",
+                               "$\\psi_{Ld} = e^{12.45}$", 
+                               "$\\psi_{Lp} = e^{47.82 -5.09Al -231.04Gr + 5.74Oc + 	4.40Pa}$", 
+                               "$\\psi_{Pt} = e^{104.91 -0.59Al +	6.56Na	-2.93Sh -18.98Sa}$", 
+                               "$\\psi_{Pb} = e^{-82.05 + 12.46Cr -15.13Gr + 	1.38Oc}$"))
 
-kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")
+kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
 
@@
 ```{r, results='asis'}
-DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus_thagus", "Phalacrocorax_bougainvillii"), 
-                   Equation= c("$\\psi_{Cl} = e^{-39.76 + 45.23 \\times native forest - 21.04 \\times gravel + 44.82 \\times sand}$", "$\\psi_{Cl} = e^{12.45}$", "$\\psi_{Cl} = e^{	47.82 -5.09 \\times altitude -231.04 \\times gravel + 5.74 \\times ocean + 	4.40 \\times paved surface}$", "$\\psi_{Cl} = e^{104.91 -0.59 \\times altitude +	6.56\\times native forest 	-2.93 \\times shrublands -18.98\\times sand}$", "$\\psi_{Cl} = e^{-82.05 + 	12.46 \\times crops -15.13 \\times gravel + 	1.38 \\times ocean}$"))
+DF_occu <- tibble( Species= c("Columba livia","Coragyps atratus", "Larosterna inca", "Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Sephanoides sephaniodes", "Turdus falcklandii"), 
+                   Equation= c("$\\psi_{Cl} = e^{-1.77 + 1.83Sa}$", 
+                               "$\\psi_{Ca} = e^{7.57 -3.29Pa +	33.80Sa}$", 
+                               "$\\psi_{Li} = e^{140.42 -2.38Al	-92.31Na -38.88Sa}$", 
+                               "$\\psi_{Ld} = e^{2289.33}$",
+                               "$\\psi_{Lm} = e^{190.57 + 2.73Ve -4.07Al -134.07Gr +	20.05Sa}$", 
+                               "$\\psi_{Pt} = e^{172.98 -2.01Al	-50.93Na -165.09Gr +	2.47Oc}$", 
+                               "$\\psi_{Ss} = e^{-106.91 + 1.64Ve +	7.14Al -43.91Na +	5.09Sh -24.45Tr}$", 
+                               "$\\psi_{Tf} = e^{687.42 + 29.20Ve +	48.41Al -34.88Oc	-505.66Gs +	59.49Tr -4.94Pa +	283.63Sa -51.82Tr}$"))
 
-kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")
-
+kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
+#dear silvain
 ```

### 2020-10-16 Occu_especifica_Ms.R

@@ -160,7 +160,7 @@ Spp <- data_reg %>% dplyr::select(starts_with(Simper)) %>%
   colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
 
 OccuInv <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=8,  
-                       form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ CobVeg + AMBIENTE+ Distancia_rio+ Altura + Buffer_2200_Bosque_Nativo+ Buffer_2200_Cultivos + Buffer_2200_Grava+ Buffer_2200_Oceano + Buffer_2200_Pastizales + Buffer_2200_Matorrales + Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso +  Buffer_2200_Plantación_de_árboles", 
+                       form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ CobVeg + Distancia_rio+ Altura + Buffer_2200_Bosque_Nativo+ Buffer_2200_Cultivos + Buffer_2200_Grava+ Buffer_2200_Oceano + Buffer_2200_Pastizales + Buffer_2200_Matorrales + Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso +  Buffer_2200_Plantación_de_árboles", 
                        dredge=TRUE, SppNames = Spp)
 
 ##############
@@ -336,7 +336,7 @@ Spp <- data_reg %>% dplyr::select(starts_with(Simper)) %>%
   colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
 
 OccuPrim <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=6,  
-                      form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ CobVeg + AMBIENTE+ Distancia_rio+ Altura + Buffer_2200_Bosque_Nativo+ Buffer_2200_Cultivos + Buffer_2200_Grava+ Buffer_2200_Oceano + Buffer_2200_Pastizales + Buffer_2200_Matorrales + Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso +  Buffer_2200_Plantación_de_árboles", 
[…]

### 2020-11-04 Occu_especifica_Ms.R
Ocupancia para las especies del simper, prediccion ocupando buffers y altura

@@ -1,4 +1,7 @@
-#Correccion abundancias aves por modelos de deteccion
+#Occupancia Especifica para especies 
+
+#prediccion a partir de varibales ambientales
+#se sacó del modelo la cob vegetal porque no pudoo ser 
 
 library(tidyverse)
 library(stringr)
@@ -160,9 +163,9 @@ Spp <- data_reg %>% dplyr::select(starts_with(Simper)) %>%
   colnames() %>% str_remove_all("1")%>% str_remove_all("2") %>% str_remove_all("3") %>% unique()
 
 OccuInv <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=8,  
-                       form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~ CobVeg + Distancia_rio+ Altura + Buffer_2200_Bosque_Nativo+ Buffer_2200_Cultivos + Buffer_2200_Grava+ Buffer_2200_Oceano + Buffer_2200_Pastizales + Buffer_2200_Matorrales + Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso +  Buffer_2200_Plantación_de_árboles", 
+                       form= "~ Temperatura +Humedad+ DirViento +RapViento+ Agua ~  Distancia_rio+ Altura + Buffer_2200_Bosque_Nativo+ Buffer_2200_Cultivos + Buffer_2200_Grava+ Buffer_2200_Oceano + Buffer_2200_Pastizales + Buffer_2200_Matorrales + Buffer_2200_Sup_impermeables+ Buffer_2200_Suelo_arenoso +  Buffer_2200_Plantación_de_árboles", 
                        dredge=TRUE, SppNames = Spp)
-
+saveRDS(OccuInv, "ModelosOccuInv_Ms.rds")
 ##############
 SppNames = OccuInv$models %>% names()
 Mods <- OccuInv$models
@@ -338,7 +341,7 @@ Spp <- data_reg %>% dplyr::select(starts_with(Simper)) %>%
 OccuPrim <- batchoccu2(pres = data_reg, sitecov = data_ocu, obscov = data_det, spp=6,  
[…]

### 2020-11-04 Ms_HabitatAves.Rmd
Archivo nuevo con tablas de ocupancia para sp simper
Mapas de prediccion de ocupancia para especies en invirnos y primavera. Primer plot

@@
 ---
-title: "Ms Habitat aves. Species composition in coastal urban habitats"
+title: "Bird species composition in coastal urban habitats"
 output:
@@
 library(knitr)
+library(rasterVis)
 
@@
 Urban modificacion over natural environments has promoted loss of native species and their replacement by non-native species [@mckinney2006urbanization].
-This is called biotic homogenization, where few species are adapted to urban and suburban conditions [@mckinney1999biotic].
-Biotic homogenization affects variety of ecosystems [grassland: @zeeman2017biotic], climates [temperate: @zeeman2017biotic],taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic]
+This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].
 
 [Stablish the importance of this research topic, more specific/detailed way]
-This urban homogenization has effects: 
-a. more homogenized biosfera with lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
+This urban homogenization is projected to lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
 which has been studied mostly in birds and plants
@@
 [Provide general background information, more specific/detailed way]
-In birds, urban homogenization in more specific: has a nonrandom filtering effect on birds, they show guildsresponse to urbanization [@silva2016nonrandom].
+Bird species comunnities in cities are more similar to urban communities nearby than to communities in sorroundinng natural environments.
+However, local features seems to be mportant in those assembles.
 Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
@@
 [Describe general problem area or the current research focus of the field]
+By 2019
 half of population live in coastal cities, however urbanization has been msotly focus in terrestiral aspects.
@@
 [General overview of this section]
-In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, a Metropolitan area in Central Chile.
-We estimated species composition based on bird presence analised using occupancy models.
+In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, estimated species composition based on bird presence analised using occupancy models and analized bird assembles in those environment.
 
 [Provide background information and justification]
-Coastal central chile present a rapid urbanization growth since the last... years, endengering natural habitats. 
-The area is near by the chilean capital which has close to 6 million inhabitants.
+The Gran Valparaíso, a Metropolitan coastal area in Central Chile, is formed by the conection of three cities: Valparaíso, a mayor port in the country, Viña del Mar, a big beach city since xxx and today one of the xx cities in ,  and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
+The area is near by the chilean capital, Santiago, which has close to 6 million inhabitants.
 This area is inmerse ina a natural-rural matrix composed ... in a grographic Coastal mountain chain-- papers bahi concon y viña
@@
 [Provide an overview of the procedure/method itself]
-species composition were analised with the package vegan for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
+To estimate species composition and assembles, occupancy models were developed with package DiversityOcuppancy [@divoccu] and 
+species composition were analised with the package vegan [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
 
@@
 
-```{r tabla3}
-#Modelo 1= Abundancia ~ Estacion *Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
-#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0
-
-```
-
 3. Invitations to view results
@@
 
-Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats.
+Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different.
 There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
@@
 During winter: *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*.
-And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (Fig.
-\@ref(fig:SIMPER1), Fig.
-\@ref(fig:SIMPER2)).
+And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (see Suplementary material for complete species list of SIMPER).
 
-```{r SIMPER1, fig.cap="Simper analysis for winter"}
-# set pander table-layout options
-library(pander)
-Inv <-  read.csv("ResumenSimper_Inv2.csv")
-Inv<- as.data.frame(Inv)
-panderOptions('table.alignment.default', function(Inv)
-    ifelse(sapply(Inv, is.numeric), 'right', 'left'))
-panderOptions('table.split.table', Inf)
-panderOptions('big.mark', ",")
-panderOptions('keep.trailing.zeros', TRUE)
+```{r OccuInv}
+Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
+Larus <-read_rds("PredInv_Larus_dominicanus.rds") 
+Coragyps <-read_rds("PredInv_Coragyps_atratus.rds")
+Larosterna <-read_rds("PredInv_Larosterna_inca.rds")
+Leucophaeus <-read_rds("PredInv_Leucophaeus_modestus.rds")
+Columba <-read_rds("PredInv_Columba_livia.rds")
+Turdus <-read_rds("PredInv_Turdus_falcklandii.rds")
+Sephanoides <-read_rds("PredInv_Sephanoides_sephaniodes.rds")
 
-pander(Inv)
-#Inv$Especie
+Especies <- stack(Pelecanus,Larus,Coragyps, Larosterna, Leucophaeus,  Columba, Turdus, Sephanoides)
+names(Especies) <- c("Pelecanus thagus", "Larus dominicanus", "Coragyps atratus", "Larosterna inca", "Leucophaeus modestus", "Columba livia", "Turdus falcklandii", "Sephanoides sephaniodes")
+
+Mytheme <- YlOrRdTheme()
+Mytheme$panel.background$col <- "black"
+
+levelplot(Especies, par.settings=Mytheme)
+
 ```
 
-```{r SIMPER2, fig.cap="Simper analysis for spring"}
-# set pander table-layout options
-library(pander)
-Prim <-  read.csv("ResumenSimper_Prim2.csv")
-Prim<- as.data.frame(Prim)
-panderOptions('table.alignment.default', function(Prim)
-    ifelse(sapply(Prim, is.numeric), 'right', 'left'))
-panderOptions('table.split.table', Inf)
-panderOptions('big.mark', ",")
-panderOptions('keep.trailing.zeros', TRUE)
+```{r OccuPrim}
+Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
+Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
+Columba <-read_rds("PredPrim_Columba_livia.rds")
+Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
+Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
+Pelecanus <-read_rds("PredPrim_Pelecanus_thagus.rds")
 
-pander(Prim)
+Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
+names(Especies) <- c("Leucophaeus pipixcan", "Larus dominicanus", "Columba livia", "Larosterna inca", "Phalacrocorax bougainvillii", "Pelecanus thagus")
+
+Mytheme <- YlOrRdTheme()
+Mytheme$panel.background$col <- "black"
+
+levelplot(Especies, par.settings=Mytheme)
 
@@
 
-species for each habitat
-Occupancy model map show
 ```{r}
@@
 
+```
+
+species for each habitat
+Occupancy model map show
+
+```{r}
+#Resultados occupancia para especies dde Simper
+ModelosOccuPrim <- read_rds("ModelosOccuPrim_Ms.rds")
+#Para generar las ecuaciones **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**
 ```

### 2020-11-04 README.Rmd
Mapas de prediccion de ocupancia para especies en invirnos y primavera. Primer plot

--- 2020-10-06 README.Rmd
@@
 Se modifica tambien la importacion de este nuevo dataframe para hacer los analisis de la comunidad
+
+# Escritura manuscrito, arreglo de figuras y analisis especificos
+
+Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**
+El manuscrito cuenta con imput desde: 
+- Algunos analisis ubicados en **Analisis_HabitatAves.R**. 
+- Ocupancia de las especies obtenidas de simper para invierno y primavera en **Occu_especifica_Ms.R**, resultados en **Resultado_OccuPrim_Ms.rds** y **Resultado_OccuInv_Ms.rds**.
+- En la segunda parte del script **Occu_especifica_Ms.R** se encuentra las predicciones realizadas para las especies seleccionadas antariormente, utilizando la capa **Capas_Proporcion_small.rds** creada desde los buffers y la altura.
+Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacio_Especie.rds**

### 2020-11-04 README.Rmd
Arreglo de las actividades realizadas en el manuscrito y lo necesario para hacerlo

@@
 
-#### Junio
+### Junio
 Se realiza ocupancia con función nueva utilizando nuevas variables ambientales generadas en **MapaYuryi.R** que corresponde a capas de cobertura vegetal en buffers (distancia desde los puntos de muestreo), archivo de salida que incluye variables ambientales y buffers por distancia: **Occdata_ocu.rds** y un leaflet al final del código para ver las capas por cada sitio en el mapa.
@@
 
-#### Ordenando los resultados y buscando una explicacion: 1. Marco conceptual rasgos funcionales
+### Ordenando los resultados y buscando una explicacion: 1. Marco conceptual rasgos funcionales
 
@@
 
---- analisis exploraorios con rasgos funcionales, pero se presentan errores desde informaciond e ocupancia por nombre comun de especies (ademas dde elevados valores de ocupancia para mas de 42 sp)
+### Extras
+Analisis exploraorios con rasgos funcionales, pero se presentan errores desde informaciond e ocupancia por nombre comun de especies (ademas dde elevados valores de ocupancia para mas de 42 sp)
 14 agoosto: Modificacion de codigo para trabajar ocupancias con nombre de especies en vez de nombre comun de aves.
@@
 
-### Exploración de datos en base a reunion 18 agosto
+### Exploración de datos en base a reunion 18 agosto 2020
 
@@
 - NMDS + ANOSIM
+
 - SIMPER
+
 - BIOENV
@@
 analisis listos para abundancia, comp especies y ocupancia
-
 modificacion de parametros de distintas funciones para su correcto uso
@@
 
-#Correccion de abundancia por deteccion
+### Correccion de abundancia por deteccion
 
@@
 
-# Escritura manuscrito, arreglo de figuras y analisis especificos
+## Escritura manuscrito, arreglo de figuras y analisis especificos
 
@@
 - En la segunda parte del script **Occu_especifica_Ms.R** se encuentra las predicciones realizadas para las especies seleccionadas antariormente, utilizando la capa **Capas_Proporcion_small.rds** creada desde los buffers y la altura.
-Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacio_Especie.rds**
+Cada especie (8 de invierno y6 de primavera) tienen sus resultados exportados por separado **PredEstacionX_EspecieX.rds**
+- graficos de comportamiento desde archivo **Comportamineto_Aves.R**, con abundancia corregida de invierno de **AbundInv_Corregido.rds** y **AbundPrim_Corregido.rds**

### 2020-11-07 Comportamiento_Aves.R
Arreglo de datos y graficos comportamiento

@@ -1,93 +1,106 @@
 #Comportamiento aves por ambiente
+# Comportamiento oactividades registradas de aves en terreno
 
 library(readxl)
 library(tidyverse)
 library(ggplot2)
 
-#There is just few species that contribute to differences between habitats. 
-#During winter: Pelecanus thagus, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and Sephanoides sephaniodes. 
-#And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, 
 
 ## Invierno
+# Winter: Pelecanus thagus, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and Sephanoides sephaniodes. 
 
-ComportamientoInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))
-ComportamientoInv <- ComportamientoInv %>% dplyr::select(AMBIENTE, Sitio, Especie, Comportamiento) %>% 
-  mutate(Comportamiento=as.character(Comportamiento),
-         Comportamiento= str_replace(Comportamiento, "1", "En el agua"), #Nadando o caminando en el agua
-         Comportamiento= str_replace(Comportamiento, "2", "En el suelo"), #-tierra, pasto, arena, roca
-         Comportamiento= str_replace(Comportamiento, "3", "Entre el follaje"), #-en árbol o arbusto
-         Comportamiento= str_replace(Comportamiento, "4", "Posado en altura"), #-poste o cable
-         Comportamiento= str_replace(Comportamiento, "5", "En el aire"), #Volando o planeando
-         Comportamiento= str_replace(Comportamiento, "6", "En un nido"),
[…]

### 2020-11-09 Ms_HabitatAves.Rmd
arreglo comportamiento en rms manuscrito

@@
 
-Amb <- Amb %>% dplyr::select(-Sitio)
+Amb <- Amb %>% dplyr::select(-Sitio) %>%
+  mutate(AMBIENTE= str_replace(AMBIENTE, "URBANO", "Urban"),
+         AMBIENTE= str_replace(AMBIENTE, "VERDE", "Green area"),
+         AMBIENTE= str_replace(AMBIENTE, "ROCA INTERVENIDA", "Modified rocky shore"),
+         AMBIENTE= str_replace(AMBIENTE, "PLAYA INTERVENIDA", "Urbanized beach"),
+         AMBIENTE= str_replace(AMBIENTE, "ROCA NATURAL", "Natural rocky shore"),
+         AMBIENTE= str_replace(AMBIENTE,"PLAYA NATURAL", "Natural beach"))
 ```
@@
 
-1. Establish importance of the fild- provide background, keywords- present the problem
+1. Establish importance of the field- provide background, keywords- present the problem
 
-[Stablish the importance of this research topic]
+[Establish the importance of this research topic]
 
-Urbanization have been growing rapidly ...
-and is one of the mayor causes of species loss [@czech2000economic].
+Urbanization has been growing rapidly. During 2018, more than half of world’s population  lived  in  urban  settlements.   
+Cities are growing in both size and number, by  2018  the  number  of  cities  with  at  least  1  million  inhabitants  had  grown  to 548 [@UN_WorldCities2018].
+and
 
 [Provide general background information]
-Urban modificacion over natural environments has promoted loss of native species and their replacement by non-native species [@mckinney2006urbanization].
-This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].
+Urban modification over natural environments is one of the mayor causes of species loss [@czech2000economic].
+Some of these loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
+This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biome [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].
 
-[Stablish the importance of this research topic, more specific/detailed way]
+[Establish the importance of this research topic, more specific/detailed way]
 This urban homogenization is projected to lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
@@
 [Provide general background information, more specific/detailed way]
-Bird species comunnities in cities are more similar to urban communities nearby than to communities in sorroundinng natural environments.
-However, local features seems to be mportant in those assembles.
+Bird species communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
+However, local features seems to be important in those assembles.
 Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
@@
 [Describe general problem area or the current research focus of the field]
-By 2019
-half of population live in coastal cities, however urbanization has been msotly focus in terrestiral aspects.
+Cities  in  coastal  areas  are the  most affected  by natural  and human  generated  disasters while  are  alsoattractive  for  private  investments, and often located in  ecologically  sensitive  areas.
+Generally coasts  are  more  densely  populated compared toin-land areas due  to the many  keyeconomic  activities takingplace in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling.
+Coastal areas are also home to species and habitats that provide  many benefits  to  the  societybut  might  often  be  threatened.
+Coastal  areas  biomes  are  rich  in biodiversity but at the same time extremely vulnerable.
+
+By 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017].
+many  key economic  activities taking place in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling.
+
+coasta como area vulnerable y hay poca investigacion
+, however urbanization has been mostly focus in terrestrial aspects.
 
@@
 
-3. Locate the gap-describe the proble to address-present a prediction to be tested
+3. Locate the gap-describe the problem to address-present a prediction to be tested
 
@@
 Urban homogenization has been studied in cities, focused in terrestrial variables
-Considering Birs comunities in urban areas depend of the perurban composition of species, there are no studies in the effects of marine habitats
+Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats
 
 [Describe gaps in the research]
-There is a gap in studies that focus in coastal ecotone and the influence of antrhopized areas
+There is a gap in studies that focus in coastal ecotone and the influence of urban areas
 focusing on marine and terrestrial interaction of species in an urbanized area and how birds use this as habitats
 
-[Decribe paper itself]
-This research aim to identified the use of coastal urban habitats by birds describing the composition of species in differrent environments, considering bird species origin (marine and terrestrial).
+[Describe paper itself]
+This research aim to identified the use of coastal urban habitats by birds describing the composition of species in different environments, considering bird species origin (marine and terrestrial).
 with the aim of: 1.
@@
 identify how urbanization affects those bird assembles, 3.
-Evaluate iconic bird species habitat ocupation, and 4.
+Evaluate iconic bird species habitat occupation, and 4.
 describe bird behavior in those habitats
@@
 [Announces the findings]
-Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inlsnd bird species
+Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inland bird species
 
-### Metodology
+### Methodology
 
@@
 [General overview of this section]
-In this research we conducted bird surveys in six coastal urban environments in the Gran Valparaíso, estimated species composition based on bird presence analised using occupancy models and analized bird assembles in those environment.
+In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on bird presence analysed using occupancy models and analysed bird assembles in those environment.
 
 [Provide background information and justification]
-The Gran Valparaíso, a Metropolitan coastal area in Central Chile, is formed by the conection of three cities: Valparaíso, a mayor port in the country, Viña del Mar, a big beach city since xxx and today one of the xx cities in ,  and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
-The area is near by the chilean capital, Santiago, which has close to 6 million inhabitants.
-This area is inmerse ina a natural-rural matrix composed ... in a grographic Coastal mountain chain-- papers bahi concon y viña
+The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to Censo 2017).
+The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
+The area is near by the chilean capital, Santiago, which has more than 7 million inhabitants.
+This area is immerse in a natural-rural matrix composed ... in a geographic Coastal mountain chain-- papers bahi concon y viña
 
 [Provide an overview of the procedure/method itself]
-To estimate species composition and assembles, occupancy models were developed with package DiversityOcuppancy [@divoccu] and 
-species composition were analised with the package vegan [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
+To estimate species composition and assembles, occupancy models were developed with DiversityOcuppancy package [@divoccu] and 
+species composition were analysed with the vegan package [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
 
@@
 [Provide details about what was done and used and shows that care was taken]
-Six coastal habitat were defined in terms of its proximity to the coast, level of anthropotization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1).
+Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1).
 Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
@@
 [Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-Bird commmunities were analised using ordination methods with vegan package in R with species abundances corrected by detection capacity, using occupancy models (see table 1).
+Bird commmunities were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with  DiversityOcuppancy package [@divoccu](see table 1).
 We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
 To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
+
+In order to understand habitat use by birds, bird activities were counted by each habitat
+
 Fit of environmental variables on species ordination was also tested.
-Bird behabiour was counted for each habitat.
 
@@
 [Describe what was done by referring to existing mehods in the literature]
-To independize our analysis from habitats already defined, ocupancy models of eight species were developed and projected over the study area
+To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.
 
@@
 For these habitats, bird assemblages differ between winter and spring seasons.
+Environmental variables can be responsible of both community identities and use of habitat idiviualy
 
@@
 Distribution of sites in graphical NMDS (Fig.
-\@ref(fig:NMDS)) showed both seassons presented differences in abundance of species mostly in the inland sites.
+\@ref(fig:NMDS)) showedthat both seassons presented differences in abundance of species mostly in the inland sites.
 Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
@@
 
-Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
-  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area") , values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
+  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
   ggtitle('A')
@@
 
-Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic()+ 
-  scale_color_manual(name="Coastal habitats", labels=c("Urbanized beach", "Natural beach", "Modified rocky shore", "Natural rocky shore","Urban centre", "Green area"), values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) +
+Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
+  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
   ggtitle('B')
@@
 
-```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A winter and B spring"}
+```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A winter (R=0.584, P<0.001) and B spring (R=0.573, P< 0.001)"}
 Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
@@
 
-There is just few species that contribute to differences between habitats.
-During winter: *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*.
-And spring: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*, according to simper analysis (see Suplementary material for complete species list of SIMPER).
+Both sampled seasons showed that few species contribute to differences between habitats.
+Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
+(For a complete species list of SIMPER, see Suplementary material).
 
-```{r OccuInv}
+Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
+
+Species such as xxx, showed differernces in habitat use between seasons.
+(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))
+
+```{r OccuInv, fig.width=9.5, fig.height=6.5}
 Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
@@
 
-```{r OccuPrim}
+```{r OccuPrim, fig.width=7, fig.height=6.5}
 Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
@@
 
+Finally, use of these habitats can be seen with the activity record of bird species.
+
+```{r Comportamineto, fig.height=10}
+ComportamientoInv <- read_rds("ComportamientoInv.rds")
+I <-ggplot(ComportamientoInv) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+
+ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
+
+P <-ggplot(ComportamientoPrim) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+
+I/P
+
+```
+
 5. Comparisons with results in other research
@@
 
-7. Possible impllications with results
+7. Possible implications with results
 
@@
 
-1. Revisting previous research- summarise
+1. Revising previous research- summaries
 [Revisit previous research]
@@
 [Revisit methodology used in this study]
-[Revisit and summarise the results]
+[Revisit and summaries the results]
 [Show where and how the present work fits into the research "map" in this field]
 
-3. Achivements/contributions- refining implications
-[Recall an aspect of the results that represents a postitive achievement or contribution of this work]
+3. Achievements/contributions- refining implications
+[Recall an aspect of the results that represents a positive achievement or contribution of this work]
 [Focus in the meaning and implications of the achievements in this work]

### 2020-11-09 Comportamiento_Aves.R

@@ -48,6 +48,8 @@ ComportamientoInv <- ComportamientoInv %>%
   mutate(Cientifico=fct_relevel(Cientifico, "Leucophaeus_modestus","Larus_dominicanus","Coragyps_atratus","Larosterna_inca","Columba_livia","Pelecanus_thagus",       
                                  "Sephanoides_sephaniodes", "Turdus_falcklandii" ))
 
+saveRDS(ComportamientoInv, "ComportamientoInv.rds")
+
 ggplot(ComportamientoInv) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
   theme(legend.position = "bottom", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
@@ -98,6 +100,8 @@ ComportamientoPrim <- ComportamientoPrim %>%
   mutate(AMBIENTE=fct_relevel(AMBIENTE, "Urban", "Green area", "Modified rocky shore", "Urbanized beach", "Natural rocky shore")) #%>% 
   #mutate(Cientifico=fct_relevel(Cientifico, "Leucophaeus_modestus","Larus_dominicanus","Coragyps_atratus","Larosterna_inca","Columba_livia","Pelecanus_thagus",       
          #                       "Sephanoides_sephaniodes", "Turdus_falcklandii" ))
+
+saveRDS(ComportamientoPrim, "ComportamientoPrim.rds")
 
 ggplot(ComportamientoPrim) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  

### 2020-11-10 Ms_HabitatAves.Rmd
Avance en intro

@@
 
-Urbanization has been growing rapidly. During 2018, more than half of world’s population  lived  in  urban  settlements.   
-Cities are growing in both size and number, by  2018  the  number  of  cities  with  at  least  1  million  inhabitants  had  grown  to 548 [@UN_WorldCities2018].
-and
+Urbanization has been growing rapidly. During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
 
 [Provide general background information]
-Urban modification over natural environments is one of the mayor causes of species loss [@czech2000economic].
-Some of these loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
-This scenario shows how few species can adapt better to urban and suburban conditions [@mckinney1999biotic], however it affects to ecosystems [grassland: @zeeman2017biotic], biome [temperate: @zeeman2017biotic], and taxonomic groups [mainly in birds and plants, but also insects: @knop2016biotic].
+
+Urbanization is a complex process that causes profound changes in the ecological functioning of the landscapeand gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
 
 [Establish the importance of this research topic, more specific/detailed way]
-This urban homogenization is projected to lower diversity, where there will be many species losers and few winners [@mckinney1999biotic].
-which has been studied mostly in birds and plants
+
+In this environment, some of these loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization] because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
 
 [Provide general background information, more specific/detailed way]
-Bird species communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
-However, local features seems to be important in those assembles.
-Composición de aves urbanas depende más de la composición de aves urbanas aledañas que de los ambientes naturales que los rodean
-Rural birds
-According to @clergeau2001urban, urban  bird  communities  are  independent of the bird diversity of adjacent landscapes, and that local features are more important than surrounding landscapes.
+
+Studies suggest that bird communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
+To bird assembles local features are more important than surrounding landscapes @clergeau2001urban,
 
@@
 [Describe general problem area or the current research focus of the field]
-Cities  in  coastal  areas  are the  most affected  by natural  and human  generated  disasters while  are  alsoattractive  for  private  investments, and often located in  ecologically  sensitive  areas.
-Generally coasts  are  more  densely  populated compared toin-land areas due  to the many  keyeconomic  activities takingplace in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling.
-Coastal areas are also home to species and habitats that provide  many benefits  to  the  societybut  might  often  be  threatened.
-Coastal  areas  biomes  are  rich  in biodiversity but at the same time extremely vulnerable.
 
-By 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017].
-many  key economic  activities taking place in coastal areas,  including  marine  transport,  shipping  of  goods,  fishing,  recreation,  tourism,  offshore gas and oil drilling.
-
-coasta como area vulnerable y hay poca investigacion
-, however urbanization has been mostly focus in terrestrial aspects.
+Cities in coastal areas combine many key economic activities such as marine transport, shipping of goods, fishing, recreation, and tourism.
+These areas are attractive for people to settle and by 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017].
+Species and ecosystems of coastal areas are often threatened by the growing urbanization, the landscape change, and also by the vulnerable that this area is naturally
 
 [Provide transition between the general problem area and the literature review]
-More than the half of the cities in the world are coastal cities and they lack of studies addressing marine and terrestrial interactions.
+
+Even this scenario, urbanization has been mostly focus in terrestrial aspects, and even when more than the half of the cities in the world rise on the coast, there is a lack of studies addressing marine and terrestrial interactions.
 
@@
 [General overview of this section]
-In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on bird presence analysed using occupancy models and analysed bird assembles in those environment.
+In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on corrected bird presences, and analysed bird assembles in those environment.
 
 [Provide background information and justification]
-The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to Censo 2017).
+The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
 The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
-The area is near by the chilean capital, Santiago, which has more than 7 million inhabitants.
-This area is immerse in a natural-rural matrix composed ... in a geographic Coastal mountain chain-- papers bahi concon y viña
 
 [Provide an overview of the procedure/method itself]
-To estimate species composition and assembles, occupancy models were developed with DiversityOcuppancy package [@divoccu] and 
-species composition were analysed with the vegan package [@Vegan] for RStudio using corrected abundance of species. Bird abundance was corrected by detection capacity using occupancy models.
+Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu].
+To estimate species assembles for habitats, the vegan package [@Vegan] was used.
+Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].
 
@@
 Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
-We tested a model where seasonality has a interacttion with the habitats defined in this research.
+We tested a model where seasonality has a interaction with the habitats defined in this research.
 
 [Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-Bird commmunities were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with  DiversityOcuppancy package [@divoccu](see table 1).
+
+Bird commmunities for each habitat were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with DiversityOcuppancy package [@divoccu](see table 1).
 We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
@@
 Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
-  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
-  ggtitle('A')
+  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))
 
@@
 Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
-  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + 
-  ggtitle('B')
+  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))
 
 #Ambos graficos con paquete patchwork
-Inv+Prim + plot_layout(guides = 'collect')
+Inv+Prim + plot_annotation(tag_levels = 'A')
 ```
@@
 Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
-  xlab("Variables")+ ylab("Dissimmilarity rank")+
-  ggtitle('A')
+  xlab("Variables")+ ylab("Dissimmilarity rank")
 
 Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
- xlab("Variables")+ ylab("Dissimmilarity rank")+
-   ggtitle('B')
+ xlab("Variables")+ ylab("Dissimmilarity rank")
 
-Inv / Prim
+Inv / Prim +plot_annotation(tag_levels = 'A')
 ```
@@
 
-```{r OccuInv, fig.width=9.5, fig.height=6.5}
+```{r OccuInv, fig.width=10, fig.height=7}
 Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
@@
 Especies <- stack(Pelecanus,Larus,Coragyps, Larosterna, Leucophaeus,  Columba, Turdus, Sephanoides)
-names(Especies) <- c("Pelecanus thagus", "Larus dominicanus", "Coragyps atratus", "Larosterna inca", "Leucophaeus modestus", "Columba livia", "Turdus falcklandii", "Sephanoides sephaniodes")
+names(Especies) <- c("Columba livia", "Coragyps atratus", "Larosterna inca","Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Turdus falcklandii", "Sephanoides sephaniodes")
 
@@
 
-```{r OccuPrim, fig.width=7, fig.height=6.5}
+```{r OccuPrim, fig.width=8, fig.height=7}
 Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
@@
 Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
-names(Especies) <- c("Leucophaeus pipixcan", "Larus dominicanus", "Columba livia", "Larosterna inca", "Phalacrocorax bougainvillii", "Pelecanus thagus")
+names(Especies) <- c("Columba livia", "Larosterna inca", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii")
 
@@
 
-```{r Comportamineto, fig.height=10}
+```{r Comportamineto, fig.height=7, fig.width=10}
 ComportamientoInv <- read_rds("ComportamientoInv.rds")
@@
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
-  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
   scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
@@
 
-I/P
+layout <- "
+AAAAAAAA
+BBBBBBB#
+"
+I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
 
 ```
+
+Most of the species were detected during the fliying, however some were founded in particular activities.
 

### 2020-11-11 Ms_HabitatAves.Rmd
CAmbios pequeños

@@
 #Ambos graficos con paquete patchwork
-Inv+Prim + plot_annotation(tag_levels = 'A')
+Inv+Prim + plot_annotation(tag_levels = 'A')+ plot_layout(guides = 'collect')
 ```
@@
 
-```{r Comportamineto, fig.height=7, fig.width=10}
+```{r Comportamineto, fig.height=8, fig.width=10}
 ComportamientoInv <- read_rds("ComportamientoInv.rds")

### 2020-11-12 Ms_HabitatAves.Rmd
Cambio mapa ocupancia a ggplot

@@
 [Establish the importance of this research topic]
-
-Urbanization has been growing rapidly. During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
+During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
 
 [Provide general background information]
-
-Urbanization is a complex process that causes profound changes in the ecological functioning of the landscapeand gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
+Urbanization is a complex process that causes profound changes in the ecological functioning of the landscaped gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
 
 [Establish the importance of this research topic, more specific/detailed way]
-
-In this environment, some of these loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization] because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
+Some of these losses of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
+These is because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
 
@@
 ```{r OccuInv, fig.width=10, fig.height=7}
+
+library(sf)
+library(raster)
+library(ggrepel)
 Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
@@
 
-Especies <- stack(Pelecanus,Larus,Coragyps, Larosterna, Leucophaeus,  Columba, Turdus, Sephanoides)
-names(Especies) <- c("Columba livia", "Coragyps atratus", "Larosterna inca","Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Turdus falcklandii", "Sephanoides sephaniodes")
+Nombres <- c("Pelecanus", "Larus", "Coragyps", "Larosterna", "Leucophaeus", "Columba", "Turdus", "Sephanoides")
+Species <- list(Pelecanus, Larus, Coragyps, Larosterna, Leucophaeus, Columba, Turdus, Sephanoides)
 
-Mytheme <- YlOrRdTheme()
-Mytheme$panel.background$col <- "black"
+temp <- list()
 
-levelplot(Especies, par.settings=Mytheme)
+for(i in 1:length(Species)){
+  temp[[i]] <- Species[[i]] %>% as("SpatialPixelsDataFrame") %>% as.data.frame()
+  colnames(temp[[i]])[1] <- Nombres[i]
+}
+
+Species_DF <- temp %>% reduce(full_join) %>% dplyr::relocate(Pelecanus, .after = y) %>% pivot_longer(Pelecanus:Sephanoides, names_to = "Species", values_to = "Occupancy")
+
+Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
+  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
+         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
+         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
+         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
+  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")
+
+ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
+nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)
 

### 2020-11-12 Ms_HabitatAves.Rmd
mapa ocupancia en ggplot para primavera tambien

@@
 ```{r OccuPrim, fig.width=8, fig.height=7}
-Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
-Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
 Columba <-read_rds("PredPrim_Columba_livia.rds")
 Larosterna <-read_rds("PredPrim_Larosterna_inca.rds")
+Larus <-read_rds("PredPrim_Larus_dominicanus.rds")
+Leucophaeus <-read_rds("PredPrim_Leucophaeus_pipixcan.rds")
 Phalacrocorax <-read_rds("PredPrim_Phalacrocorax_bougainvillii.rds")
@@
 
-Especies <- stack(Leucophaeus, Larus, Columba, Larosterna, Phalacrocorax,  Pelecanus)
-names(Especies) <- c("Columba livia", "Larosterna inca", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii")
+Nombres <- c("Columba", "Larosterna", "Larus","Leucophaeus", "Phalacrocorax", "Pelecanus")
+Species <- list(Columba, Larosterna, Larus, Leucophaeus, Phalacrocorax, Pelecanus)
 
-Mytheme <- YlOrRdTheme()
-Mytheme$panel.background$col <- "black"
+temp <- list()
 
-levelplot(Especies, par.settings=Mytheme)
+for(i in 1:length(Species)){
+  temp[[i]] <- Species[[i]] %>% as("SpatialPixelsDataFrame") %>% as.data.frame()
+  colnames(temp[[i]])[1] <- Nombres[i]
+}
+
+Species_DF <- temp %>% reduce(full_join) %>% dplyr::relocate(Columba, .after = y) %>% pivot_longer(Columba:Pelecanus, names_to = "Species", values_to = "Occupancy")
+
+Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
+  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
+         Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
+         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
+         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
+  dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
+  st_transform(crs="+proj=utm +zone=19 +south +datum=WGS84 +units=m +no_defs +ellps=WGS84 +towgs84=0,0,0")
+
+ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
+nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)
 

### 2020-11-16 Ms_HabitatAves.Rmd
eleccion de 6 sitios para grafico de ocupancia

@@
 Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
-  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
-  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
+  dplyr::filter(Sitio %in% c("TERMINAL", "PLAYA LA BOCA", "PARQUE EL LITRE", "CALETA EL MEMBRILLO", "ROCA OCEANICA","SECTOR 5")) %>% 
+  mutate(Sitio= str_replace(Sitio, "TERMINAL", "T"),
          Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
-         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
-         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
+         Sitio= str_replace(Sitio, "PARQUE EL LITRE", "PEL"),
+         Sitio= str_replace(Sitio, "CALETA EL MEMBRILLO", "CEM"),
+         Sitio= str_replace(Sitio, "ROCA OCEANICA", "RO"),
+         Sitio= str_replace(Sitio, "SECTOR 5", "PR")) %>% 
   dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
@@
 
-ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+OcuI <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
     ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
 nudge_x=-5000, nudge_y = 1000)+ 
-  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")
 
@@
 Sitios <- read.csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
-  dplyr::filter(Sitio %in% c("PLAZA ANIBAL PINTO", "PLAYA LA BOCA", "PLAZA GABRIELA MISTRAL", "LAGUNA VERDE")) %>% 
-  mutate(Sitio= str_replace(Sitio, "PLAZA ANIBAL PINTO", "PAP"),
+ dplyr::filter(Sitio %in% c("TERMINAL", "PLAYA LA BOCA", "PARQUE EL LITRE", "CALETA EL MEMBRILLO", "ROCA OCEANICA","SECTOR 5")) %>% 
+  mutate(Sitio= str_replace(Sitio, "TERMINAL", "T"),
          Sitio= str_replace(Sitio, "PLAYA LA BOCA", "PLB"),
-         Sitio= str_replace(Sitio, "PLAZA GABRIELA MISTRAL", "PGM"),
-         Sitio= str_replace(Sitio, "LAGUNA VERDE", "LG")) %>% 
+         Sitio= str_replace(Sitio, "PARQUE EL LITRE", "PEL"),
+         Sitio= str_replace(Sitio, "CALETA EL MEMBRILLO", "CEM"),
+         Sitio= str_replace(Sitio, "ROCA OCEANICA", "RO"),
+         Sitio= str_replace(Sitio, "SECTOR 5", "PR")) %>% 
   dplyr::select(Sitio, Latitud, Longitud) %>% distinct() %>% st_as_sf(coords=c("Longitud","Latitud"),crs="+proj=longlat +datum=WGS84 +no_defs") %>% 
@@
 
-ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+OcuP <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
     ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
-nudge_x=-5000, nudge_y = 1000)+ 
-  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)
+nudge_x=-5000, nudge_y = 1000)+   theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + 
+  labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")
+
+```
+
+```{r, fig.height=10}
+
+layout <- "
+AAAABBB
+AAAABBB
+"
+OcuI + OcuP+plot_layout(design = layout, guides = 'collect') +plot_annotation(tag_levels = 'A')
 

### 2020-11-16 Ms_HabitatAves.Rmd
Figura ocupancia arreglada para inv y primavera con nombre de sitios y patcowrk correcto, falta orden de sp

@@
 nudge_x=-5000, nudge_y = 1000)+ 
-  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "none")
 
@@
     ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
-nudge_x=-5000, nudge_y = 1000)+   theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + 
-  labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=2)+ theme(legend.position = "bottom")
+nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)
 
@@
 
-```{r, fig.height=10}
+```{r, fig.width=13, fig.height=6}
 
 layout <- "
-AAAABBB
-AAAABBB
+AAAA
+BBB#
 "
-OcuI + OcuP+plot_layout(design = layout, guides = 'collect') +plot_annotation(tag_levels = 'A')
+OcuI + OcuP+plot_annotation(tag_levels = 'A')+ plot_layout(design = layout)
 

### 2020-11-19 Figuras presentacion lab.Rmd
fig occu x sp

--- 2020-11-16 Ms_HabitatAves.Rmd
@@
 ---
-title: "Bird species composition in coastal urban habitats"
+title: "Figuras presentacion Lab, Nov 2020"
 output:
-  bookdown::word_document2:
-    reference_docx: "Para_Template.docx"
-bibliography: tesis_ref_2020.bib
+  pdf_document
 ---
@@
 library(rasterVis)
+library(sf)
+library(raster)
 
@@
 
-### Introduction
-
-1. Establish importance of the field- provide background, keywords- present the problem
-
-[Establish the importance of this research topic]
-During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
-
-[Provide general background information]
-Urbanization is a complex process that causes profound changes in the ecological functioning of the landscaped gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
-
-[Establish the importance of this research topic, more specific/detailed way]
-Some of these losses of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
-These is because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
-
-[Provide general background information, more specific/detailed way]
-
-Studies suggest that bird communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
-To bird assembles local features are more important than surrounding landscapes @clergeau2001urban,
-
-2. Previous an current research and contributions
-
-[Describe general problem area or the current research focus of the field]
-
-Cities in coastal areas combine many key economic activities such as marine transport, shipping of goods, fishing, recreation, and tourism.
-These areas are attractive for people to settle and by 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017].
-Species and ecosystems of coastal areas are often threatened by the growing urbanization, the landscape change, and also by the vulnerable that this area is naturally
-
-[Provide transition between the general problem area and the literature review]
-
-Even this scenario, urbanization has been mostly focus in terrestrial aspects, and even when more than the half of the cities in the world rise on the coast, there is a lack of studies addressing marine and terrestrial interactions.
-
-3. Locate the gap-describe the problem to address-present a prediction to be tested
-
-[Provide brief overview of key research projects in this area]
-Urban homogenization has been studied in cities, focused in terrestrial variables
-Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats
-
-[Describe gaps in the research]
-There is a gap in studies that focus in coastal ecotone and the influence of urban areas
-focusing on marine and terrestrial interaction of species in an urbanized area and how birds use this as habitats
-
-[Describe paper itself]
-This research aim to identified the use of coastal urban habitats by birds describing the composition of species in different environments, considering bird species origin (marine and terrestrial).
-with the aim of: 1.
-Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2.
-identify how urbanization affects those bird assembles, 3.
-Evaluate iconic bird species habitat occupation, and 4.
-describe bird behavior in those habitats
-
-4. Describe the present paper
-[Give details about the methodology reported in the paper]
-The present study was carried out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
-
-[Announces the findings]
-Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inland bird species
-
-### Methodology
-
 ```{r, results='hide'}
@@
 
-1. Overview-purpose of the work-give source of material/equipment used
-
-[General overview of this section]
-In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on corrected bird presences, and analysed bird assembles in those environment.
-
-[Provide background information and justification]
-The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
-The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
-
-[Provide an overview of the procedure/method itself]
-Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu].
-To estimate species assembles for habitats, the vegan package [@Vegan] was used.
-Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].
-
-2. Details about materials and methods- justify choices
-
-[Provide details about what was done and used and shows that care was taken]
-Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1).
-Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
-Surveys were conducted randomly during sunrise and the three hours later for 10 minutes, registering species and behaviour.
-
-Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
-We tested a model where seasonality has a interaction with the habitats defined in this research.
-
-[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-
-Bird commmunities for each habitat were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with DiversityOcuppancy package [@divoccu](see table 1).
-We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
-To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
-
-In order to understand habitat use by birds, bird activities were counted by each habitat
-
-Fit of environmental variables on species ordination was also tested.
-
-3. Relate to other studies
-
-[Describe what was done by referring to existing mehods in the literature]
-To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.
-
-[Provide more detailed information about the method and show that was a good choice]
-Covariables of detection and occupation are describedd in table 1.
-
-4. Indicate where problems occurred
-
-[Mention possible difficulty in the methodology]
-
 ```{r}
@@
 
-### Results
-
-1. Revisting the research aim/existing research
-Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.
-
-2. General overview of results
-The six coastal urban habitats shows distingible birs species assembles where only a few species contribute to the difference between them.
-For these habitats, bird assemblages differ between winter and spring seasons.
-Environmental variables can be responsible of both community identities and use of habitat idiviualy
-
-3. Invitations to view results
-
-Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla 3).
-Distribution of sites in graphical NMDS (Fig.
-\@ref(fig:NMDS)) showedthat both seassons presented differences in abundance of species mostly in the inland sites.
-Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
-
 ```{r NMDS, fig.width=9, fig.height=4, fig.cap="Sites distribution in A winter and B spring"}
@@
 Inv <- ggplot(Tidy_Inv_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
-  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))
+  scale_color_manual(name="Coastal habitats",  values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + ggtitle('Invierno')
 
@@
 Prim <-ggplot(Tidy_Prim_nmds2_bray)+geom_point(aes(x=MDS1, y=MDS2, color=AMBIENTE))+theme_classic() + 
-  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33'))
+  scale_color_manual(name="Coastal habitats", values = c('#e41a1c','#377eb8','#4daf4a','#984ea3','#ff7f00','#ffff33')) + ggtitle('Primavera')
 
 #Ambos graficos con paquete patchwork
-Inv+Prim + plot_annotation(tag_levels = 'A')+ plot_layout(guides = 'collect')
+Inv+Prim + plot_layout(guides = 'collect')
 ```
-
-Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different.
-There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
-\@ref(fig:ANOSIM))
 
@@
 Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
-  xlab("Variables")+ ylab("Dissimmilarity rank")
+  xlab("Variables")+ ylab("Dissimmilarity rank")+ ggtitle('Invierno')
 
 Prim <- ggplot()+ geom_boxplot(aes(Anosim_Diss_Prim2$class.vec, y=Anosim_Diss_Prim2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
- xlab("Variables")+ ylab("Dissimmilarity rank")
+ xlab("Variables")+ ylab("Dissimmilarity rank") + ggtitle('Primavera')
 
-Inv / Prim +plot_annotation(tag_levels = 'A')
+Inv / Prim 
 ```
 
-4. Specific/key results in details
-
 Both sampled seasons showed that few species contribute to differences between habitats.
-Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
-(For a complete species list of SIMPER, see Suplementary material).
-
-Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
-
-Species such as xxx, showed differernces in habitat use between seasons.
-(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))
+Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*
 
@@
 
-library(sf)
-library(raster)
-library(ggrepel)
 Pelecanus <-read_rds("PredInv_Pelecanus_thagus.rds")
@@
 
-Species_DF <- temp %>% reduce(full_join) %>% dplyr::relocate(Pelecanus, .after = y) %>% pivot_longer(Pelecanus:Sephanoides, names_to = "Species", values_to = "Occupancy")
+Species_DFInv <- temp %>% reduce(full_join) %>% dplyr::relocate(Pelecanus, .after = y) %>% pivot_longer(Pelecanus:Sephanoides, names_to = "Species", values_to = "Occupancy")
 
@@
 
-OcuI <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+OcuI <- ggplot() + geom_raster(data = Species_DFInv, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
     ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
@@
 ```
+
+during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
 
@@
 
-Species_DF <- temp %>% reduce(full_join) %>% dplyr::relocate(Columba, .after = y) %>% pivot_longer(Columba:Pelecanus, names_to = "Species", values_to = "Occupancy")
+Species_DFPrim <- temp %>% reduce(full_join) %>% dplyr::relocate(Columba, .after = y) %>% pivot_longer(Columba:Pelecanus, names_to = "Species", values_to = "Occupancy")
 
@@
 
-OcuP <- ggplot() + geom_raster(data = Species_DF, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+OcuP <- ggplot() + geom_raster(data = Species_DFPrim, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
     ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, 
@@
 
-During winter, community assemblages were explain by three environmental variables: coastal urban habitats, crops and tree plantations. 
-In spring, variables were coastal urban habitats and native forest.
+```{r Pelecanus}
+
+Species_DFInv_Pel <- Species_DFInv %>% dplyr::filter(Species=="Pelecanus")
+Species_DFPrim_Pel <- Species_DFPrim %>% dplyr::filter(Species=="Pelecanus")
+
+OcuI_Pel <- ggplot() + geom_raster(data = Species_DFInv_Pel, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "none") + ggtitle('Invierno')
+
+OcuP_Pel <- ggplot() + geom_raster(data = Species_DFPrim_Pel, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1) + ggtitle('Primavera')
+
+OcuI_Pel+OcuP_Pel
+```
+
+```{r Larus}
+Species_DFInv_Larus <- Species_DFInv %>% dplyr::filter(Species=="Larus")
+Species_DFPrim_Larus <- Species_DFPrim %>% dplyr::filter(Species=="Larus")
+
+OcuI_Larus <- ggplot() + geom_raster(data = Species_DFInv_Larus, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "none") + ggtitle('Invierno')
+
+OcuP_Larus <- ggplot() + geom_raster(data = Species_DFPrim_Larus, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1) + ggtitle('Primavera')
+
+OcuI_Larus + OcuP_Larus
+```
+
+```{r Larosterna}
+Species_DFInv_Larosterna <- Species_DFInv %>% dplyr::filter(Species=="Larosterna")
+Species_DFPrim_Larosterna <- Species_DFPrim %>% dplyr::filter(Species=="Larosterna")
+
+OcuI_Larosterna <- ggplot() + geom_raster(data = Species_DFInv_Larosterna, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "none") + ggtitle('Invierno')
+
+OcuP_Larosterna <- ggplot() + geom_raster(data = Species_DFPrim_Larosterna, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1) + ggtitle('Primavera')
+
+OcuI_Larosterna + OcuP_Larosterna
+```
+
+```{r Columba}
+Species_DFInv_Columba <- Species_DFInv %>% dplyr::filter(Species=="Columba")
+Species_DFPrim_Columba <- Species_DFPrim %>% dplyr::filter(Species=="Columba")
+
+OcuI_Columba <- ggplot() + geom_raster(data = Species_DFInv_Columba, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "none") + ggtitle('Invierno')
+
+OcuP_Columba <- ggplot() + geom_raster(data = Species_DFPrim_Columba, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1) + ggtitle('Primavera')
+
+OcuI_Columba + OcuP_Columba
+```
 
@@
 
-species for each habitat
-Occupancy model map show
-
 ```{r}
@@
 ```
-
-Finally, use of these habitats can be seen with the activity record of bird species.
 
@@
 
-Most of the species were detected during the fliying, however some were founded in particular activities.
+```{r CompLarus, fig.height=8, fig.width=10}
+ComportamientoInv <- read_rds("ComportamientoInv.rds")
+I <-ggplot(ComportamientoInv) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
 
-5. Comparisons with results in other research
+ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
 
-Occupancy models for specific species
+P <-ggplot(ComportamientoPrim) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
 
-6. problems with results
+layout <- "
+AAAAAAAA
+BBBBBBB#
+"
+I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
 
-7. Possible implications with results
-
-### Discussion/Conclusion
-
-1. Revising previous research- summaries
-[Revisit previous research]
-[Revisit Introduction to recall specific weakness in methodology used in previous studies]
-
-2. Mapping 
-[Revisit methodology used in this study]
-[Revisit and summaries the results]
-[Show where and how the present work fits into the research "map" in this field]
-
-3. Achievements/contributions- refining implications
-[Recall an aspect of the results that represents a positive achievement or contribution of this work]
-[Focus in the meaning and implications of the achievements in this work]
-[Note if one of the achievement or contributions of the work is a novelty]
-[Describe implications of the results, including possible applications]
-
-4. Limitations-current and future work-applications
-[Describe limitations which should direct future research]
-[Suggest a specific area to be addressed in future work]
-
-### References
+```

### 2020-11-19 Figuras presentacion lab.Rmd
Fig comp x sp

@@
 
-```{r Pelecanus}
+```{r Pelecanus, fig.width=12}
 
@@
 
-OcuI_Pel+OcuP_Pel
+OcuI_Pel/ OcuP_Pel
 ```
 
-```{r Larus}
+```{r Larus, fig.width=12}
 Species_DFInv_Larus <- Species_DFInv %>% dplyr::filter(Species=="Larus")
@@
 
-OcuI_Larus + OcuP_Larus
+OcuI_Larus / OcuP_Larus
 ```
 
-```{r Larosterna}
+```{r Larosterna, fig.width=12}
 Species_DFInv_Larosterna <- Species_DFInv %>% dplyr::filter(Species=="Larosterna")
@@
 
-OcuI_Larosterna + OcuP_Larosterna
+OcuI_Larosterna / OcuP_Larosterna
 ```
 
-```{r Columba}
+```{r Columba, fig.width=12}
 Species_DFInv_Columba <- Species_DFInv %>% dplyr::filter(Species=="Columba")
@@
 
-OcuI_Columba + OcuP_Columba
+OcuI_Columba / OcuP_Columba
 ```
@@
   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")
 
@@
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+ ggtitle("Primavera")
 
@@
 "
-I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
+I + P + plot_layout(design = layout)
 
@@
 
-```{r CompLarus, fig.height=8, fig.width=10}
-ComportamientoInv <- read_rds("ComportamientoInv.rds")
-I <-ggplot(ComportamientoInv) + 
+```{r CompLarus, fig.height=7, fig.width=7}
+ComportamientoInv_Larus <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")
+
+I <-ggplot(ComportamientoInv_Larus) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")
 
-ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
+ComportamientoPrim_Larus <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")
 
-P <-ggplot(ComportamientoPrim) + 
+P <-ggplot(ComportamientoPrim_Larus) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
+  ggtitle("Primavera")
 
-layout <- "
-AAAAAAAA
-BBBBBBB#
-"
-I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
+I / P 
+```
 
+```{r CompPele, fig.height=7, fig.width=7}
+ComportamientoInv_Pele <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")
+
+I <-ggplot(ComportamientoInv_Pele) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")
+
+ComportamientoPrim_Pele <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")
+
+P <-ggplot(ComportamientoPrim_Pele) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
+  ggtitle("Primavera")
+
+I / P 
 ```
+
+```{r CompLarosterna, fig.height=7, fig.width=7}
+ComportamientoInv_Larosterna <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")
+
+I <-ggplot(ComportamientoInv_Larosterna) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")
+
+ComportamientoPrim_Larosterna <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")
+
+P <-ggplot(ComportamientoPrim_Larosterna) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
+  ggtitle("Primavera")
+
+I / P 
+```
+
+```{r CompColumba, fig.height=7, fig.width=7}
+ComportamientoInv_Columba <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Columba_livia")
+
+I <-ggplot(ComportamientoInv_Columba) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior") +ggtitle("Invierno")
+
+ComportamientoPrim_Columba <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Columba_livia")
+
+P <-ggplot(ComportamientoPrim_Columba) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")+
+  ggtitle("Primavera")
+
+I / P 
+```

### 2020-11-20 Figuras presentacion lab.Rmd
Arreglo paleta colores graficos comportamiento x sp

--- 2020-11-19 Figuras presentacion lab.Rmd
@@
 ```{r Comportamineto, fig.height=8, fig.width=10}
+
+PalleteInv <- c("Flying"= '#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c',  "In the foliage"='#33a02c', "Perching"='#ff7f00',"Standing over a thing"='#fb9a99' )
+PalletePrim <- c("Flying"='#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c', "In the foliage"='#33a02c', "Perching"='#ff7f00', "Standing over a thing"='#fb9a99', "Other"='#fdbf6f', "Nesting"='#b2df8a')
+
 ComportamientoInv <- read_rds("ComportamientoInv.rds")
@@
   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
 
@@
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+ ggtitle("Primavera")
 
@@
 
-```{r CompLarus, fig.height=8, fig.width=10}
-ComportamientoInv <- read_rds("ComportamientoInv.rds")
-I <-ggplot(ComportamientoInv) + 
+```{r CompLarus, fig.height=7, fig.width=7}
+
+PalleteInv <- c("Flying"= '#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c',  "In the foliage"='#33a02c', "Perching"='#ff7f00',"Standing over a thing"='#fb9a99' )
+PalletePrim <- c("Flying"='#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c', "In the foliage"='#33a02c', "Perching"='#ff7f00', "Standing over a thing"='#fb9a99', "Other"='#fdbf6f', "Nesting"='#b2df8a')
+
+ComportamientoInv_Larus <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")
+
+I <-ggplot(ComportamientoInv_Larus) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
 
-ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
+ComportamientoPrim_Larus <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larus_dominicanus")
 
-P <-ggplot(ComportamientoPrim) + 
+P <-ggplot(ComportamientoPrim_Larus) + 
   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+  scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+
+  ggtitle("Primavera")
 
-layout <- "
-AAAAAAAA
-BBBBBBB#
-"
-I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
+I / P 
+```
 
+```{r CompPele, fig.height=7, fig.width=7}
+
+PalleteInv <- c("Flying"= '#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c',  "In the foliage"='#33a02c', "Perching"='#ff7f00',"Standing over a thing"='#fb9a99' )
+PalletePrim <- c("Flying"='#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c', "In the foliage"='#33a02c', "Perching"='#ff7f00', "Standing over a thing"='#fb9a99', "Other"='#fdbf6f', "Nesting"='#b2df8a')
+ComportamientoInv_Pele <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")
+
+I <-ggplot(ComportamientoInv_Pele) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
+
+ComportamientoPrim_Pele <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Pelecanus_thagus")
+
+P <-ggplot(ComportamientoPrim_Pele) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values =PalletePrim, name="Bird behavior")+
+  ggtitle("Primavera")
+
+I / P 
 ```
+
+```{r CompLarosterna, fig.height=7, fig.width=7}
+PalleteInv <- c("Flying"= '#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c',  "In the foliage"='#33a02c', "Perching"='#ff7f00',"Standing over a thing"='#fb9a99' )
+PalletePrim <- c("Flying"='#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c', "In the foliage"='#33a02c', "Perching"='#ff7f00', "Standing over a thing"='#fb9a99', "Other"='#fdbf6f', "Nesting"='#b2df8a')
+ComportamientoInv_Larosterna <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")
+
+I <-ggplot(ComportamientoInv_Larosterna) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
+
+ComportamientoPrim_Larosterna <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Larosterna_inca")
+
+P <-ggplot(ComportamientoPrim_Larosterna) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+
+  ggtitle("Primavera")
+
+I / P 
+```
+
+```{r CompColumba, fig.height=7, fig.width=7}
+
+PalleteInv <- c("Flying"= '#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c',  "In the foliage"='#33a02c', "Perching"='#ff7f00',"Standing over a thing"='#fb9a99' )
+PalletePrim <- c("Flying"='#a6cee3', "On the water"='#1f78b4', "Walking"='#e31a1c', "In the foliage"='#33a02c', "Perching"='#ff7f00', "Standing over a thing"='#fb9a99', "Other"='#fdbf6f', "Nesting"='#b2df8a')
+
+ComportamientoInv_Columba <- read_rds("ComportamientoInv.rds") %>% dplyr::filter(Cientifico=="Columba_livia")
+
+I <-ggplot(ComportamientoInv_Columba) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") + ggtitle("Invierno")
+
+ComportamientoPrim_Columba <- read_rds( "ComportamientoPrim.rds") %>% dplyr::filter(Cientifico=="Columba_livia")
+
+P <-ggplot(ComportamientoPrim_Columba) + 
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+  scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+ 
+  ggtitle("Primavera")
+
+I / P 
+```

### 2020-11-21 Figuras presentacion lab.Rmd
Algunos arreglos occupancia grupo sp

@@
 ```
+```{r Sp_una_estacion, fig.width=12}
+
+Sp_una_estacion_DFInv <- Species_DFInv %>% dplyr::filter(Species %in% c("Leucophaeus","Coragyps",  "Turdus", "Sephanoides")) %>% 
+  mutate(Species=case_when(Species=="Leucophaeus"~"Leucophaeus modestus",
+                           Species=="Coragyps"~"Coragyps atratus",
+                           Species=="Sephanoides"~"Sephanoides sephanoides",
+                           Species=="Turdus"~"Turdus falcklandii"))
+Sp_una_estacion_DFPrim <- Species_DFPrim %>% dplyr::filter(Species %in% c("Leucophaeus", "Phalacrocorax")) %>% 
+  mutate(Species=case_when(Species=="Phalacrocorax"~"Phalacrocorax bougainvillii",
+                           Species=="Leucophaeus"~"Leucophaeus pipixcan"))
+
+OcuI_Sp_una_estacion <- ggplot() + geom_raster(data = Sp_una_estacion_DFInv, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1)+ theme(legend.position = "right") + ggtitle('Invierno')
+
+OcuP_Sp_una_estacion <- ggplot() + geom_raster(data = Sp_una_estacion_DFPrim, aes(x = x, y = y, fill = Occupancy)) + geom_sf(data = Sitios, color="red") +
+    ggrepel::geom_text_repel(data = Sitios,  aes(label = Sitio,  geometry = geometry),  stat = "sf_coordinates", force = 1, nudge_x=-5000, nudge_y = 1000)+ 
+  theme_classic() + scale_fill_viridis_c("Occupancy", option = "plasma", direction = -1) + labs(x = NULL, y = NULL) + facet_wrap(~Species, nrow=1) + ggtitle('Primavera')
+
+layout <- "
+AAAA
+BBB#
+"
+
+OcuI_Sp_una_estacion+ OcuP_Sp_una_estacion + plot_layout(design = layout) 
+```
 
@@
   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno") +ylim(c(0,250))
 
@@
   scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+
-  ggtitle("Primavera")
+  ggtitle("Primavera")  +ylim(c(0,250))
 
@@
 I <-ggplot(ComportamientoInv_Pele) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico)+  
   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")  +ylim(c(0, 45))
 
@@
 P <-ggplot(ComportamientoPrim_Pele) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico)+  
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
   scale_fill_manual(aesthetics = "fill", values =PalletePrim, name="Bird behavior")+
-  ggtitle("Primavera")
+  ggtitle("Primavera")  +ylim(c(0, 45))
 
@@
 I <-ggplot(ComportamientoInv_Larosterna) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico)+  
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") +ggtitle("Invierno")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") + ggtitle("Invierno") + ylim(c(0, 50))
 
@@
 P <-ggplot(ComportamientoPrim_Larosterna) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico)+  
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
   scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+
-  ggtitle("Primavera")
+  ggtitle("Primavera") + ylim(c(0, 50))
 
@@
   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") + ggtitle("Invierno")
+  scale_fill_manual(aesthetics = "fill", values = PalleteInv, name="Bird behavior") + ggtitle("Invierno")  +ylim(c(0, 170))
 
@@
   scale_fill_manual(aesthetics = "fill", values = PalletePrim, name="Bird behavior")+ 
-  ggtitle("Primavera")
+  ggtitle("Primavera") +ylim(c(0,170))
 

### 2020-11-21 Tablas_Ms_HabitatAves.Rmd
Algunos arreglos occupancia grupo sp

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 library(kableExtra)
 library(tidyverse)
+```
+
+```{r,results='asis'}
+#Modelo 1= Abundancia ~ Estacion * Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
+#Modelo 2= Abundancia ~ Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves )           #AIC 18241.0
+DF_seasson <- tibble(Model= c("$Estacion \\times Especie + Ambiente+ \\frac{1}{Sitio}$", "$Especie + Ambiente + \\frac{1}{Sitio}$"), AIC= c(17716.1, 18241.0))
+
+kable(DF_seasson, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic")
+
+```
+
+```{r, results='asis'}
+Inv_DF <-  read.csv("ResumenSimper_Inv2.csv") %>% as.data.frame() 
+kable(Inv_DF, booktabs = T)
+
+```
+
+```{r, results='asis'}
+Prim_DF <-  read.csv("ResumenSimper_Prim2.csv") %>% as.data.frame()
+kable(Prim_DF, booktabs = T)
+
 ```

### 2020-11-23 Figuras presentacion lab.Rmd
Algunos detalles apra presentacion de viernes27 en lab

@@
          AMBIENTE= str_replace(AMBIENTE,"PLAYA NATURAL", "Natural beach"))
+```
+
+```{r}
+
+#Abund_Prim <-ggplot(AvesInv2, aes(x=Sitio, y=Riqueza)) + geom_col(aes(fill=Habitat), position="dodge") + facet_wrap(~AMBIENTE, scales = "free_x", ncol=2)+
+#  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
+#  xlab("Sitios de muestreo")+   theme(axis.text.x=element_blank()) + geom_hline(data = Riqueza_Prom,aes(yintercept = Riqueza, color = Habitat), lty=2)
+
 ```

### 2020-11-23 Exploración_enfocada.R

@@ -29,7 +29,8 @@ AvesInv <- left_join(x=AvesInv, y= BirdNames)
 
 #Grafico riqueza especies invierno
 AvesInv_riq <- AvesInv %>% group_by(Sitio, AMBIENTE, Habitat) %>% summarise(Riqueza = n())
-AvesInv_riq <- AvesInv_riq %>% mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL"))
+AvesInv_riq <- AvesInv_riq %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
 
 Riqueza_Prom <- AvesInv_riq %>% group_by(AMBIENTE, Habitat) %>% summarise(Riqueza = mean(Riqueza))
 
@@ -62,12 +63,14 @@ AvesPrim <- left_join(x=AvesPrim, y= BirdNames)
 
 #Grafico riqueza especies primavera
 AvesPrim_riq <- AvesPrim %>% group_by(Sitio, AMBIENTE, Habitat) %>% summarise(Riqueza = n())
-AvesPrim_riq <- AvesPrim_riq %>% mutate(AMBIENTE=fct_relevel(AMBIENTE, "URBANO","VERDE", "ROQUERIO INTERVENIDO","PLAYA INTERVENIDA",  "ROQUERIO NATURAL"))
+AvesPrim_riq <- AvesPrim_riq %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
 
 Riqueza_Prom <- AvesPrim_riq %>% group_by(AMBIENTE, Habitat) %>% summarise(Riqueza = mean(Riqueza))
 
 
[…]

### 2020-12-02 Figuras presentacion lab.Rmd
GLM de aves por ambientes considerando modificacion de habitat

@@
 library(MASS)
-library(ggplot2)
 library(ggrepel)
@@
 library(raster)
+
+```
+
+```{r}
+# riqueza promedio por ambiente+ ds... dos temporadas
+# del documento RiquezaAves_ambiente.R
+
+#Preparacion datos
+BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
+
+#Riqueza invierno
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))%>% rename(Nombre =Especie)
+AvesInv <- AvesInv %>% group_by(Sitio, Nombre, AMBIENTE) %>% summarise(n=sum(N_individuos)) %>% 
+  mutate(Nombre= str_replace(Nombre, "PELICANO", "PELICANO COMÚN"),
+         Nombre= str_replace(Nombre, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Nombre= str_replace(Nombre, "LILEN", "LILE"))
+
+AvesInv <- left_join(x=AvesInv, y= BirdNames) 
+AvesInv_riq <- AvesInv %>% group_by(AMBIENTE,Sitio, Habitat) %>% summarise(Riqueza = n())
+
+AvesInv_riq2 <- AvesInv_riq %>% group_by(AMBIENTE, Habitat) %>% summarise_at("Riqueza", .funs = list(mean=mean, max=max, min=min)) %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
+
+# Riqueza primavera
+AMB_nombres <-read_rds("Occdata_occu.rds") %>% dplyr::select(Sitio, AMBIENTE)
+
+AvesPrim <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves sep-oct 2019/Monitoreo punto/Registro_aves_veranoFINAL.csv")%>% 
+  rename(Nombre =Especie) 
+AvesPrim <- left_join(AvesPrim, AMB_nombres)
+AvesPrim <- AvesPrim %>% group_by(Sitio, Nombre, AMBIENTE) %>% summarise(n=sum(N_individuos)) %>% 
+  mutate(Nombre= str_replace(Nombre, "PELICANO", "PELICANO COMÚN"),
+         Nombre= str_replace(Nombre, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Nombre= str_replace(Nombre, "LILEN", "LILE"),
+         Nombre= str_replace(Nombre, "CAHUIL", "GAVIOTA CAHUIL")) %>% 
+  mutate(AMBIENTE= str_replace(AMBIENTE, "ROCA INTERVENIDA", "ROQUERIO INTERVENIDO"),
+         AMBIENTE= str_replace(AMBIENTE, "ROCA NATURAL", "ROQUERIO NATURAL"))
+
+AvesPrim <- left_join(x=AvesPrim, y= BirdNames) 
+AvesPrim_riq <- AvesPrim %>% group_by(AMBIENTE,Sitio, Habitat) %>% summarise(Riqueza = n())
+
+AvesPrim_riq2 <- AvesPrim_riq %>% group_by(AMBIENTE, Habitat) %>% summarise_at("Riqueza", .funs = list(mean=mean, max=max, min=min)) %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
+
+```
+
+```{r}
+
+A <-ggplot(AvesInv_riq2, aes(x=AMBIENTE, y=mean)) + geom_col(aes(fill=Habitat), position="dodge") +
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
+  xlab(" ")+ geom_errorbar(aes(ymin=min, ymax=max), position = position_dodge2(width = 0.1, padding = 0.7))+ 
+  facet_wrap(~AMBIENTE, scales = "free_x", ncol=2) +   theme(axis.text.x=element_blank())
+
+B <-ggplot(AvesPrim_riq2, aes(x=AMBIENTE, y=mean)) + geom_col(aes(fill=Habitat), position="dodge") +
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
+  xlab(" ")+ geom_errorbar(aes(ymin=min, ymax=max), position = position_dodge2(width = 0.1, padding = 0.7))+ 
+  facet_wrap(~AMBIENTE, scales = "free_x", ncol=2) +   theme(axis.text.x=element_blank())
+
+#A+B + plot_layout(guides = 'collect')
+```
+
+```{r}
+
+# GLMmixto con variables aleatorias
+library(MuMIn)
+
+nuevoinv <- AvesInv_riq %>% ungroup() %>% mutate(Temporada="Invierno") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Playa",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Roquerio",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Terrestre")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Intervenido",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+nuevoprim <- AvesPrim_riq %>% ungroup() %>% mutate(Temporada="Primavera") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Playa",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Roquerio",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Terrestre")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Intervenido",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+Riqueza <- bind_rows(nuevoinv, nuevoprim)
+
+# Modelo
+Modelo <- glm(Riqueza ~ Temporada + Ambiente + Grado_modificacion + Habitat +  Temporada:Ambiente + Ambiente:Grado_modificacion , family = poisson, data =Riqueza ) 
+options(na.action = "na.fail")
+#Seleccion de modelos
+
+Selected <- dredge(Modelo, m.lim = c(0, floor(nrow(Riqueza)/10)))
+
+Final <- subset(Selected, delta < 2)
+Final_conpeso <- model.sel(Final)
+
+Final_DF <- as.data.frame(Final_conpeso)
+kable(Final_DF, digits = 2, booktabs=T) %>%  kable_styling(latex_options = c("scale_down"), font_size = 9)
+
+NewData <- Riqueza %>% dplyr::select(-Riqueza, -Sitio, -AMBIENTE) %>% distinct()
+
+Predicciones <- predict(Modelo, NewData, type = "response",se.fit = T)
+
+NewData$Pred <- Predicciones$fit
+NewData$SE <- Predicciones$se.fit
+
+ggplot(NewData, aes(y=Pred, x=Habitat)) + geom_col(aes(fill=Grado_modificacion ), position="dodge") +
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies")+
+   geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
+  facet_grid(Ambiente ~ Temporada) + xlab("Habitat origen de especies aves")
 

### 2020-12-02 GLM_aves.R

@@ -1,4 +1,4 @@
-# Verificar diferencias no estacionales para aves
+# Verificar diferencias no estacionales para aves considderando especies
 #mediante GLMmixto x estación
 
 library(tidyverse)

### 2020-12-02 Graficos_MediaSD.R

@@ -6,7 +6,7 @@ library(ggplot2)
 
 # RIQUEZA DE ESPECIES: Media de sitios por ambiente y sd
 
-#PolaRRR
+# Graficos polares
 
 #invierno
 

### 2020-12-02 RiquezaAves_ambiente.R

@@ -1,0 +1,111 @@
+# para grafico figura 1 resultados
+# riqueza promedio por ambiente+ ds... dos temporadas
+
+library(tidyverse)
+library(patchwork)
+
+#Preparacion datos
+BirdNames <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/BirdNames.csv") %>% dplyr::select(-X1)
+
+#Riqueza invierno
+AvesInv <- read_csv("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Muestreo aves jun-jul 2019/Monitoreo_punto/Reg_completo_aves_inv.csv") %>% 
+  dplyr::mutate(Especie = str_trim(str_remove_all(Especie,pattern = "JUVENIL")))%>% rename(Nombre =Especie)
+AvesInv <- AvesInv %>% group_by(Sitio, Nombre, AMBIENTE) %>% summarise(n=sum(N_individuos)) %>% 
+  mutate(Nombre= str_replace(Nombre, "PELICANO", "PELICANO COMÚN"),
+         Nombre= str_replace(Nombre, "JOTE NEGRO", "JOTE CABEZA NEGRA"),
+         Nombre= str_replace(Nombre, "LILEN", "LILE"))
+
+AvesInv <- left_join(x=AvesInv, y= BirdNames) 
+
+#Grafico riqueza especies invierno
+AvesInv_riq <- AvesInv %>% group_by(AMBIENTE,Sitio, Habitat) %>% summarise(Riqueza = n())
+
+AvesInv_riq2 <- AvesInv_riq %>% group_by(AMBIENTE, Habitat) %>% summarise_at("Riqueza", .funs = list(mean=mean, max=max, min=min)) %>% 
+  mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
+
+ggplot(AvesInv_riq2, aes(x=AMBIENTE, y=mean)) + geom_col(aes(fill=Habitat), position="dodge") +
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies invierno")+
[…]

### 2020-12-04 Ms_HabitatAves.Rmd
permanova

@@
 Prim_nmds2_bray <-suppressMessages(metaMDS(AvesPrim2,autotransform = FALSE, distance="bray", k=2, try=20, trymax=100, wascores=FALSE, trace=1, plot=FALSE)) 
+```
+
+```{r}
+#Inv
+
+Mod0 <- adonis2(AvesInv2 ~ 1, data = Amb, by = "terms")
+Mod1 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")###################### Menor AIC
+Mod2 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
+Mod3 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")
+Mod4 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
+Mod5 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
+
+AICc.PERMANOVA2 <- function(adonis2.model) {
+
+  # check to see if object is an adonis2 model...
+
+  if (is.na(adonis2.model$SumOfSqs[1]))
+    stop("object not output of adonis2 {vegan} ")
+
+  # Ok, now extract appropriate terms from the adonis model Calculating AICc
+  # using residual sum of squares (RSS or SSE) since I don't think that adonis
+  # returns something I can use as a likelihood function... maximum likelihood
+  # and MSE estimates are the same when distribution is gaussian See e.g.
+  # https://www.jessicayung.com/mse-as-maximum-likelihood/;
+  # https://towardsdatascience.com/probability-concepts-explained-maximum-likelihood-estimation-c7b4342fdbb1
+  # So using RSS or MSE estimates is fine as long as the residuals are
+  # Gaussian https://robjhyndman.com/hyndsight/aic/ If models have different
+  # conditional likelihoods then AIC is not valid. However, comparing models
+  # with different error distributions is ok (above link).
+
+  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
+  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
+
+  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  # AIC : 2*k + n*ln(RSS/n)
+  # AICc: AIC + [2k(k+1)]/(n-k-1)
+
+  # based on https://en.wikipedia.org/wiki/Akaike_information_criterion;
+  # https://www.statisticshowto.datasciencecentral.com/akaikes-information-criterion/ ;
+  # https://www.researchgate.net/post/What_is_the_AIC_formula;
+  # http://avesbiodiv.mncn.csic.es/estadistica/ejemploaic.pdf;
+  # https://medium.com/better-programming/data-science-modeling-how-to-use-linear-regression-with-python-fdf6ca5481be
+
+  AIC <- 2*k + nn*log(RSS/nn)
+  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
+
+  output <- data.frame(AICc = AICc, k = k, N = nn)
+
+  return(output)
+
+}
+
+DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
+
+DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
+DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
+DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
+DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
+DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
+DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
+
+```
+
+```{r}
+#Prim
+
+Mod0 <- adonis2(AvesPrim2 ~ 1, data = Amb, by = "terms")
+Mod1 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")
+Mod2 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
+Mod3 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")########################     Menor AIC
+Mod4 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
+Mod5 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
+
+AICc.PERMANOVA2 <- function(adonis2.model) {
+
+  # check to see if object is an adonis2 model...
+
+  if (is.na(adonis2.model$SumOfSqs[1]))
+    stop("object not output of adonis2 {vegan} ")
+
+  # Ok, now extract appropriate terms from the adonis model Calculating AICc
+  # using residual sum of squares (RSS or SSE) since I don't think that adonis
+  # returns something I can use as a likelihood function... maximum likelihood
+  # and MSE estimates are the same when distribution is gaussian See e.g.
+  # https://www.jessicayung.com/mse-as-maximum-likelihood/;
+  # https://towardsdatascience.com/probability-concepts-explained-maximum-likelihood-estimation-c7b4342fdbb1
+  # So using RSS or MSE estimates is fine as long as the residuals are
+  # Gaussian https://robjhyndman.com/hyndsight/aic/ If models have different
+  # conditional likelihoods then AIC is not valid. However, comparing models
+  # with different error distributions is ok (above link).
+
+  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
+  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
+
+  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  # AIC : 2*k + n*ln(RSS/n)
+  # AICc: AIC + [2k(k+1)]/(n-k-1)
+
+  # based on https://en.wikipedia.org/wiki/Akaike_information_criterion;
+  # https://www.statisticshowto.datasciencecentral.com/akaikes-information-criterion/ ;
+  # https://www.researchgate.net/post/What_is_the_AIC_formula;
+  # http://avesbiodiv.mncn.csic.es/estadistica/ejemploaic.pdf;
+  # https://medium.com/better-programming/data-science-modeling-how-to-use-linear-regression-with-python-fdf6ca5481be
+
+  AIC <- 2*k + nn*log(RSS/nn)
+  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
+
+  output <- data.frame(AICc = AICc, k = k, N = nn)
+
+  return(output)
+
+}
+
+DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
+
+DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
+DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
+DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
+DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
+DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
+DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
+
 ```

### 2020-12-04 Exploración_enfocada.R

@@ -1,4 +1,4 @@
-#Exploracion datos monitoreo visual aves
+a#Exploracion datos monitoreo visual aves
 
 #reorden y vegan con preguntas generales Stefan tras reunion 18 agosot 2020
 

### 2020-12-04 RiquezaAves_ambiente.R

@@ -89,17 +89,13 @@ options(na.action = "na.fail")
 #Seleccion de modelos
 
 Selected <- dredge(Modelo, m.lim = c(0, floor(nrow(Riqueza)/10)))
-
 Final <- subset(Selected, delta < 2)
 Final_conpeso <- model.sel(Final)
 
 Final_DF <- as.data.frame(Final_conpeso)
-kable(Final_DF, digits = 2, booktabs=T) %>%  kable_styling(latex_options = c("scale_down"), font_size = 9)
-
-
+#kable(Final_DF, digits = 2, booktabs=T) %>%  kable_styling(latex_options = c("scale_down"), font_size = 9)
 
 NewData <- Riqueza %>% dplyr::select(-Riqueza, -Sitio, -AMBIENTE) %>% distinct()
-
 Predicciones <- predict(Modelo, NewData, type = "response",se.fit = T)
 
 NewData$Pred <- Predicciones$fit
@@ -109,3 +105,4 @@ ggplot(NewData, aes(y=Pred, x=Grado_modificacion)) + geom_col(aes(fill=Habitat),
   scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Riqueza de especies")+
    geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
   facet_grid(Temporada ~ Ambiente) +   theme(axis.text.x=element_blank())
+

### 2020-12-09 Ms_HabitatAves.Rmd
Inclusion de modelo de riqueza inicio MS

@@
 library(rasterVis)
+library(sf)
 
@@
 ### Methodology
+
+```{r}
+
+# GLMmixto con variables aleatorias
+library(MuMIn)
+
+nuevoinv <- AvesInv_riq %>% ungroup() %>% mutate(Temporada="Winter") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Beach",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Rocky shore",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Land")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Modified",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+nuevoprim <- AvesPrim_riq %>% ungroup() %>% mutate(Temporada="Spring") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Beach",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Rocky shore",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Land")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Modified",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+Riqueza <- bind_rows(nuevoinv, nuevoprim)
+
+# Modelo
+Modelo <- glm(Riqueza ~ Temporada + Ambiente + Grado_modificacion + Habitat +  Temporada:Ambiente + Ambiente:Grado_modificacion , family = poisson, data =Riqueza ) 
+options(na.action = "na.fail")
+#Seleccion de modelos
+
+Selected <- dredge(Modelo, m.lim = c(0, floor(nrow(Riqueza)/10)))
+
+Final <- subset(Selected, delta < 2)
+Final_conpeso <- model.sel(Final)
+
+Final_DF <- as.data.frame(Final_conpeso)
+#kable(Final_DF, digits = 2, booktabs=T) %>%  kable_styling(latex_options = c("scale_down"), font_size = 9)
+
+NewData <- Riqueza %>% dplyr::select(-Riqueza, -Sitio, -AMBIENTE) %>% distinct()
+
+Predicciones <- predict(Modelo, NewData, type = "response",se.fit = T)
+
+NewData$Pred <- Predicciones$fit
+NewData$SE <- Predicciones$se.fit
+
+ggplot(NewData, aes(y=Pred, x=Habitat)) + geom_col(aes(fill=Grado_modificacion ), position="dodge") +
+  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Species richness")+
+   geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
+  facet_grid(Ambiente ~ Temporada) + xlab("Habitat of origin")
+
+```
 

### 2020-12-09 README.Rmd
permanova
Inclusion de modelo de riqueza inicio MS

@@
 - graficos de comportamiento desde archivo **Comportamineto_Aves.R**, con abundancia corregida de invierno de **AbundInv_Corregido.rds** y **AbundPrim_Corregido.rds**
+
+## Figuras para presentacion de laboratorio viernes 4 diciembre
+
+Esta presentación surgió con la idea de darle una vuelta a los resultados de este estudio
+Archivo: **Figuras presentacion lab.R**
+Se alimenta de los archivos
+- **RiquezaAves_ambiente.R** tiene riqueza de aves y la riqueza a partir de los modelos de prediccion
+
+## Inclusion de comentarios de la reunion de lab
+
+- Figura prediccion de riqueza al comienzo de resultados en manuscrito y tabla de modelos. Obtenido de **Figuras presentacion lab.R**

### 2020-12-09 Tablas_Ms_HabitatAves.Rmd
Algunos detalles apra presentacion de viernes27 en lab
Inclusion de modelo de riqueza inicio MS

@@
 library(tidyverse)
+```
+
+```{r}
+# GLMmixto con variables aleatorias
+library(MuMIn)
+
+nuevoinv <- AvesInv_riq %>% ungroup() %>% mutate(Temporada="Winter") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Beach",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Rocky shore",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Land")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Modified",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+nuevoprim <- AvesPrim_riq %>% ungroup() %>% mutate(Temporada="Spring") %>% 
+  mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Beach",
+                              AMBIENTE =="ROQUERIO INTERVENIDO"| AMBIENTE =="ROQUERIO NATURAL"~"Rocky shore",
+                              AMBIENTE =="URBANO" | AMBIENTE == "VERDE"~"Land")) %>% 
+  mutate(Grado_modificacion=case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="ROQUERIO INTERVENIDO" |AMBIENTE =="URBANO"~"Modified",
+                                      AMBIENTE == "PLAYA NATURAL"| AMBIENTE =="ROQUERIO NATURAL" |AMBIENTE =="VERDE"~"Natural" ))
+
+Riqueza <- bind_rows(nuevoinv, nuevoprim)
+
+# Modelo
+Modelo <- glm(Riqueza ~ Temporada + Ambiente + Grado_modificacion + Habitat +  Temporada:Ambiente + Ambiente:Grado_modificacion , family = poisson, data =Riqueza ) 
+options(na.action = "na.fail")
+#Seleccion de modelos
+
+Selected <- dredge(Modelo, m.lim = c(0, floor(nrow(Riqueza)/10)))
+
+Final <- subset(Selected, delta < 2)
+Final_conpeso <- model.sel(Final)
+
+Final_DF <- as.data.frame(Final_conpeso)
+kable(Final_DF, digits = 2, booktabs=T) %>%  kable_styling(latex_options = c("scale_down"), font_size = 9)
+
 ```
@@
 kable(DF_occu, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
-#dear silvain
+
 ```

### 2020-12-10 Ms_HabitatAves.Rmd
Arreglo Ms con presentacion Lab

@@
 
-### Introduction
+# Introduction
 
@@
 
-### Methodology
+# Methodology
+
+1. Overview-purpose of the work-give source of material/equipment used
+
+[General overview of this section]
+
+In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition and analised occupancy of key species in those environments.
+
+[Provide background information and justification]
+
+The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
+The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las txx years.
+
+[Provide an overview of the procedure/method itself]
+
+Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu].
+To estimate species assembles for habitats, the vegan package [@Vegan] was used.
+Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].
+
+2. Details about materials and methods- justify choices
+
+[Provide details about what was done and used and shows that care was taken]
+Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: natural rocky shore, modified rocky shore, natural beach, and urbanized beach, green area, and urban center (Fig.
+\@ref(fig:Ambientes)).
+Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
+Between four and six surveys were conducted daily randomly during sunrise and the three hours later for 10 minutes in each site.
+All species that were seen and heard were recorded.
+
+Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
+We tested a model where seasonality has a interaction with the habitats defined in this research.
+
+[Continuing to describe what was done in detail, using language which comunicate that care was taken]
+
+Bird commmunities for each habitat were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with DiversityOcuppancy package [@divoccu](see table 1).
+We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM). 
+To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
+
+In order to understand habitat use by birds, environmental variables were prepared from landcover layers.
+A 2000m diameter buffer was made
+
+Environmental variables used by bird assembles were tested with a permanova for each season of sampling
+
+```{r Ambientes, fig.cap="The six environments selected to sample: Natural rocky shore, modified rocky shore, natural beach, modified beach, green area, and urban center."}
+#figura 1 con los 6 ambientes costeros estudiados
+
+include_graphics("Ambientes_Aves.png")
+```
+
+3. Relate to other studies
+
+[Describe what was done by referring to existing mehods in the literature]
+
+To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.
+
+[Provide more detailed information about the method and show that was a good choice]
+Covariables of detection and occupation are describedd in table 1.
+Ocupancy models were proyected to the study area.
+
+4. Indicate where problems occurred
+
+[Mention possible difficulty in the methodology]
 
 ```{r}
+#Covariables de deteccion y ocupaciono ocupadas para los modelos
+```
+
+### Results
+
+1. Revisting the research aim/existing research
+
+Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.
+
+2. General overview of results
+
+Species richnes is similar between same natural and modified environments. 
+There are distingible birs species assembles where only a few species contribute to the difference between them. For these habitats, bird assemblages differ between winter and spring seasons.
+Environmental variables can be responsible of both community identities and use of habitat individualy
+
+3. Invitations to view results
+
+```{r PredRiqueza}
 
@@
 library(MuMIn)
+
+AvesInv_riq <- readRDS("AvesInv_riq.rds")
+AvesPrim_riq <- readRDS("AvesPrim_riq.rds")
 
@@
 ggplot(NewData, aes(y=Pred, x=Habitat)) + geom_col(aes(fill=Grado_modificacion ), position="dodge") +
-  scale_fill_manual(aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Species richness")+
+  scale_fill_manual(name="Intervention", aesthetics = c("fill", "color"),values = c( '#5ab4ac','#d8b365')) +  theme_bw()+ ylab("Species richness")+
    geom_errorbar(aes(ymin=Pred-SE, ymax=Pred+SE), position = position_dodge2(width = 0.1, padding = 0.7))+
@@
 
-```{r, results='hide'}
+Species richnes is similar between two seasons of sampling, environments, nor habitat of origin of species. Althogh modified anvironmnet have less species for site, only urban centers are distinct.
+
+```{r DataNMDS, results='hide'}
 ##### METAMDS: Non-metric Multidimensional scaling- NMDS
@@
 ```
-
-```{r}
-#Inv
-
-Mod0 <- adonis2(AvesInv2 ~ 1, data = Amb, by = "terms")
-Mod1 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")###################### Menor AIC
-Mod2 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
-Mod3 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")
-Mod4 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
-Mod5 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
-
-AICc.PERMANOVA2 <- function(adonis2.model) {
-
-  # check to see if object is an adonis2 model...
-
-  if (is.na(adonis2.model$SumOfSqs[1]))
-    stop("object not output of adonis2 {vegan} ")
-
-  # Ok, now extract appropriate terms from the adonis model Calculating AICc
-  # using residual sum of squares (RSS or SSE) since I don't think that adonis
-  # returns something I can use as a likelihood function... maximum likelihood
-  # and MSE estimates are the same when distribution is gaussian See e.g.
-  # https://www.jessicayung.com/mse-as-maximum-likelihood/;
-  # https://towardsdatascience.com/probability-concepts-explained-maximum-likelihood-estimation-c7b4342fdbb1
-  # So using RSS or MSE estimates is fine as long as the residuals are
-  # Gaussian https://robjhyndman.com/hyndsight/aic/ If models have different
-  # conditional likelihoods then AIC is not valid. However, comparing models
-  # with different error distributions is ok (above link).
-
-  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
-  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
-
-  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
-
-  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
-
-  # AIC : 2*k + n*ln(RSS/n)
-  # AICc: AIC + [2k(k+1)]/(n-k-1)
-
-  # based on https://en.wikipedia.org/wiki/Akaike_information_criterion;
-  # https://www.statisticshowto.datasciencecentral.com/akaikes-information-criterion/ ;
-  # https://www.researchgate.net/post/What_is_the_AIC_formula;
-  # http://avesbiodiv.mncn.csic.es/estadistica/ejemploaic.pdf;
-  # https://medium.com/better-programming/data-science-modeling-how-to-use-linear-regression-with-python-fdf6ca5481be
-
-  AIC <- 2*k + nn*log(RSS/nn)
-  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
-
-  output <- data.frame(AICc = AICc, k = k, N = nn)
-
-  return(output)
-
-}
-
-DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
-
-DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
-DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
-DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
-DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
-DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
-DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
-
-```
-
-```{r}
-#Prim
-
-Mod0 <- adonis2(AvesPrim2 ~ 1, data = Amb, by = "terms")
-Mod1 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")
-Mod2 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
-Mod3 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")########################     Menor AIC
-Mod4 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
-Mod5 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
-
-AICc.PERMANOVA2 <- function(adonis2.model) {
-
-  # check to see if object is an adonis2 model...
-
-  if (is.na(adonis2.model$SumOfSqs[1]))
-    stop("object not output of adonis2 {vegan} ")
-
-  # Ok, now extract appropriate terms from the adonis model Calculating AICc
-  # using residual sum of squares (RSS or SSE) since I don't think that adonis
-  # returns something I can use as a likelihood function... maximum likelihood
-  # and MSE estimates are the same when distribution is gaussian See e.g.
-  # https://www.jessicayung.com/mse-as-maximum-likelihood/;
-  # https://towardsdatascience.com/probability-concepts-explained-maximum-likelihood-estimation-c7b4342fdbb1
-  # So using RSS or MSE estimates is fine as long as the residuals are
-  # Gaussian https://robjhyndman.com/hyndsight/aic/ If models have different
-  # conditional likelihoods then AIC is not valid. However, comparing models
-  # with different error distributions is ok (above link).
-
-  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
-  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
-
-  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
-
-  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
-
-  # AIC : 2*k + n*ln(RSS/n)
-  # AICc: AIC + [2k(k+1)]/(n-k-1)
-
-  # based on https://en.wikipedia.org/wiki/Akaike_information_criterion;
-  # https://www.statisticshowto.datasciencecentral.com/akaikes-information-criterion/ ;
-  # https://www.researchgate.net/post/What_is_the_AIC_formula;
-  # http://avesbiodiv.mncn.csic.es/estadistica/ejemploaic.pdf;
-  # https://medium.com/better-programming/data-science-modeling-how-to-use-linear-regression-with-python-fdf6ca5481be
-
-  AIC <- 2*k + nn*log(RSS/nn)
-  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
-
-  output <- data.frame(AICc = AICc, k = k, N = nn)
-
-  return(output)
-
-}
-
-DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
-
-DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
-DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
-DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
-DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
-DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
-DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
-
-```
-
-1. Overview-purpose of the work-give source of material/equipment used
-
-[General overview of this section]
-In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition based on corrected bird presences, and analysed bird assembles in those environment.
-
-[Provide background information and justification]
-The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
-The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that growth from a rural beach to a one of place of mayor urban growth in the las txx years.
-
-[Provide an overview of the procedure/method itself]
-Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu].
-To estimate species assembles for habitats, the vegan package [@Vegan] was used.
-Particular species were analized in a continuos environmental gradient using ocupancy probability from occupancy models also with DiversityOcuppancy package [@divoccu].
-
-2. Details about materials and methods- justify choices
-
-[Provide details about what was done and used and shows that care was taken]
-Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: urban centre, green area, natural rocky shore, modified rocky shore, natural beach, and urbanized beach (Figura 1).
-Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
-Surveys were conducted randomly during sunrise and the three hours later for 10 minutes, registering species and behaviour.
-
-Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
-We tested a model where seasonality has a interaction with the habitats defined in this research.
-
-[Continuing to describe what was done in detail, using languajge which comunicate that care was taken]
-
-Bird commmunities for each habitat were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with DiversityOcuppancy package [@divoccu](see table 1).
-We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM).
-To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
-
-In order to understand habitat use by birds, bird activities were counted by each habitat
-
-Fit of environmental variables on species ordination was also tested.
-
-3. Relate to other studies
-
-[Describe what was done by referring to existing mehods in the literature]
-To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.
-
-[Provide more detailed information about the method and show that was a good choice]
-Covariables of detection and occupation are describedd in table 1.
-
-4. Indicate where problems occurred
-
-[Mention possible difficulty in the methodology]
-
-```{r}
-#figura 1 con los 6 ambientes costeros estudiados
-```
-
-```{r}
-#Covariables de deteccion y ocupaciono ocupadas para los modelos
-```
-
-### Results
-
-1. Revisting the research aim/existing research
-Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.
-
-2. General overview of results
-The six coastal urban habitats shows distingible birs species assembles where only a few species contribute to the difference between them.
-For these habitats, bird assemblages differ between winter and spring seasons.
-Environmental variables can be responsible of both community identities and use of habitat idiviualy
-
-3. Invitations to view results
-
-Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla 3).
-Distribution of sites in graphical NMDS (Fig.
-\@ref(fig:NMDS)) showedthat both seassons presented differences in abundance of species mostly in the inland sites.
-Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
 
@@
 
-Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different.
-There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
-\@ref(fig:ANOSIM))
+Corrected abundances by detection probability
 
-```{r, results='hide'}
+Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla ModGLMEstacion).
+Distribution of sites in graphical NMDS (Fig.
+\@ref(fig:NMDS)) showed that both seassons presented differences in abundance of species mostly in the inland sites.
+Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
+
+```{r DataAnosim, results='hide'}
 ## test: ANOSIM
@@
 
+Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different.
+There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
+\@ref(fig:ANOSIM))
+
+```{r DataPermInv}
+#Inv
+
+Mod0 <- adonis2(AvesInv2 ~ 1, data = Amb, by = "terms")
+Mod1 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")###################### Menor AIC
+Mod2 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
+Mod3 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")
+Mod4 <- adonis2(AvesInv2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
+Mod5 <- adonis2(AvesInv2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
+
+AICc.PERMANOVA2 <- function(adonis2.model) {
+
+  # check to see if object is an adonis2 model...
+
+  if (is.na(adonis2.model$SumOfSqs[1]))
+    stop("object not output of adonis2 {vegan} ")
+
+  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
+  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
+
+  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  # AIC : 2*k + n*ln(RSS/n)
+  # AICc: AIC + [2k(k+1)]/(n-k-1)
+
+  AIC <- 2*k + nn*log(RSS/nn)
+  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
+
+  output <- data.frame(AICc = AICc, k = k, N = nn)
+
+  return(output)
+
+}
+
+DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
+
+DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
+DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
+DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
+DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
+DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
+DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
+
+```
+
+```{r DataPermPrim}
+#Prim
+
+Mod0 <- adonis2(AvesPrim2 ~ 1, data = Amb, by = "terms")
+Mod1 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`, data = Amb, by = "terms")
+Mod2 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+`Vegetation cover`, data = Amb, by = "terms")
+Mod3 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Ocean , data = Amb, by = "terms")########################     Menor AIC
+Mod4 <- adonis2(AvesPrim2 ~ Altitude +  Ocean +`Vegetation cover`+ Shrublands, data = Amb, by = "terms")
+Mod5 <- adonis2(AvesPrim2 ~ Altitude + `Paved surface`+ Shrublands+ Ocean, data = Amb, by = "terms")
+
+AICc.PERMANOVA2 <- function(adonis2.model) {
+
+  # check to see if object is an adonis2 model...
+
+  if (is.na(adonis2.model$SumOfSqs[1]))
+    stop("object not output of adonis2 {vegan} ")
+
+  RSS <- adonis2.model$SumOfSqs[ length(adonis2.model$SumOfSqs) - 1 ]
+  MSE <- RSS / adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  nn <- adonis2.model$Df[ length(adonis2.model$Df) ] + 1
+
+  k <- nn - adonis2.model$Df[ length(adonis2.model$Df) - 1 ]
+
+  # AIC : 2*k + n*ln(RSS/n)
+  # AICc: AIC + [2k(k+1)]/(n-k-1)
+
+   AIC <- 2*k + nn*log(RSS/nn)
+  AICc <- AIC + (2*k*(k + 1))/(nn - k - 1)
+
+  output <- data.frame(AICc = AICc, k = k, N = nn)
+
+  return(output)
+
+}
+
+DF<- data.frame(Modelo = paste0("Mod", 0:5), AICc = NA)
+
+DF$AICc[1] <- AICc.PERMANOVA2(Mod0)$AICc
+DF$AICc[2] <-  AICc.PERMANOVA2(Mod1)$AICc
+DF$AICc[3] <- AICc.PERMANOVA2(Mod2)$AICc
+DF$AICc[4] <-  AICc.PERMANOVA2(Mod3)$AICc
+DF$AICc[5] <-  AICc.PERMANOVA2(Mod4)$AICc
+DF$AICc[6] <-  AICc.PERMANOVA2(Mod5)$AICc
+
+```
+
+Altitud, oceano y cob veg en invierno
+Altitud, oceano y sup imp en primavera
+
 4. Specific/key results in details
@@
 Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
-(For a complete species list of SIMPER, see Suplementary material).
-
-Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
-
-Species such as xxx, showed differernces in habitat use between seasons.
-(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))
+(For a complete species list of SIMPER, see Suplementary material SimperPrim, SimperInv).
 
@@
 
-```{r, fig.width=13, fig.height=6}
+```{r Ocupancia, fig.width=13, fig.height=6}
 
@@
 
+Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
+
+Species such as xxx, showed differernces in habitat use between seasons.
+(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))
+
 During winter, community assemblages were explain by three environmental variables: coastal urban habitats, crops and tree plantations. 
 In spring, variables were coastal urban habitats and native forest.
-
-```{r}
-#ORDISTEP
-
-#Invierno
-#Step: AvesInv2 ~ AMBIENTE + Cultivos + `Plantacion de arboles`
-
-#Primavera
-#Step: AvesPrim2 ~ AMBIENTE + `Bosque nativo`
-
-```
 
@@
 
-```{r Comportamineto, fig.height=8, fig.width=10}
-ComportamientoInv <- read_rds("ComportamientoInv.rds")
-I <-ggplot(ComportamientoInv) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
-  theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
-
-ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
-
-P <-ggplot(ComportamientoPrim) + 
-  geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
-  theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
-  scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
-
-layout <- "
-AAAAAAAA
-BBBBBBB#
-"
-I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
+```{r Comportamiento, fig.height=8, fig.width=10}
+# ComportamientoInv <- read_rds("ComportamientoInv.rds")
+# I <-ggplot(ComportamientoInv) + 
+#   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=4, scales = "free_y")+  
+#   theme(legend.position = "none", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+#   scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#33a02c','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+# 
+# ComportamientoPrim <- read_rds( "ComportamientoPrim.rds")
+# 
+# P <-ggplot(ComportamientoPrim) + 
+#   geom_col(aes(x=AMBIENTE, y=Total_ind, fill=Comportamiento), color="black") + theme_classic()+ facet_wrap(~Cientifico, ncol=3, scales = "free_y")+  
+#   theme(legend.position = "right", axis.text.x = element_text(angle = 45, hjust = 1))+ ylab("Número individuos") +xlab(" ")+
+#   scale_fill_manual(aesthetics = "fill", values = c('#a6cee3','#1f78b4','#b2df8a','#33a02c','#fb9a99','#e31a1c','#fdbf6f','#ff7f00'), name="Bird behavior")
+# 
+# layout <- "
+# AAAAAAAA
+# BBBBBBB#
+# "
+# I + P + plot_layout(design = layout) +plot_annotation(tag_levels = 'A')
+#
 

### 2020-12-10 README.Rmd
Arreglo Ms con presentacion Lab

--- 2020-11-04 README.Rmd
@@
 Escritura de manuscrito en ingles **Ms_HabitatAves.Rmd**
+
 El manuscrito cuenta con imput desde: 
@@
 - graficos de comportamiento desde archivo **Comportamineto_Aves.R**, con abundancia corregida de invierno de **AbundInv_Corregido.rds** y **AbundPrim_Corregido.rds**
+
+## Figuras para presentacion de laboratorio viernes 4 diciembre
+
+Esta presentación surgió con la idea de darle una vuelta a los resultados de este estudio
+Archivo: **Figuras presentacion lab.R**
+Se alimenta de los archivos
+- **RiquezaAves_ambiente.R** tiene riqueza de aves y la riqueza a partir de los modelos de prediccion
+- desde **RiquezaAves_ambiente.R** se exportan **AvesInv_riq.rds** y **AvesPrim_riq.rds**
+
+## Inclusion de comentarios de la reunion de lab
+
+- Figura prediccion de riqueza al comienzo de resultados en manuscrito y tabla de modelos. Obtenido de **Figuras presentacion lab.R**

### 2020-12-10 Tablas_Ms_HabitatAves.Rmd
Arreglo Ms con presentacion Lab

@@
 
-```{r}
+```{r ModPredRiqueza}
 # GLMmixto con variables aleatorias
@@
 
-```{r,results='asis'}
+```{r ModGLMEstacion,results='asis'}
 #Modelo 1= Abundancia ~ Estacion * Especie + AMBIENTE+ (1|Sitio), family = poisson, data =Aves ) #AIC 17716.1
@@
 
-```{r, results='asis'}
+```{r SimperInv, results='asis'}
 Inv_DF <-  read.csv("ResumenSimper_Inv2.csv") %>% as.data.frame() 
@@
 
-```{r, results='asis'}
+```{r SimperPrim, results='asis'}
 Prim_DF <-  read.csv("ResumenSimper_Prim2.csv") %>% as.data.frame()
@@
 
-```{r, results='asis'}
+```{r ModOcuPrim, results='asis'}
 DF_occu <- tibble( Species= c("Columba livia", "Larus dominicanus", "Leucophaeus pipixcan", "Pelecanus thagus", "Phalacrocorax bougainvillii"), 
@@
 
-```{r, results='asis'}
+```{r ModOcuInv, results='asis'}
 DF_occu <- tibble( Species= c("Columba livia","Coragyps atratus", "Larosterna inca", "Larus dominicanus", "Leucophaeus modestus", "Pelecanus thagus", "Sephanoides sephaniodes", "Turdus falcklandii"), 

### 2020-12-10 RiquezaAves_ambiente.R

@@ -20,6 +20,8 @@ AvesInv <- left_join(x=AvesInv, y= BirdNames)
 #Grafico riqueza especies invierno
 AvesInv_riq <- AvesInv %>% group_by(AMBIENTE,Sitio, Habitat) %>% summarise(Riqueza = n())
 
+saveRDS(AvesInv_riq, "AvesInv_riq.rds")
+
 AvesInv_riq2 <- AvesInv_riq %>% group_by(AMBIENTE, Habitat) %>% summarise_at("Riqueza", .funs = list(mean=mean, max=max, min=min)) %>% 
   mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))
 
@@ -50,6 +52,8 @@ AvesPrim <- left_join(x=AvesPrim, y= BirdNames)
 #Grafico riqueza especies primavera
 
 AvesPrim_riq <- AvesPrim %>% group_by(AMBIENTE,Sitio, Habitat) %>% summarise(Riqueza = n())
+
+saveRDS(AvesPrim_riq, "AvesPrim_riq.rds")
 
 AvesPrim_riq2 <- AvesPrim_riq %>% group_by(AMBIENTE, Habitat) %>% summarise_at("Riqueza", .funs = list(mean=mean, max=max, min=min)) %>% 
   mutate(AMBIENTE=fct_relevel(AMBIENTE, "VERDE", "URBANO", "ROQUERIO NATURAL","ROQUERIO INTERVENIDO","PLAYA NATURAL","PLAYA INTERVENIDA"))

### 2020-12-17 Ms_HabitatAves.Rmd
Avance con orden de resultados

@@
 
-1. Establish importance of the field- provide background, keywords- present the problem
-
-[Establish the importance of this research topic]
 During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
-
-[Provide general background information]
 Urbanization is a complex process that causes profound changes in the ecological functioning of the landscaped gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
-
-[Establish the importance of this research topic, more specific/detailed way]
 Some of these losses of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
 These is because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
-
-[Provide general background information, more specific/detailed way]
-
 Studies suggest that bird communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
@@
 These areas are attractive for people to settle and by 2017, about 40%  of the world’s population live within 100 km of the coast [@UNocean_fact2017].
+Hence, only in 2009, 67% of magacities corresponded to coastal cities *von glasgow 2013*.
 Species and ecosystems of coastal areas are often threatened by the growing urbanization, the landscape change, and also by the vulnerable that this area is naturally
-
-[Provide transition between the general problem area and the literature review]
 
@@
 
-[Provide brief overview of key research projects in this area]
-Urban homogenization has been studied in cities, focused in terrestrial variables
-Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats
+Birds have been largely studied in urban ecology and they are considered one of the most recognised ways to interact with nature [@miller2002conservation;@jones2011appetite]
 
-[Describe gaps in the research]
-There is a gap in studies that focus in coastal ecotone and the influence of urban areas
-focusing on marine and terrestrial interaction of species in an urbanized area and how birds use this as habitats
+Urban homogenization has been studied in cities and there is many information about bird species.
+Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats.
 
-[Describe paper itself]
+Although birds are the most research species in coastal urban studies, most of the literature have been centered in pollution and human impacts and they have focused on terrestrial ecosystems [@graells2020review].
+
+There is a gap in studies that focus in coastal ecotone and the influence of urban areas focusing on marine and terrestrial interaction of species in an urbanized area and how birds use it.
+
 This research aim to identified the use of coastal urban habitats by birds describing the composition of species in different environments, considering bird species origin (marine and terrestrial).
-with the aim of: 1.
-Identify bird species assemble of habitats in coastal urban environments, specifically the interaction between marine and inland birds, 2.
-identify how urbanization affects those bird assembles, 3.
-Evaluate iconic bird species habitat occupation, and 4.
-describe bird behavior in those habitats
+
+Specifically, the objectives of this study are: 
+1. Identify bird species assemble in coastal urban environments, specifically the interaction between marine and inland birds, 
+2. Caracterize differences among those bird assembles, 
+3. identify patterns in spatial use in coastal cities from iconic bird species habitat occupation.
 
@@
 [Give details about the methodology reported in the paper]
-The present study was carried out in the Gran Valparaíso, a metropolitan area that includes three municipalities in central Chile
+
+We studied coastal urban diversity of birds in the Graeter Valparaíso, determined assembles in different environments, relationships with environmental conditions and occupancy of bird species.
 
 [Announces the findings]
-Urban habitats in coastal areas present the conditions that allow specific species composition, cohabiting marine and inland bird species
+Bird assembles showed to be different among environments, showing that urban habitats in coastal areas present the conditions that allow specific species composition.
+This allow the coexistence of marine and inland bird species.
 
@@
 
-[General overview of this section]
+In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition and analised occupancy of key species in those environments.
+The Greater Valparaíso is the largest metropolitan coastal area in Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
+It is composed by three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las txx years.
 
-In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition and analised occupancy of key species in those environments.
-
-[Provide background information and justification]
-
-The Greater Valparaíso is the largest metropolitan coastal area in Central Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
-The three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las txx years.
-
-[Provide an overview of the procedure/method itself]
-
-Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu].
 To estimate species assembles for habitats, the vegan package [@Vegan] was used. 
@@
 Six replicas of theses habitats were sampled by visual bird surveys in south hemisfer winter and spring of 2019.
-Between four and six surveys were conducted daily randomly during sunrise and the three hours later for 10 minutes in each site.
-All species that were seen and heard were recorded.
+Between four and six surveys were conducted daily and randomly during sunrise and the three hours later for 10 minutes in each site.
+All species that were seen and heard were recorded in a tablet.
 
+## Layers preparation
+
+In order to understand habitat use by birds, environmental variables were prepared from landcover layers.
+For each of the 36 samplig points a 2000m diameter buffer was made using the pecentaje of covering area in the selection.
+
+## Data analysis
+
+Bird abundance obtained from the field was corrected by detection capacity of sampling using occupancy models with DiversityOcuppancy package [@divoccu]. 
 Seasonality was tested with a mixed GLM with abundance as a response variable and a random effect of sample sites.
@@
 
-[Continuing to describe what was done in detail, using language which comunicate that care was taken]
-
 Bird commmunities for each habitat were analised using ordination methods with vegan package [@Vegan] in R with species abundances corrected by detection capacity, using occupancy models with DiversityOcuppancy package [@divoccu](see table 1).
 We  determined dissimilarity distances among sample sites and tested significant differences among habitat with analysis of similarities (ANOSIM). 
-To determine species contribution to the differrence between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
-
-In order to understand habitat use by birds, environmental variables were prepared from landcover layers.
-A 2000m diameter buffer was made
-
-Environmental variables used by bird assembles were tested with a permanova for each season of sampling
+To determine species contribution to the difference between habitats we used Bray-Curtis dissimilaries with SIMPER analysis.
+Environmental variables used by bird assembles were tested with a permanova for each season of sampling.
 
@@
 
-[Describe what was done by referring to existing mehods in the literature]
+To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed.
 
-To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed and projected over the study area.
-
-[Provide more detailed information about the method and show that was a good choice]
-Covariables of detection and occupation are describedd in table 1.
-Ocupancy models were proyected to the study area.
-
-4. Indicate where problems occurred
-
-[Mention possible difficulty in the methodology]
+Covariables of occupation are described in table 1. Occupancy models were analysed using DiversityOccupancy package in R. Akaike information criteria was use in order to select the best model.
+Ocupancy models selected were proyected to the study area showing the probability of use of habitat for each species.
 
@@
 
-Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat. Urbanization is a big factor in bird assemblages.
+Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat.
+*Elements of urbanization and closeness to the coast are important factors on bird assemblages.*
 
@@
 
-Species richnes is similar between same natural and modified environments. 
-There are distingible birs species assembles where only a few species contribute to the difference between them. For these habitats, bird assemblages differ between winter and spring seasons.
-Environmental variables can be responsible of both community identities and use of habitat individualy
+A total of 58 bird species were found in the six coastal urban environments sampled. From those, 37 were present in both seasons.
+Species richnes are similar between winter and spring (45 and 48 species, respectively)
+
+Predicted species richness are also similar between same natural and modified environments.
+Only terrestrial environments showed significative differences, where urban environments showed fewer species that green areas.
 
@@
 
-Species richnes is similar between two seasons of sampling, environments, nor habitat of origin of species. Althogh modified anvironmnet have less species for site, only urban centers are distinct.
-
 ```{r DataNMDS, results='hide'}
@@
 
-Corrected abundances by detection probability
-
 Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla ModGLMEstacion).
@@
 \@ref(fig:NMDS)) showed that both seassons presented differences in abundance of species mostly in the inland sites.
-Additionally, coastal modified sites, as those in urbanized beach and modified rocky shore habitats, are closer to urban centres than coastal natural sites.
+Additionally, coastal modified sites, such as urbanized beach and modified rocky shore, are closer to urban centres than coastal natural sites.
 
@@
 
-Dissimilary rank shows with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats, this demonstrate that group of species for each habitat are different.
-There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig.
-\@ref(fig:ANOSIM))
+Seasonal ANOSIM analysis shows that assembles in each environment are different among them (R=0.584 winter and R=0.573 spring, both P< 0.01)
+Dissimilary rank indicates with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats. 
+There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig. \@ref(fig:ANOSIM)).
 
@@
 
-Altitud, oceano y cob veg en invierno
-Altitud, oceano y sup imp en primavera
+Winter assemble is defined by altitude, percentage of ocean, and vegetation cover. Spring assembles are defined by altitude, percentage of ocean and paved surfaces.
 
@@
 
-Predictions in the studied area indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
+Predictions in the studied area indicates differences of habitat use. During winter,  (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
 
@@
 
-species for each habitat
-Occupancy model map show
+Four species showed distinctive characteristics of habitat use according to accupancy projections and covariables determined by the models selected.
+
+*Larus dominicanus* presented the same probability of occupancy in the whole area both winter and spring. In this case, there was none covariable in the model that dertermined the occupancy.
+
+Occupancy of *Pelcanus thagus* is similar between both seasons, with higher probabilities of ocupancy in coastal areas.
+This species is determined by covariables as altitude and the presence of native forest
+
+*Larosterna inca*
+
+# escribir como esto:
+*Columba livia* occupancy is different between winter and spring.
+During the winter its presence is focussed in certain coastal areas, defined by the presence of sand (mapa y modelo).
+During the spring, its presence is high in almost the whole study area with exception of some small areas.
+According to the model selected presence of native forrest and sand, and the ausence of grave and tree plantation allow this pattern.
 
@@
 
-Most of the species were detected during the fliying, however some were founded in particular activities.
-
-5. Comparisons with results in other research
-
-Occupancy models for specific species
-
-6. problems with results
-
-7. Possible implications with results
-
 ### Discussion/Conclusion
@@
 [Revisit Introduction to recall specific weakness in methodology used in previous studies]
+
+Living in the city: can anyone become an‘urban exploiter’?
+Are urban bird communities influenced by the bird diversity of adjacent landscapes?
+Generalists are the most urban-tolerant of birds: a phylogenetically controlled analysis of ecological and life history traits using a novel continuous measure of bird responses to urbanization
+Bird Diversity in Urban Ecosystems: The Role of the Biome and Land Use Along Urbanization Gradients
+Arthropod abundance modulates bird community responses to urbanization   … es importante considerar la disponibilidad de alimento en especies que pueden movilizarse desde su ambiente ideal?
+A habitat island approach to conserving birdsin urban landscapes: case studies from southernand northern Europe
+Distribution and habitat selection of wintering birds in urbanenvironments
+Bird communities and the structure of urban habitats
+Species interactions and habitat associations of birds inhabiting urban areas of Sydney, Australia
 

### 2020-12-18 Ms_HabitatAves.Rmd
Avance discusion y tabla covariables

@@
 
+# Abstract
+
+I. 
+M.
+R.Six environments present specific assembles and they are determined mostly by variables such as altitude and percentage of the ocean in the areas.
+From the species ocurrence in those, there are strictly marine species and some can move to inland environments.
+Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with hay percentage of shrubs and native forrest).
+D-C. Elements of urbanization and closeness to the coast are important factors on bird assemblages
+
 # Introduction
@@
 Species and ecosystems of coastal areas are often threatened by the growing urbanization, the landscape change, and also by the vulnerable that this area is naturally
-
 Even this scenario, urbanization has been mostly focus in terrestrial aspects, and even when more than the half of the cities in the world rise on the coast, there is a lack of studies addressing marine and terrestrial interactions.
@@
 Birds have been largely studied in urban ecology and they are considered one of the most recognised ways to interact with nature [@miller2002conservation;@jones2011appetite]
-
 Urban homogenization has been studied in cities and there is many information about bird species.
 Considering bird communities in urban areas depend of the peri-urban composition of species, there are no studies in the effects of marine habitats.
-
 Although birds are the most research species in coastal urban studies, most of the literature have been centered in pollution and human impacts and they have focused on terrestrial ecosystems [@graells2020review].
-
 There is a gap in studies that focus in coastal ecotone and the influence of urban areas focusing on marine and terrestrial interaction of species in an urbanized area and how birds use it.
@@
 This research aim to identified the use of coastal urban habitats by birds describing the composition of species in different environments, considering bird species origin (marine and terrestrial).
-
 Specifically, the objectives of this study are: 
 1. Identify bird species assemble in coastal urban environments, specifically the interaction between marine and inland birds, 
-2. Caracterize differences among those bird assembles, 
+2. Caracterize differences among those bird assembles, and
 3. identify patterns in spatial use in coastal cities from iconic bird species habitat occupation.
@@
 4. Describe the present paper
-[Give details about the methodology reported in the paper]
 
-We studied coastal urban diversity of birds in the Graeter Valparaíso, determined assembles in different environments, relationships with environmental conditions and occupancy of bird species.
+We studied coastal urban diversity of birds in the Graeter Valparaíso, determined assembles in different environments, relationships with environmental conditions and occupancy of key bird species.
+Bird assembles showed to be different among environments, showing that variability of urban habitats in coastal areas allow specific species composition, hence the coexistence of marine and inland bird species.
 
-[Announces the findings]
-Bird assembles showed to be different among environments, showing that urban habitats in coastal areas present the conditions that allow specific species composition.
-This allow the coexistence of marine and inland bird species.
+**Conclusion: La variabilidad ambiental dentro de las ciudades costeras permite la co-ocurrencia de especies marinas y terrestres, determinando ensambles especfíficos para los distintos ambientes**
 
@@
 
-Living in the city: can anyone become an‘urban exploiter’?
-Are urban bird communities influenced by the bird diversity of adjacent landscapes?
-Generalists are the most urban-tolerant of birds: a phylogenetically controlled analysis of ecological and life history traits using a novel continuous measure of bird responses to urbanization
-Bird Diversity in Urban Ecosystems: The Role of the Biome and Land Use Along Urbanization Gradients
-Arthropod abundance modulates bird community responses to urbanization   … es importante considerar la disponibilidad de alimento en especies que pueden movilizarse desde su ambiente ideal?
-A habitat island approach to conserving birdsin urban landscapes: case studies from southernand northern Europe
-Distribution and habitat selection of wintering birds in urbanenvironments
-Bird communities and the structure of urban habitats
-Species interactions and habitat associations of birds inhabiting urban areas of Sydney, Australia
-
 2. Mapping 
 [Revisit methodology used in this study]
+
+This study gives information about not only bird species richness found in coastal urban habitats, also describe species identity in terms of assembles adapted in specific conditions within the city and bird ocurrence in continuos conditions
+
 [Revisit and summaries the results]
+Six environments present specific assembles and they are determined mostly by variables such as altitude and percentage of the ocean in the areas.
+From the species ocurrence in those, there are strictly marine species and some can move to inland environments.
+Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with hay percentage of shrubs and native forrest).
+
 [Show where and how the present work fits into the research "map" in this field]
@@
 [Recall an aspect of the results that represents a positive achievement or contribution of this work]
+
+Environmental variability within coastal urban areas could allow the co-ocurrence of marine and terrestrial bird species, which is reflected in specific asembles in the six studied environments.
+
 [Focus in the meaning and implications of the achievements in this work]
+
 [Note if one of the achievement or contributions of the work is a novelty]
@@
 [Describe limitations which should direct future research]
+High variability among studied environments plays a difficult rol 
+This is considered at the momnet of occupancy analysis and analysis are made considering continuos data
+It is possible that buffer area of influence should be specific for each species
+
 [Suggest a specific area to be addressed in future work]

### 2020-12-18 Tablas_Ms_HabitatAves.Rmd
Avance con orden de resultados
Avance discusion y tabla covariables

@@
 library(tidyverse)
+
+```
+
+```{r covariables, results='asis'}
+DF_cov <- tibble( `Detection covariables`= c("Temperatura","Humedad", "DirViento" ,"RapViento", "Agua"), 
+                   `Occupancy covariables`= c("Vegetation cover","Altitude","Distance to river",
+                                              "Grassland", "Shrublands", "Native forest","Tree plantation" ,"Crops" ,
+                                              "Paved surface","Sand", "Gravel", "Ocean" )
+                   )
+
+kable(DF_cov, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
+
 ```

### 2020-12-18 Tablas_Ms_HabitatAves.Rmd
Arreglo tabla covariables

--- 2020-12-10 Tablas_Ms_HabitatAves.Rmd
@@
 library(tidyverse)
+
+```
+
+```{r covariables, results='asis'}
+DF_cov <- tibble( `Detection covariables`= c("Temperatura","Humedad", "DirViento" ,"RapViento", "Agua", " ", " ", " ", " ", " ", " ", " "), 
+                   `Occupancy covariables`= c("Vegetation cover","Altitude","Distance to river",
+                                              "Grassland", "Shrublands", "Native forest","Tree plantation" ,"Crops" ,
+                                              "Paved surface","Sand", "Gravel", "Ocean" )
+                   )
+
+kable(DF_cov, booktabs=T, escape = F) %>% kable_styling(latex_options = "basic") %>% column_spec(column = 1, italic = T)
+
 ```

### 2021-01-12 Ms_HabitatAves.Rmd
Arreglo intro y resultados

@@
 
-I. 
-M.
-R.Six environments present specific assembles and they are determined mostly by variables such as altitude and percentage of the ocean in the areas.
+Six environments present specific assembles and they are determined mostly by variables such as altitude and percentage of the ocean in the areas.
 From the species ocurrence in those, there are strictly marine species and some can move to inland environments.
-Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with hay percentage of shrubs and native forrest).
-D-C. Elements of urbanization and closeness to the coast are important factors on bird assemblages
+Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with hay percentage of shrubs and native forest).
+Elements of urbanization and closeness to the coast are important factors on bird assemblages
 
@@
 During 2018, more than half of world’s population lived in urban settlements with cities growing in both size and number [@UN_WorldCities2018].
-Urbanization is a complex process that causes profound changes in the ecological functioning of the landscaped gradually results in a changing spatial structure [@antrop2000changing] being one of the mayor causes of species loss [@czech2000economic].
-Some of these losses of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
+Urbanization is a complex process and one of the major drivers of natural habitat loss and degradation [@grimm2008global] and it has generated profound changes in the ecological functioning of the landscape [@antrop2000changing] being
+Although the impact of urbanisation varies with the speed and intensity of environmental alterations, it is one of the mayor causes of biodiversity loss [@czech2000economic].
+(McKinney 2002; Clergeauet al.2006; Aronsonet al.2014).
+It has been estudied that loss of native species have promoted the replacement by non-native species [@mckinney2006urbanization].
 These is because few species can adapt better to urban and suburban conditions [@mckinney1999biotic], affecting at ecosystemic level [grassland: @zeeman2017biotic], biomes [temperate: @zeeman2017biotic], and taxonomic groups [insects: @knop2016biotic, but mainly studies in birds and plants].
 Studies suggest that bird communities in cities are more similar to urban communities nearby than to communities in surrounding natural environments.
-To bird assembles local features are more important than surrounding landscapes @clergeau2001urban,
-
-2. Previous an current research and contributions
-
-[Describe general problem area or the current research focus of the field]
+To bird assembles, local features are more important than surrounding landscapes @clergeau2001urban.
 
@@
 Even this scenario, urbanization has been mostly focus in terrestrial aspects, and even when more than the half of the cities in the world rise on the coast, there is a lack of studies addressing marine and terrestrial interactions.
+marine and inland interactions could be importatn
 
-3. Locate the gap-describe the problem to address-present a prediction to be tested
-
-Birds have been largely studied in urban ecology and they are considered one of the most recognised ways to interact with nature [@miller2002conservation;@jones2011appetite]
+Birds have been largely studied in urban ecology and they are considered one of the most recognised ways to interact with nature [@miller2002conservation; @jones2011appetite]
 Urban homogenization has been studied in cities and there is many information about bird species.
@@
 Specifically, the objectives of this study are: 
-1. Identify bird species assemble in coastal urban environments, specifically the interaction between marine and inland birds, 
-2. Caracterize differences among those bird assembles, and
-3. identify patterns in spatial use in coastal cities from iconic bird species habitat occupation.
+1. Identify and characterize bird species assemble in coastal urban environments, specifically the interaction between marine and inland birds, and 
+2. identify patterns in spatial use in coastal cities from iconic bird species habitat occupation.
 
-4. Describe the present paper
-
-We studied coastal urban diversity of birds in the Graeter Valparaíso, determined assembles in different environments, relationships with environmental conditions and occupancy of key bird species.
+We studied coastal urban diversity of birds in coastal metropolitan area in South America, determined assembles in different environments, relationships with environmental conditions and occupancy of key bird species.
 Bird assembles showed to be different among environments, showing that variability of urban habitats in coastal areas allow specific species composition, hence the coexistence of marine and inland bird species.
@@
 
-1. Overview-purpose of the work-give source of material/equipment used
-
 In this research, we conducted bird surveys in six coastal urban environments in the Greater Valparaíso, estimated species composition and analised occupancy of key species in those environments.
 The Greater Valparaíso is the largest metropolitan coastal area in Chile and the second most populated urban area in the country (935,602 people according to @censo2017chile).
-It is composed by three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las txx years.
+It is composed by three coastal cities: Valparaíso, the mayor port in the country; Viña del Mar, with high touristic infrastructure; and Concón, a small area that grew from a rural beach to a one of place of mayor urban growth in the las xx years.
+
+```{r}
+
+```
 
@@
 
-2. Details about materials and methods- justify choices
-
-[Provide details about what was done and used and shows that care was taken]
 Six coastal habitat were defined in terms of its proximity to the coast, level of urbanization and land cover: natural rocky shore, modified rocky shore, natural beach, and urbanized beach, green area, and urban center (Fig.
@@
 All species that were seen and heard were recorded in a tablet.
-
-## Layers preparation
-
-In order to understand habitat use by birds, environmental variables were prepared from landcover layers.
-For each of the 36 samplig points a 2000m diameter buffer was made using the pecentaje of covering area in the selection.
 
@@
 
-3. Relate to other studies
-
-To independize our analysis from habitats already defined, ocupancy models of SIMPER selected species were developed.
-
-Covariables of occupation are described in table 1. Occupancy models were analysed using DiversityOccupancy package in R. Akaike information criteria was use in order to select the best model.
-Ocupancy models selected were proyected to the study area showing the probability of use of habitat for each species.
+SIMPER selected species ocurrence was analized using ocupancy models with the package DiversityOccupancy in R [@divoccu] .
+In order to do this, environmental variables were prepared from landcover layers.
+For each of the 36 samplig points a 2000m diameter buffer was made using the pecentaje of covering area in the selection.
+Covariables of occupation are described in table 1. 
+To select the best model of ocurrence, Akaike Information Criteria (AIC) was used. 
+Models selected were proyected to the study area showing the probability of use of habitat for each species in the area.
 
@@
 
-1. Revisting the research aim/existing research
-
 Coastal cities in central Chile probed to allow habitats were marine and terrestrial bird species can cohabitat.
@@
 
-2. General overview of results
-
 A total of 58 bird species were found in the six coastal urban environments sampled. From those, 37 were present in both seasons.
-Species richnes are similar between winter and spring (45 and 48 species, respectively)
+Species richnes are similar between winter and spring (45 and 48 species, respectively).
 
@@
 Only terrestrial environments showed significative differences, where urban environments showed fewer species that green areas.
-
-3. Invitations to view results
 
@@
 
-```{r NMDS, fig.width=9, fig.height=4, fig.cap="Sites distribution in A winter and B spring"}
+```{r NMDS, fig.width=9, fig.height=4, fig.cap="MDS sites distribution according to bird asembles in A: winter and B: spring"}
 #Funcion para grafico NMDS en ggplot Invierno
@@
 
-Coastal urban habitats show specific composition of species abundances for winter and spring seassons (Tabla ModGLMEstacion).
-Distribution of sites in graphical NMDS (Fig.
+Coastal urban habitats show specific composition of species abundances for winter and spring seasons (Tabla ModGLMEstacion).
+Distribution of sites in graphical MDS (Fig.
 \@ref(fig:NMDS)) showed that both seassons presented differences in abundance of species mostly in the inland sites.
-Additionally, coastal modified sites, such as urbanized beach and modified rocky shore, are closer to urban centres than coastal natural sites.
+Additionally, coastal modified sites, such as urbanized beach and modified rocky shore, are more similar to urban centres than coastal natural sites.
 
@@
 
-```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A winter (R=0.584, P<0.001) and B spring (R=0.573, P< 0.001)"}
+```{r ANOSIM, fig.width=9, fig.cap="Dissimilarity ranking between an within the habitats in A: winter (R=0.584, P<0.001) and B: spring (R=0.573, P< 0.001)"}
 Inv <- ggplot()+ geom_boxplot(aes(x=Anosim_Diss_Inv2$class.vec, y=Anosim_Diss_Inv2$dis.rank), notch = TRUE, varwidth=TRUE)+theme_classic()+
@@
 
-Seasonal ANOSIM analysis shows that assembles in each environment are different among them (R=0.584 winter and R=0.573 spring, both P< 0.01)
-Dissimilary rank indicates with an 95% confidence interval that dissimilarities withing habitat are lower than between habitats. 
+Seasonal ANOSIM analysis shows that assembles in each environment are different among them for both seasons studied (R=0.584, P< 0.01 in winter and R=0.573, P< 0.01 in spring).
+Dissimilary rank indicates with an 95% confidence interval (notch in boxplot), that dissimilarities withing each habitat are lower than between them. 
 There is one exception shown by natural beach habitat during winter, here variability of species in the habitat is as high as we consider all habitats together (Fig. \@ref(fig:ANOSIM)).
@@
 
-Winter assemble is defined by altitude, percentage of ocean, and vegetation cover. Spring assembles are defined by altitude, percentage of ocean and paved surfaces.
+Permanova indicates that both winter and spring aassembles are determined by environmental variables such as altitude, ocean cover.
+Two variables are different for each season: during the winter, vegetation cover also determined assembles and during spring paved surfaces cover.
 
-4. Specific/key results in details
+Both sampled seasons showed that few species contribute to differences among bird assembles found in the six habitats. 
+Acccording to simper analysis, during winter eigth species showed to add to this difference between habitats.
+The contribution of each one of them go from 5 to 12%.
+These species are *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephanoides*.
+In each one of the paired habitat comparision the cumulative sum of two or more species reaches up to 29.3% of the explanation.
 
-Both sampled seasons showed that few species contribute to differences between habitats.
-Acccording to simper analysis, during winter species were *Pelecanus thagus*, *Larus dominicanus*, *Coragyps atratus*, *Larosterna inca*, *Leucophaeus modestus*, *Columba livia*, *Turdus falcklandii*, and *Sephanoides sephaniodes*; and during spring, *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
+During the spring, six species show to add to the difference of bird assembles: *Leucophaeus pipixcan*, *Larus dominicanus*, *Columba livia*, *Larosterna inca*, *Phalacrocorax bougainvillii*, and *Pelecanus thagus*.
+The contribution of each species go from 5 to 11% to the difference, reaching 26.1% in the cumulative sum of two or more species contribution.
 (For a complete species list of SIMPER, see Suplementary material SimperPrim, SimperInv).
@@
 
-Predictions in the studied area indicates differences of habitat use. During winter,  (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim))
+Predictions of ocurrence of those bird species on the studied area, indicates differences of habitat use (Fig. \@ref(fig:OccuInv) and \@ref(fig:OccuPrim)). 
+Most of the predictions (nine of 15 proyections) show higher levels of occupancy in the coast than in the inland. 
+In winter two species are strictly marine, three are marine and are able to use part of the terrestrial habitats, two are present in the whole stydy area, and one terrestrial and able to use part of the coast.
+In spring, four species are strictly marine and two are present in the whole stydy area (one of them with some restrictiones in the coast and inland).
 
-Species such as xxx, showed differernces in habitat use between seasons.
-(Fig. \@ref(fig:OccuInv)), (Fig. \@ref(fig:OccuPrim))
+Only four species are present in both seasons.
+From those, two of species  showed the same use of habitats between winter and sprin (**Larus dominicanus** and **Pelecanus thagus**), while the other two showed differences between seasons (**Columba livia** and **Larosterna inca**).
+*Larus dominicanus* presented the maximun probability of occupancy in the whole area both winter and spring. In this case, there was none covariable in the model that determined the occupancy. 
+Occupancy of *Pelcanus thagus* is almos identical between both seasons.
+Projection shows the maximun probability of ocupancy in the coast and probabilities of zero in inland areas.
+The ocurrence of this species is determined by the altitude (negative effect) and in the winter ausence of native forest, grave and the presence of ocean surface, and in spring the presence of native forest, and the ausence of shrubs and sand.
 
@@
 
-Four species showed distinctive characteristics of habitat use according to accupancy projections and covariables determined by the models selected.
+*Larosterna inca* shows similar ocurrence in both seasons, however during the spring it expand a little to the inland in some specific parts of the study area. The ocurrence is determine
 
-*Larus dominicanus* presented the same probability of occupancy in the whole area both winter and spring. In this case, there was none covariable in the model that dertermined the occupancy.
-
-Occupancy of *Pelcanus thagus* is similar between both seasons, with higher probabilities of ocupancy in coastal areas.
-This species is determined by covariables as altitude and the presence of native forest
-
-*Larosterna inca*
-
-# escribir como esto:
-*Columba livia* occupancy is different between winter and spring.
+*Columba livia* .
 During the winter its presence is focussed in certain coastal areas, defined by the presence of sand (mapa y modelo).
 During the spring, its presence is high in almost the whole study area with exception of some small areas.
-According to the model selected presence of native forrest and sand, and the ausence of grave and tree plantation allow this pattern.
+According to the model selected, the presence of native forest and sand, and the ausence of grave and tree plantation allow this pattern.
 
@@
 [Revisit and summaries the results]
-Six environments present specific assembles and they are determined mostly by variables such as altitude and percentage of the ocean in the areas.
+Coastal urban environment studied present specific assembles of birds and they are determined mostly by variables such as altitude and ocean surface surrounding that areas.
 From the species ocurrence in those, there are strictly marine species and some can move to inland environments.
@@
 
+Clergeau, P., Jokim€aki, J. & Savard, J.-P. (2001). Are urban birdcommunities influenced by the bird diversity of adjacent landscapes?J. Appl. Ecol., 38, 1122–1134:
+- Test the random dispersal-assembly hypothesis
+- whatmakes a species tolerant to urbanisation is less obvious (Evanset al.2011).
+According to our analyses, this is primarily related  to  life  history  and  the  way  individuals  use  the resources
+- Evidence is nonetheless clearer for the importance of lifehistory.
+Life  history  integrates  key  evolved  adaptationsexpected to influence the colonisation-extinction dynamicsthat ultimately sustain biodiversity (Stearns 2000; Saetheret al.2005), and hence has long been considered central tounderstanding the varying responses of organisms to environ-mental changes
+
+para que una especies se catalogue de tolerante o no tolerante a la urbanizacion, primero tiene q estar presente en los alrededores para ver si es posible el que entre o no a la ciudad.
+
+especies en areas intervenidas y modificadas por la urbanizacion
+disponibilidad de alimentacion y refugio que permiten la ocurrencia de especies (no necesariamente su reproduccion)
+adaptabilidad de las especies para la busqueda de estos recursos (plasticidad en la dieta de palomas y gaviotas)
+
+Much of the species loss is associated with a lack of appropriate adaptations of most species for exploiting resources and avoiding risks of the urban environments.
+
+Some species with seasonal differences are related to migratory behaviour, or specific nesting habitat requierements (**Leucophaeus modestus** in @cikutovic1988gonadal, **Sephanoides sephanoides**).
+
 ### References

### 2021-01-12 Tablas_Ms_HabitatAves.Rmd
Arreglo intro y resultados

@@
 
-nuevoinv <- AvesInv_riq %>% ungroup() %>% mutate(Temporada="Winter") %>% 
+AvesInv_riq <- readRDS("AvesInv_riq.rds")
+nuevoinv <- AvesInv_riq  %>% mutate(Temporada="Winter") %>% 
   mutate(Ambiente = case_when(AMBIENTE == "PLAYA INTERVENIDA"| AMBIENTE =="PLAYA NATURAL"~"Beach",
@@
 
+AvesPrim_riq <- readRDS("AvesPrim_riq.rds")
 nuevoprim <- AvesPrim_riq %>% ungroup() %>% mutate(Temporada="Spring") %>% 

### 2021-01-12 Analisis_HabitatAves.R

@@ -1,0 +1,198 @@
+# ANALISIS HABITAT AVES- desde septiembre 2020
+#Se utiliza la abundancia corregida por deteccion
+
+library(readxl)
+library(tidyverse)
+library(vegan)
+library(MASS)
+library(ggplot2)
+library(ggrepel)
+###########################################
+#preparacion de datos registro aves
+
+AvesInv2 <- read_rds("AbundInv_Corregido.rds") 
+AvesInv2 <-AvesInv2 %>% ungroup() %>% dplyr::select(-Sitio) %>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+AvesPrim2 <- read_rds("AbundPrim_Corregido.rds")
+AvesPrim2 <-AvesPrim2 %>% ungroup() %>% dplyr::select(-Sitio)%>% mutate_all(~replace(., is.na(.), 0)) %>% sqrt()
+
+#Datos ambientales  incluidos buffers
+
+Amb<- read_rds("/home/giorgia/Documents/Doctorado tesis/Monitoreo aves/MonitoreoVisualGit/Occdata_occu.rds")
+Amb <- Amb %>% 
+  dplyr::select(Sitio,CobVeg, AMBIENTE, Distancia_rio, Altura, `Buffer_2200_Bosque Nativo`, `Buffer_2200_Cultivos`, `Buffer_2200_Grava`, `Buffer_2200_Oceano`, `Buffer_2200_Pastizales`, `Buffer_2200_Matorrales`, `Buffer_2200_Sup impermeables`, `Buffer_2200_Suelo arenoso`, `Buffer_2200_Plantación de árboles`) %>% 
+  rename( `Cobertura vegetal` =CobVeg) %>% rename( `Distancia a río` =Distancia_rio) %>% 
+  rename( `Bosque nativo` =`Buffer_2200_Bosque Nativo`) %>% rename( Cultivos =`Buffer_2200_Cultivos`) %>% 
+  rename( Grava =`Buffer_2200_Grava`) %>% rename( Oceano =`Buffer_2200_Oceano`) %>% 
+  rename( Pastizales =`Buffer_2200_Pastizales`) %>% rename( `Matorrales` =`Buffer_2200_Matorrales`) %>% 
+  rename( `Superficies impermeables` =`Buffer_2200_Sup impermeables`) %>% rename( `Suelo arenoso` =`Buffer_2200_Suelo arenoso`) %>% 
[…]

### 2021-01-12 Ms_HabitatAves.Rmd
UN poco de avance en resultados (occu) y discusion

@@
 The ocurrence of this species is determined by the altitude (negative effect) and in the winter ausence of native forest, grave and the presence of ocean surface, and in spring the presence of native forest, and the ausence of shrubs and sand.
+During the winter the ocurrence of *Columba livia* is focussed in certain coastal areas, defined by the presence of sand (mapa y modelo).
+During the spring, its presence is high in almost the whole study area with exception of some small areas.
+According to the model selected, the presence of native forest and sand, and the ausence of grave and tree plantation allow this pattern.
+*Larosterna inca* shows similar ocurrence in both seasons, however during the spring it expand a little to the inland in some specific parts of the study area.
+The ocurrence is determined by covariables such as altitud, native forest, sand (winter), and crops and ocean (spring).
 
@@
 In spring, variables were coastal urban habitats and native forest.
-
-*Larosterna inca* shows similar ocurrence in both seasons, however during the spring it expand a little to the inland in some specific parts of the study area. The ocurrence is determine
-
-*Columba livia* .
-During the winter its presence is focussed in certain coastal areas, defined by the presence of sand (mapa y modelo).
-During the spring, its presence is high in almost the whole study area with exception of some small areas.
-According to the model selected, the presence of native forest and sand, and the ausence of grave and tree plantation allow this pattern.
 
@@
 
-This study gives information about not only bird species richness found in coastal urban habitats, also describe species identity in terms of assembles adapted in specific conditions within the city and bird ocurrence in continuos conditions
+This study gives information about not only bird species richness found in coastal urban habitats, also describe species identity in terms of assembles adapted in specific conditions within the metropolitan coastal area and bird ocurrence in continuos conditions.
 
@@
 Coastal urban environment studied present specific assembles of birds and they are determined mostly by variables such as altitude and ocean surface surrounding that areas. 
-From the species ocurrence in those, there are strictly marine species and some can move to inland environments.
-Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with hay percentage of shrubs and native forrest).
+From the key species studied, there are strictly marine species and some can move to inland environments.
+Most of the terrestrial species are less strict and they manage to get closer to the ocean, specifically in areas with native vegetation such as natural beaches and natural rocky shore (with high percentage of shrubs and native forrest).
 
 [Show where and how the present work fits into the research "map" in this field]
+Althogh assembles found in coastal urban areas were different among them, there were several species shared and only a few that contribute to the difference between pairs of comparision. 
+This specific species showed that marine species ocurrence is determined by not only marine variables
+and terestrial species can be positive influence by conditions presented in the coast line.
+
+The evidence shows that in inland areas only high urbanized environments present low abundance of species, nevertheless 
+most of the birds
 

### 2021-01-12 Ms_HabitatAves.Rmd
avance discusion

@@
 
-Some species with seasonal differences are related to migratory behaviour, or specific nesting habitat requierements (**Leucophaeus modestus** in @cikutovic1988gonadal, **Sephanoides sephanoides**).
+Some species with seasonal differences are related to migratory behaviour, or specific nesting habitat requierements (**Leucophaeus modestus** that nest only in the Atacama desert: @cikutovic1988gonadal and @aguilar2016unusual, **Sephanoides sephanoides**).
 
